\section{The Construction of the First Table}

The first table from 1° to 6° is constructed as follows: the figure 2 is entered next to \Libra\, 1°

\begin{tabular}{lr}
\Libra\, 1° & 2 \\
\Libra\, 2° & 4 \\
\Libra\, 3° & 6 \\
\Libra\, 4° & 8 \\
\Libra\, 5° & 10 \\
\Libra\, 6° & 12 \\
\end{tabular}

There is a progressive increase of 2.

At \Libra\, 7° this sequence is broken and a factor of 14 is added for a total of 26 to be entered next to \Libra\, 7°:

\begin{tabular}{lr}
\Libra\, 7° & 26 \\
\Libra\, 8° & 28 \\
\Libra\, 9° & 30 \\ 
\Libra\, 10°  & 2 \\
\Libra\, 11°  & 4 \\
\Libra\, 12°  & 6 \\
\end{tabular}

Here again 14 is added to the sequence for a total of 20 next to \Libra\, 13°:

\begin{tabular}{lr}
\Libra\, 13° & 20 \\
\Libra\, 14° & 22 \\
\Libra\, 15° & 24 \\
\Libra\, 16° & 26 \\
\Libra\, 17° & 28 \\
\Libra\, 18° & 30 \\
\end{tabular}

Here again 14 is added to the sequence for a total of 44, from which 30 is subtracted, leaving 14. This figure will be entered next to \Libra\, 19°:

\begin{tabular}{lr}
\Libra\, 19° & 14 \\
\Libra\, 20° & 16 \\
\Libra\, 21° & 18 \\
\Libra\, 22° & 20 \\
\Libra\, 23° & 22 \\ 
\Libra\, 24° & 24 \\
\end{tabular}

Again 14 is added to the sequence for a total of 38, from which 30 is subtracted, leaving 8. This figure will be entered next to \Libra\, 25°:

\begin{tabular}{lr}
\Libra\, 25° & 8 \\
\Libra\, 26° & 10 \\ 
\Libra\, 27° & 12 \\
\Libra\, 28° & 14 \\ 
\Libra\, 29° & 16 \\ 
\Libra\, 30° & 18 \\
\end{tabular}

So every 6° the sequence will be broken, 14 will be added, then 2 will be added <per degree> in each sign. Therefore \Libra\, will have the figure 2 next to \Libra\, 1° and 18 next to \Libra\, 30°. \Leo\, and \Pisces\, have the same arrangement of figures as \Libra\,.

Next in order \Scorpio\, will have 14 next to \Scorpio\, 1°, 2 will be added to each degree in the series, giving 24 next to \Scorpio\, 6°. Then the sequence is broken, finishing with 30 next to \Scorpio\, 30°. \Aries\, and \Virgo\, will have the same numbers.

In order to explain the construction more briefly so that the \textbf{/296K/} table as a whole and its particulars may be remembered, calculate the increments <between signs> as follows: 2 is entered next to \Libra\, 1°. To this figure I add 12 (for the \textbf{/283P/} circle of signs) for a total of 14. \Scorpio\, has this figure entered next to \Scorpio\, 1°. Add 12 again to this 14 for a total of 26. \Sagittarius\, has this figure, 26, next to \Sagittarius\, 1°. Going in the order of signs and adding 12, we can find the correct figure to be entered next to the first degree of each sign. By adding 12 <to the figure at 1° of each sign> and by breaking the sequence with the addition of 14, we can construct the entire table. The figure next to \Sagittarius\, 1° will be the same as
\Taurus\, 1°; \Aquarius\, 1° will be the same as \Cancer\, 1°; \Capricorn\, 1° will be the same as \Gemini\, 1°. 

In one respect these pairs will have similar powers and will support each other mutually, but in other respects they will be different because of their different rising times. 

This table also has the years tabulated beside the figures and the degrees as an example <of the procedure>. Intelligent students will easily grasp the precise calculations for each klima and for changes in the location <of the nativity>.

\newpage