\chapter{Preface}
This is a copy of the \textit{Vettius Valens Anthologies} that Prof. Riley translated and kindly made freely available on his \href{https://www.csus.edu/indiv/r/rileymt/}{website}.

I have taken a number of liberties with the layout, primarily to make the text easier to read. I have kept Prof. Riley's angle brackets ($< >$) which mark his clarifications within the text. I have also kept his references to the pages of the original Greek texts edited by Wilhelm Kroll (1908 edition) (\textbf{/\#K/}) and David Pingree (1986 edition) (\textbf{/\#P/}). 

The public domain \href{https://www.ctan.org/pkg/starfont}{StarFont Sans} astrological fonts used in this document were created by Anthony I.P. Owen and made available as a Latex package by Matthew Skala. 

This document was built from Latex files created with the \href{https://www.tug.org/texworks/}{TexWorks} editor.

\section{Annotations}

Annotations have been added primarily as margin notes and footnotes. 

In addition, comments/questions/musings/summaries or other assertions appear in \textit{italics} between square brackets. For example, ([\textit{my interjections}]). 

Any Table of Content entries that appear in bracketed italics are not part of the original text. For example, the entry under Book I, \textit{[General Indications]} is a section title not found in the original text.

\section{Abbreviations}
The following abbreviations are used in the text:

\begin{description}
\item[AATPB]
	\textsl{Ancient Astrology Theory and Practice: Mathseos Libri VIII by Firmicus Maternus} trans. Jean Rhys Bram, Noyes Press, 1975.	
	
\item[AATPG] \textsl{Ancient Astrology in Theory and Practice, Vol One} by Demetra George, Rubedo, 2019

\item[CAA]
	\textsl{Carmen Astrologicum: Dorotheus of Sidon} trans. David Pingree, Astrology Classics, 2005

\item[CAD]
	\textsl{Carmen Astrologicum: Dorotheus of Sidon: The 'Umar Al-Tabari Translation} trans. Benjamin N. Dykes. 2019.

\item[CAP]
	\textsl{Carmen Astrologicum: Dorotheus of Sidon} trans. David Pingree, Ascella, 1993.

\item[DF]
	\textsl{Definitions and Foundations} trans. Robert H. Schmidt, Golden Hind Press, 2009.
	
\item[GH] 
	\textsl{Greek Horoscopes} by O. Neugebauer and H.B. Van Hoesen, J.H. Furst, 1959 (reprint 1987)
	
\item[HA] 
	\textsl{Hellenistic Astrology: The Study of Fate and Fortune} by Chris Brennan, Amor Fati, 2017 (errata corrected 2020)
	
\item[LH]
	\textsl{Liber Hermetis} trans. Robert Zoller, Spica, 1998.
	
\item[PAG] 
	\textsl{Late Classical Astrology: Paulus Alexandrinus and Olympiodorus} trans. Dorian Gieseler Greenbaum, M.A., Arhat, 2001.

\item[PAH] 
	\textsl{Paul of Alexandria Introduction to Astrology} trans. James Herschel Holden, M.A., AFA, 2012.

\item[PAS] 
	\textsl{Paulus Alexandrinus: Introductory Matters} trans. Robert Schmidt, Golden Hind Press, 1993, rev. 3rd edition 1995.
	
\item[PTA]
	\textsl{Tetrabiblos: Claudius Ptolemy} trans. J.M. Ashmand, Astrology Classics, 2002.
	
\item[PTR]
	\textit{Ptolemy Tetrabiblos} trans.  F. E. Robbins, Harvard University Press, 1940.
	
\item[VRS1] 
	\textsl{Vettius Valens: The Anthology Book I} trans. Robert H. Schmidt, Golden Hind Press, 1993.

\item[VRS2] 
	\textsl{Vettius Valens: The Anthology Book II, Part 1} trans. Robert H. Schmidt, Golden Hind Press, 1994.

\item[VRS3] 
	\textsl{Vettius Valens: The Anthology Book II (concl.) \& Book III} trans. Robert H. Schmidt, Golden Hind Press, 1994.

\item[VRS4] 
	\textsl{Vettius Valens: The Anthology Book IV} trans. Robert H. Schmidt, Golden Hind Press, 1996.

\item[VRS5] 
	\textsl{Vettius Valens: The Anthology Book V \& VI} trans. Robert H. Schmidt, Golden Hind Press, 1997.

\item[VRS7] 
	\textsl{Vettius Valens: The Anthology Book VII} trans. Robert H. Schmidt, Golden Hind Press, 2001.

\end{description}
\newpage

\section{Useful Links}

\noindent\href{https://www.jcremers.com/}{PlanetDance Astrology Software}

	A free astrology software application created by J.C. Remers. Includes a number Hellenistic Greek techniques under Horoscope->Classical.


\noindent\href{http://www.projecthindsight.com/images/TablesPDFs/Tb2-AscT-sysAB.pdf}{Table of Hellenistic Ascenional Times}
	
	In the Schmidt translations, Robert Hand, in the footnotes, appears to have used the \textsl{Table of Ascensions – System A for Babylon: Klima 2} to work out many of the ascenional timing examples Valens uses.
	
\newpage
