\section{Preface}
\index{astrology!oath}
First of all I must exact an oath from my readers—particularly in regard to this book—that they guard my words as a mystic secret. I have expounded the preceding methods in a complex but logical order,
methods which have a great power to attract and to guide men to a love of beauty. <Through these methods> they may extend their range of interests from the lesser matters to the greater, and they might not abandon their quest and, in so doing, bring criticism on us. 

Now it is best to come to these matters after training oneself in those books which we previously composed. For the distribution <of the
chronocratorships> will be considered unassailable and sacred as a result of the <previously made> overall and periodic determinations <of the chronocrators>. For just as a man might climb to a mountain peak, hiking through canyons and winding places with great toil, then come upon a temple with its precious statues of “gold, silver, and ivory” and perhaps of purple. This man would consider his climb to have been of no trouble or toil, and he would worship with gladness, imagining that he is associating with the gods in heaven. Those who follow our directions have this same experience, and I adjure them by the sacred circle of the \Sun, by the varied paths of the \Moon, by the powers of the other stars, and by the circle of the
twelve signs to keep these matters secret, never to share them with the ignorant or the uninitiated, and to remember and to honor the one who inducted them into this art. 

May it go well for those who keep this oath and may the aforesaid gods grant them what they wish; may the opposite happen to those who foreswear this oath.

\newpage