\section{The Critical Year. The Ecliptic Place.}

In order to complete this treatise, it is necessary to continue with the rest of the topics—now the critical year. The critical year is found from the transmission or reception of malefics in relation to the luminaries, the Ascendant, and each other. 

The general procedure is as follows. In all cases, it is necessary
to count off the years from the sign in the Ascendant. If the current year is found to be in the sign of the new or full moon, or in the sign in square or opposition to the <new or full moon> sign, the year will be critical and troublesome, especially if (under these circumstances) Saturn is found to be passing through the four places which just precedeed the angles at the nativity. If the basis of the nativity is in accord, death will follow, bodily weakness, bleeding, dangerous diseases, hidden troubles, falls, sudden dangers.

Sometimes the critical point affects matters of livelihood and rank, if the bodily state is helped by an aspect of benefics. In addition, determine the distance from Saturn’s position at the nativity to the ruler of the \textbf{/211K/} new or full moon, then count that distance from the Ascendant. When Saturn transits that position or is in opposition or square with that position, death will occur, or a grave crisis to health or business. 

Likewise the critical year will occur if Saturn is at the ascending or the descending node, or at the points square with these. If someone takes to his bed ill while the Sun is transiting \textbf{/201P/} the ascending or descending node or through the points square with them, and if a malefic beholds the Sun, then the bout of disease will be dangerous and hazardous. Indications of the intensity or the danger will occur when the Moon transits the same places (the ascending <or descending> node).

\mndl Since the previously mentioned place (i.e. the ecliptic place) is powerful, I offer this advice to my readers, not with the idea that it is possible to appeal the decrees of fate and to act according to one’s wishes, but <with the suggestion> that it is possible (I would certainly claim it to be so) for the initiates of this art to weaken the evil to some extent. For God, in his desire that man should foreknow the future, brought this science into the world, a science through which anyone can know his fate in order to bear the good with great contentment and the bad with great steadfastness. 

Some things which must be guarded against are foreknown because of the conjunctions and aspects of the benefics. Nevertheless even if a benefic is able to do something, a malefic in conjunction or aspect will hinder the good. If either malefics alone or benefics alone are in conjunction or in configuration, with no aspect of the other, then the results will be definite. 

Accordingly then, the initiates of this art, those wishing to have knowledge of the future, will be helped because they will not be burdened with vain hopes, will not expend grievous midnight toil, will not vainly love the impossible, nor in a like manner will they be carried away by their eagerness to attain what they may expect because of some momentary good fortune. A suddenly appearing good often grieves men as if it were an evil; a suddenly appearing evil causes the greatest misery to those who have not trained their minds in advance.
So as not to be diverted and go into irrelevancies, <let us resume>. 

It will be necessary to examine the sign in which the ascending node of each nativity is located: note whether it is tropic, solid, bicorporeal, and which star rules it. The effect of the sign will be weakened there. For we often find \textbf{/212K/} that stars which normally can have some effect at the nativity or at transits have no effect in these places. If they are at a phase while at the ascending or descending node, they become the causes of evil, especially if they are found to be retrograde or setting. 

It will also be necessary to examine the current position of the ascending node in the year in question to see which Place of the nativity it is transiting, for in this case too the effects of the sign and its ruler \textbf{/202P/} will be weakened. Especially if they are also
found to be chronocrators, they can have no effect until the time when they pass out of that place.

\newpage