\section{Initiatives [Elections]}

With reference to the days under investigation: if the moon is passing through the current position of the ascending node, or through the points in square or opposition, particularly if it is at the same degree position, beware of starting anything: do not sail, do not marry, do not have meetings, do not begin anything, do not plant, do not introduce; in short, do not do anything. What has been started will be judged insecure or prone to come to a bad end; it will be something regrettable, incomplete, subject to penalties, grievous, and not lasting.
 
 If someone seems to have begun the development of some business in these days, the business will go bankrupt, will be troublesome, subject to penalties, easily ruined, and a stumbling block. Not even benefics which happen to be in these places do anything entirely good.
Therefore, even without <consulting> a natal chart, if anyone guards against the current transits of the moon through the ascending node, he will not make a mistake.

If one finds someone beginning some matter while the moon is passing through the ecliptic places, he can forecast that the matter will be incomplete, regretted, and subject to penalties. I myself, being as wary of such days as I could be, have cast Initiatives for activities and friendships according to the chronocratorships of the current period, and I have considered the beginnnings to be unexceptionable and easily attainable. 

But occasionally I have been in error because of the untimely presence of a friend, an untimely association, or because I began something under duress, and I found the results to be grievous or subject to
penalties and delays. Consequently they <Initiatives> must be cast for all beginnings: the sailing of fleets, \textbf{/213K/} campaigns, commands, advancement, departures—everything that can come to accomplishment in life. 

<Without the Initiatives> it is not beneficial to sacrifice to the gods or to dedicate sanctuaries.  Prayers will not be fulfilled nor God be worshipped. He will be called lazy and inactive because oath-takers
will be perjured and oaths will not be fulfilled. Neither gifts to the masses nor expenditures on buildings will be celebrated or lasting; they will be criticized and will crumble. Neither will the treatment of bodily
ills be successful; men will be disease-ridden and incurable, especially if malefics are in aspect with these places or if the Moon is passing through their degree-positions. (If it is only in the same sign, it will be
effective in a delayed and dilatory manner; but even so it will bring insecure/unsteady actions.)

\newpage