\section{The Operative Month: For Day Births, From the Current Sun to the Moon at Birth, and the Same Distance from the Ascendant (6K, 4P)}

\textbf{/214K/}The King had this opinion about the operative month: determine the distance from the \Sun’s current position to the \Moon’s position at birth, then count that distance from the Ascendant. 

It will be necessary to examine the ruler of the sign where the count stops to see if it is in operative signs, and to make a judgement about the stars in conjunction or in aspect, whether benefic or malefic. (For day births, determine the distance from the \Moon’s current position to the \Sun’s position at birth; count that from the Ascendant.)

Some astrologers note the ruler of the degree-position of the new or full moon and forecast according to that “month.” Some consider the following month to be effective: note the configuration which the \Moon\xspace at the nativity was found to have with the \Sun; whenever it has the same configuration with the current \Sun,
it will determine the month. \textbf{/204P/} For example: \Sun\xspace in \Leo\xspace 5\deg, \Moon\xspace in \Libra\xspace 2\deg. The distance from
the \Sun\xspace to the \Moon\xspace is 81\deg. 

When the \Moon\xspace is the same distance from the \Sun\xspace in any month, i.e. when it has the same configuration as it had at the nativity, it will indicate the <operative> month.

In my experience, those months in which the distribution of the years occur have seemed to be operative. When the \Sun\xspace is in those places or at the points in square or opposition to them, it will make a
forecast of the results which are indicated for the year or for the transmissions. 

In the same way \Mars, \Venus, \Mercury, and the \Moon, when they are passing through the places mentioned above, will be indicative. We will judge that place to be even more effective in producing results, if these stars are passing through a phase while transiting the place. At that time innovations and activities in business will occur. 

If the sign <?> is passing out of whatever configuration the it has\footnote{Possibly, if a planet passes out of a configuration it had in the sign(?)}, there will be no change or innovation, nor a fulfillment of the expected outcome. However, the \Sun\xspace passing through these places and
arousing the power of the chronocrators is very effective.



\newpage