\section{The Method of New and Full Moons. Conception with Reference to the Ascending Node. Length of Life, with Examples (12K,9P)}

I am reminding you of my generosity in supplying proofs for every chapter so that I do not seem to be writing this in order to obfuscate. Now if you rush to the books of the older compilers, be aware that their texts have been adorned with an affected style which can bewilder the minds of their readers and of the ignorant, although their texts have not attained the truth and are enemies of the wise. Wasting the time of
many men and leading them astray, these texts have defrauded some of life and have terminally afflicted others. 

\index{\textit{Critodemus}}
Let anyone read the so-called \mn{\tiny{Critodemus}} \textit{Vision of Critodemus}: how its beginning is so fantastical and how the rest is so marvellous to the unlearned. “Coursing the deep,” he says, “and traversing vast wilds, I was deemed worthy by the gods of attaining a safe harbor and a secure anchorage.” Then with frightful oaths he expounds his methods and his transmissions. He sanctifies his readers in other ways and displays much
bombast throughout the book, such as it is. He indicates that its powers control everything <with its prodigious learning>, but he locks up in infinite verbiage the truth of his teaching. 

This man should be praised and admired, since he has gone through so much labor and has become a guide for seekers. Indeed, by arranging his material mystically and complexly in tabular form and in connected prose, he has attracted many enthusiasts, some of whom have ignored his useless bombast, have tracked down the relevant chapters with great toil, and have brought praise and credit to the man. Others with a less tenacious spirit, have brought criticism to this art. My exposition will (as I think) be persuasive and educational for my readers, and they will not regret
their work. \textbf{/143P/} Through the influence of what has been and will be said, I hope to bring back into the fold those who have come to hate their role <as student>.

Since the casting of rays—either houseruling or destructive—has now been set out as previously outlined, \textbf{/151K/} I want to share, not to hide, the method for the Numerical Lot and the anaeretic, powerful places, now that I have tested them. 

\index{length of life}
\index{nodes}
\index{vital sector}
First of all, it will be necessary to determine for every nativity whether it has a controller or a houseruler. If it is found to have one, it is necessary to use the previously mentioned terms. If however the nativity is found to be lacking a houseruler or a controller, and is destroyed by no afflicting ray, then it will be necessary to determine the degree of the previous new or full moon (for night and day births) and to count from the new or full moon “upward” (=in the direction of
diurnal motion) to the Ascendant or to another angle, or (which is more powerful) to the ascending or descending node. Then having noted the number of degrees, count this amount from the Ascendant in the direction of diurnal motion (=toward MC). Where the count stops, calculate the total number of years from
the apheta (using the rising times of the native’s klima), then make your forecast.

If, for a day birth, the number is excessive, subtract the distance between the new or full moon and the ascending or descending node from the distance between the angles, i.e. between the Ascendant and MC, then do your operations in the same manner, counting the remaining degrees from the Ascendant to MC in the direction of diurnal motion. 

For night births, take the distance from the new or full moon to the ascending or descending nodes or a center (in the direction of diurnal motion), then count that distance from
the Ascendant in the order of the signs. Calculate the years where the count stops, using the rising times, and make the forecast. If the number is excessive, subtract the distance from the Ascendant to IC, then count the remainder from the Descendant in the order of the signs (i.e. toward MC). The total, calculated from the rising times, will be the length of life.

In most cases, it is necessary to place the vital sector starting with the Ascendant or with the Descendant at the point to which the ascending or descending node inclines, or to which the new or full moon inclines, (i.e. whether in the hemisphere above the earth or towards the one below): if the nativity is
at the new moon, start with the Ascendant; if full moon, with the Descendant.

If the Ascendant, the ascending node, or the descending node is found in the sign of the new or full moon, or in the signs in opposition or square with them, \textbf{/144P}/ then for day births count the total distance from the Ascendant, for night births from the Descendant in the order of the signs. \textbf{/152K/} The point square with the ascending node has an anaeretic force—of course, the exact-to-the-degree vital sector which starts at the \Sun\xspace and \Moon\xspace and runs to the ascending node and to the points in opposition or square with the node <?>.

Occasionally, when there is a controller or a houseruler, the anaereta coincides with the apheta or the houseruler and strengthens the destructive force. If in such a case the controller is suitably situated, and the apparent houseruler is distributing the chronocratorship, then the vital sector of this horoscope (whether counted in the direction of diurnal motion or in the order of the signs using the total of the rising times) will be considered as characteristic of one who dies at birth or in the womb. 

\index{conception}
The same considerations should be applied when forecasting conception, but the Ascendant at the time of delivery must be observed. 

The conception itself will be in vain if someone observes the new or full moon extending to the ascending or descending nodes or to the angles. 

If the same number of years are found to be granted when you
calculate from the delivery and from the conception, then death will indisputably occur.

\newpage