\section{The Distinguishing Characteristics of the Triangles, the Houserulers, the Helpers, and the Sects of the Sun and the Moon—for Day or Night Births}

An examination of the distinguishing characteristics of the previously mentioned triangles, along with the lofty or mediocre fortune of each person’s nativity, will be indicative. 

\mnm[0.3cm]
For day nativities, it will be necessary to examine the Sun: 
\begin{enumerate}
\item in which triangle it lies;
\item its predominant houseruler and its helper, viz. whether it is at, following, or preceding an angle, rising or setting, and whether it is in its own signs;
\item which benefic or malefic it has in aspect. 
\end{enumerate}
Having determined all this, then make the prediction. 

\mndl[0.2cm]
If $<$the houseruler$>$ happens to be in the Ascendant or at MC or is in one of the operative signs, $<$astrologers$>$ forecast a fortunate and illustrious nativity; if it follows an angle, a nativity of moderate fortune; if it precedes an angle, a base and unfortunate nativity. It is also necessary to see how the Sun itself is situated and which stars it has in aspect. For night nativities it will be necessary to inspect the Moon in a similar fashion and to determine how the predominant houseruler of the triangle and its assistant are configured, as was stated above.

\textbf{/57K/} For nativities which are badly situated (whether day or night births), if the predominant
houseruler is unfavorably located, but its successor is at an angle or otherwise configured \textbf{/56P/} well, the
native will experience ups and downs during his early years until the rising time of the sign or until the cyclical return of the chronocrator, but will afterwards be vigorous and effective—except for being unsteady and anxious. 

If the preceding houseruler is favorably situated and the succeeding one unfavorably, the native will fulfill his promise well at first, but afterwards will be brought low, starting at the time of the rising of the sign in which the succeeding houseruler is unfavorably situated. (We will clarify in more detail the determination of the chronocrator at the appropriate time.) 

If both houserulers are will situated, good fortune will be enduring and will be remarkable (unless some malefic is opposed or in superior aspect), and the nativity will not take a turn for the worse. 

Whenever any star is a houseruler and just precedes an angle, it will be negative and a diminisher of fortune: it puts men in the power of others; it brings men into vicissitudes and reduces their rank; it afflicts them with injuries, diseases, and criminal charges, as well as poverty.

Now then, for those born during the day: if the Sun is found in \Aries, \Leo, or \Sagittarius, it is best for it to be at an angle. If it follows an angle, and if the stars of its sect are similarly situated, and if \Mars\xspace is not in opposition or in square, then $<$the \Sun$>$ will be considered to be indicative of good fortune. If the situation is reversed, the opposite will be the case. 

If the Sun is found in \Taurus, \Virgo, or \Capricorn\xspace (for day births), it will be necessary to investigate first how \Venus\xspace is configured, second the \Moon, and third
\Mars, and to see what stars they have in aspect. In the same way, if the \Sun\xspace is in the next triangle, \Gemini, \Libra, or \Aquarius\xspace (for day births), it will be necessary to look at \Saturn, then \Mercury, then \Jupiter. The same for the triangle \Cancer, \Scorpio, and \Pisces: if the \Sun\xspace is there (for day births), it will be necessary to look at \Venus, then \Mars, then the \Moon, to see if they are at angles. Having determined all this, then make the prediction. For night births, it is necessary to look at the \Moon\xspace in the same manner.

\mndl[0.2cm]
\textbf{/58K/} It is best if the stars of the day sect are found at angles in their own triangles or in operative
places; the same is true for the stars of the night sect. If they are in other triangles or in the opposite sect, prosperity will be less and will be \textbf{/57P/} subject to anxiety. 

\marginnote{\Fortune}[0.3cm]
If the houserulers and their helpers are unfavorably situated, it will be necessary to examine the Lot of Fortune and its houseruler. If they are found to be at an angle or just following an angle, with benefics in aspect, then the native will have some good fortune and rank. He will be subject to vicissitudes and reversals on occasion, but he will not be
totally at a loss. If even these $<$the Lot and its houseruler$>$ are badly situated, affairs must be considered
mediocre, even harsh: men will find it hard to succeed in their undertakings; they will be in need, poverty stricken;
they will blaspheme the gods. If these places have malefics in aspect, men will be toilers, vagrants, captives, abject, wretched, disabled, and endangered. But if the Lot of Fortune and its houseruler have benefics in aspect—even though they themselves are unfavorably situated—men will get by on others’
pity or be adopted by others, and they will lead a respectable life for some time, receiving a share of business, trusts, or gifts. They will not, however, continue their life without disturbance or without criticism.

\marginnote{\small{\textsc{Aspects}}}[0.2cm]
It will be necessary to look at the aspects of every houseruler and the arrangement of the configurations,
to see if they are appropriate or the reverse. If, for example, Saturn is found in opposition or in square for night births, it will bring about reversals, ruin, dangers, injuries, and diseases, as well as sluggishness in
enterprises. 

For day births, Mars causes hot, reckless men, precarious in their activities and in their livelihoods. They experience imprisonment, trials, abuse, cuts, burns, bleeding, and accidents/falls. But \mnmb if these stars happen to be configured properly, in their own sects, they are actively positive. As a result, these stars are not to be considered malefics in all cases; they can be bestowers of good. Particularly if Saturn (for day births) has a favorable relationship with the houseruler and has \Jupiter\xspace and the \Sun\xspace in aspect, it then makes men wealthy, famous, profiting from legacies, lords of estates and slaves, guardians and supervisors of others' affairs. 

For night births, however, if Saturn is \textbf{/59K/} configured well and has a relationship with the houseruler, it will also cause the loss of what was gained, reduction in rank, and infamy. 

Let the same considerations be true for Mars: for night births it grants leadership, generalship, public commands of the masses; for day births (if \Mars\xspace is in operative places), it brings about the previously \textbf{/58P/} mentioned circumstances, but it then turns them into reversals, fears, and oppositions; it makes leadership subject to factionalism and terror. It brings attacks of enemies and uprisings of the mob, famines and plagues on cities, assaults, fires, dangerous crises.

\mnbm[0.2cm]
In the same way the benefics will take on the character of malefics whenever they are situated badly as houserulers. If they happen to be at angles while their houseruler just precedes an angle, their ability to do good will be weakened. 

\marginnote{\footnotesize{\textsc{Dispositor}}}[0.3cm]
In any type $<$of forecast/nativity$>$ it will be necessary to examine how the houseruler of the houseruler is situated and what stars it has in aspect. If the overall houseruler is
unfavorably situated, but its ruler $<$=ruler of its sign$>$ is configured well, then the native will have help and
a basis of livelihood and rank proportional to the position of the star.

\newpage