\section{The Star Which Holds the Ascendant or The Lot}

If Saturn is allotted the hour\footnote{The delineations are meant to hold for \textit{any planet} ruling the Ascendant (the ``hour'' marker), or the Lot of Fortune, or any planet physically located in the Ascendant (1st House).} of the Lot <of Fortune> and is in the Ascendant, with \Mars\xspace not in opposition, the native will be fortunate in activities controlled by \Saturn. \textbf{/59P/} If \Jupiter\xspace is in aspect, he will be doubly fortunate; if \Venus\xspace is in aspect, he will be fortunate through the help of women or eunuchs. If \Mars\xspace is in conjunction or in opposition, the native will suffer disturbance and reversals. If \Mercury\xspace
shares the Ascendant with \Saturn, the native will be handicapped in his hearing.

Jupiter, when allotted the hour or the Lot and in the Ascendant, causes men to be very fortunate from youth. If \Mars\xspace is in configuration (at the same center or in trine), men will advance by means of brilliant campaigns and will win the acquisition of a livelihood. If \Saturn\xspace is also in aspect, men become exalted; if \Venus\xspace is in aspect, they become even more exalted. If \Mercury\xspace is in aspect, men are involved in exchanges.

Mars, when allotted the hour or the Lot and in the Ascendant, urges men toward the military. If \Jupiter\xspace is in aspect, the native advances in status; if \Venus\xspace is, he attains an extraordinary status. If \Mercury\xspace is in conjunction, he will accept a deposit given without witnesses, but will later deny it. If \Jupiter\xspace is in conjunction, he will acquire much property from many people, but after his death it will all revert to the royal treasury.

Venus, when allotted the hour or the Lot <and in the Ascendant>, indicates great good and makes men far-renowned. If \Mercury\xspace is in conjunction, it makes musicians. But if, given the preceding configuration, \Saturn\xspace is in opposition to them or is in a superior aspect, it robs men of what they have.

Mercury, when allotted the hour or the Lot and in the Ascendant, makes men fortunate. If \Jupiter\xspace is in
conjunction or square, men will have control of tribunals and cities. If \Saturn\xspace is in conjunction as well, the
control, honors, goods, and success will be double. \textbf{/61K/}

The Sun inheriting the hour or Fortune and in the Ascendant: if \Jupiter\xspace is in conjunction or square, the native will be fortunate. If \Mercury\xspace is also in conjunction, he will succeed through his words. If \Mars\xspace is in conjunction or square along with \Jupiter, the native will be great, a master of life and death. If, given the previous configuration, \Saturn\xspace is square or in opposition, the native will fall into mishaps and penalties.

The Moon, when inheriting the hour or the Lot of Fortune <and in the Ascendant>, makes men great, especially when it is in its own triangle. If \Venus\xspace is in conjunction or square, the native will be thought worthy of great honor. If \Mars\xspace is also with the \Moon, he will be master of life and death. If \Saturn\xspace is, he will control many districts.\textbf{/60P/} If \Jupiter\xspace is in conjunction or square, they will be great kings. If none of the above is the case, and if \Mercury\xspace is configured with the \Moon, success will be from words and special aptitudes. If \Mars\xspace is also in conjunction or square, it makes tyrants and great lords. If \Mars\xspace is in opposition to the \Moon, with no benefics in aspect, the child will be exposed; but if a benefic is in aspect, the exposed child will survive and be reared. Likewise if \Mars\xspace appears in square or is found in a superior aspect, it entangles the native in wanderings, separations, and vicissitudes. But if \Venus\xspace is in square at an angle, men will be wronged by women. If \Saturn\xspace is in conjunction in a lewd sign, men will be pimps, and if \Mars\xspace is also in the configuration, then men will hire their wives out to others. If \Saturn\xspace is square with the \Moon\xspace or is in \mned exact opposition (to the degree) to [\Saturn], the native will have an interruption of
nurture and will be abandoned by his parents. If \Mercury\xspace is square or in opposition to the \Moon, men will be contrary-minded, always in opposition, involved in slanders and accusations from a superior. If, in addition, a malefic is in the aspect or in the configuration, it will bring discredit and condemnation. \Jupiter\xspace lying \mned exactly opposite the \Moon\xspace causes sterility \textbf{/62K/} and the opposition of superiors.

\mndl[0.2cm]
In general, malefics which behold the luminaries and the Ascendant with no benefics <in aspect> make men short-lived. If the ruler of the Ascendant lies in its proper place or in its own sect, it becomes the bestower of <long> lifespans. If it is configured with the lord of the Lot <of Fortune>, the native becomes full of years and luck. If the ruler happens to be setting, the native becomes short-lived. If a malefic is in conjunction or in superior aspect with the \Moon, the infants will not survive.

\newpage