\section{The [XI] Place of the Good Daimon. Many Configurations. The Hearing and the Beholding Signs Must Also Be Investigated.}
\index{places!11@11th}
\index{planets!benefics}
If the benefics are in the Sign of the Good Daimon, located in their proper places and in their proper faces, they make men illustrious and rich from youth—even more so if they are trine from the right with the Lot of Fortune\footnote{A planet in the 11th would be in ``trine from the right'' to a Lot of Fortune in the 2nd.} or sextile with the Ascendant. If they are in a listening\footnote{The \textsl{listening} signs are most likely the \textsl{Commanding \& Obeying} signs. There are two pairs of signs in this category that are trine each  other: \Gemini-\Aquarius, \Leo-\Sagittarius. Planets in trines between these signs are \textsl{intensified}; their strength, and therefore effect, is increased.} or beholding\footnote{The \textsl{beholding} signs are most likely the \textsl{Seeing \& Perceiving} signs. There are two pairs of signs in this category that are trine each  other: \Taurus-\Virgo, \Scorpio-\Pisces. Planets in trines between these signs are \textsl{intensified}; their strength, and therefore effect, is increased.} sign they provide even more and greater benefits. 

If one of the benefics appears in opposition to the Good Daimon and its houseruler is also present, these stars bring bigger and better benefits and successes. 

If malefics are in conjunction \textbf{/63K/} with the Good Daimon, they cannot do any evil. 

It is most efficacious if the houserulers of the Lot, the Ascendant, and the Good Daimon happen to be rising or if most stars are in conjunction or in aspect with these in operative signs; they then make men glorious and extremely wealthy. 
\index{planets!\Jupiter}\index{planets!\Jupiter-\Mercury}
<If \Jupiter\, is in the Place of the Good Daimon, the native will be fortunate, possess a good income, and have many
children. If it is also the ruler of the Lot of Fortune, the native will be rich and blessed. If \Mercury\, is in conjunction with it, the native will be [an] imperial steward and will be happy in his children.>\footnote{Prof. Riley: ``The passage in brackets has been transposed from the end of chapter 8K;9P to its proper place here''}

\newpage