\section*{The IX Place of the God Sun, just before MC. The Ninth 
Place from the Ascendant. It Has Many Configurations (7K,8P)}
\addcontentsline{toc}{section}{\hspace{2em} (7K,8P) The IX Place of the God Sun, just before MC. The Ninth Place from the Ascendant. It Has Many Configurations}
\index{places!9th}
\index{planets!benefics}
If benefics happen to be in this Place and have been assigned the Ascendant or Fortune, the native will be blessed, reverent, a prophet of the great god; in fact he will be obeyed like a god.

If <benefics> are not there, and if Mercury alone is in aspect, the native will be involved in soothsaying; [he will] expound his craft to the masses\footnote{Prof. Riley: or “…the native will be involved in finance; he will control the masses through his business dealings.” (Rhetorius in CCAG 8.4 pp. 163-4)}. He will become [a] royal clerk from his middle years. But if malefics are in conjunction and rule the previously mentioned places (the Ascendant and Fortune), or if they are in aspect from the right with the Lot, the native will be a tyrant: he will found some cities; he will sack others; he will pillage many people most wickedly. 

\index{lots!Daimon} \index{lots!Fortune}
If Daimon or Fortune happens to be in the <XII> Place of the Bad Daimon, but the houserulers of the Lot and of the Ascendant are in this Place <of the God>, the native will be involved in very many evils, in travel, and will lose whatever he has gained, or he will take refuge in temples because of his desires or pains. \textbf{/64P/}

\newpage