\section{The [VII] Place of the Descendant (9K,10P)}
\index{places!7th}
\index{planets!benefics}
Benefics in this Place and ruling the Ascendant or the Lot of Fortune indicate good things for the native: inheritances, sudden acquisition of other property, and benefits from a death. \textbf{/65K/} 

If the benefics are not in their own places, men are less prosperous, but not poverty-stricken. If Mercury alone is in conjunction and in its proper face, the native will make gains in his old age and will be entrusted with cities and the affairs of kings. 

\index{planets!malefics}
If malefics are in this Place and rule the Lot or the Ascendant and are in their proper faces, the native’s life will be subject to ups and downs, especially in old age, but he will not be in poverty. He will spend the income derived from calumny and wickedness/vituperation. 

If malefics rule the Lots but are not in their proper face or in their own sect, the native will lead a wretched old age; a few will come into prisons for a time and into decrepitude and disease. If \Jupiter\, is in aspect from the right, men enter temple service because of sickness; they are troubled and suffer from hemorrhages and disease of the genitals or fingers. 

\index{planets!Mercury}
If Mercury is with \Mars\, in the Setting Sign, men become accomplices in banditry and murder; as a result they perish miserably thereafter. 

Malefics setting while out of their own signs cause suicides.

Benefics make men with much experience and those who are fortunate in old age.

\newpage