\section{The VI Place. The Place of Mars (10K,11P)}
\index{places!06@6th}
\index{places!benefic}
If benefics happen to be in this Place, the native will lose whatever he possesses; his property will not stay with him. \textbf{/64P/} He will suffer loss because of fines when advanced in years. 

\index{planets!\Sun}
If the \Sun\, is in this Place and rules the Lot of Fortune or the Ascendant, it causes the native to be condemned by the highest authority. 

\index{planets!\Saturn}
If \Saturn\, rules <these places>, the native will be a wanderer, prone to give offense, and he will flee his homeland, barely keeping himself alive. 

\index{planets!\Jupiter}
If \Jupiter\, rules the Lot or the Ascendant, the native will lose his property in civil suits. 

\index{planets!\Venus}
If \Venus\, rules\footnote{The ``if...rules'' applies to the Lot or Ascendant as stated previously, same for the remaining paragraphs.}, he will suffer trials and penalties because of a woman. Such men, being disagreeable, are insensible to love. 

\index{planets!\Mars}
If \Mars\, rules, it causes wounds and diseases \textbf{/66K/} in the limb indicated by the sign <where Mars is>, and it makes naked beggars who come to a miserable end. 

\index{planets!\Mercury}
If \Mercury\, rules the Lot or the Ascendant, it makes plotters, thieves, slanderers, and men who are reviled in public. 

\index{planets!\Moon}
If the \Moon\, is in this Place, the native will be a slave, helpless—unless the rest are in conjunction with the \Moon: if the other stars are situated favorably, the native can be free and respectable, even though the \Moon\, is in <the VI Place of> Bad Fortune.

\newpage