\section{The V Place. Many Theorems (11K,12P)}
\index{places!5th}
\index{planets!benefics}
If benefics hold the Ascendant or the Lot of Fortune, the native will be great, will lead the masses, and will make laws for them.

\index{planets!Venus}
Venus will be especially gracious if it rules the Ascendant or the Lot. Especially if Venus is in its proper face or in its own place, it makes men wealthy and honored. \mndl The same if true for all the stars: if they govern the Ascendant or the Lot, they produce the good that is appropriate to their nature and to Good Fortune. 

\index{planets!Mars}
If Mars happens to be situated as specified, men will be rulers of all sorts of places: governors, tyrants, and masters of life and death—not only over lesser men but also over men of
high rank. 

\index{planets!Saturn}
If Saturn is in this Place, men will be masters of estates, flocks, and herds; they will establish towns and villages. 

\index{planets!Sun}
If the Sun is in this Place, men will be friends of great lords, associates of kings, governors of temples. 

\index{planets!Mercury}
If Mercury is in this Place men will be successful through words and worthy of much money. 

\index{planets!Moon}
If the Moon is configured well, holds the Lot or the Ascendant, and is in this Place along with its <the \Moon’s> houseruler, the native will be long-lived, \textbf{/65P/} growing old in prosperity. 

\index{planets!benefics}
\mndl The benefics help greatly while passing through this Place; the malefics cannot do harm. \textbf{/67K/}

\newpage