\section{The III Place. The Place of the Goddess Moon (13K,14P)}

If the Moon is in this Place, is assigned the Ascendant or the Lot, and is in its proper face, the native will be great and a master of many good things. He will rule a city; he will give orders to many men; he will be obeyed; and he will be master of treasuries. 

If the Sun should also be in this Place with the \Moon\xspace when the \Moon\xspace is just past new, the native will be a priest or priestess of the great goddess and will have a unsurpassable livelihood. 

If Saturn is here with the \Moon, the native will be subject to God's wrath, will be punished, will often come into trials, and will blaspheme the gods many times because of what has happened to him. 

If Jupiter is with the \Moon, the native will be a prophet, fortunate, rich, famous, and will be master of many good things. 

If Mars is in conjunction with the \Moon, he will be successful, but wicked: he will embezzle deposits, will get his living through the murder or robbery of others, and will travel widely. If \Mars\xspace is appropriately situated in its own faces, the native will be a governor of towns and cities (depending on the character of the nativity), but he will also be unjust, a perjurer, and covetous of others’ goods. He will perish suddenly because of the wrath of authority. \textbf{/68K/} 

If Venus in her own places rules the $<$III$>$ Place of the Goddess and the Lot of Fortune \textbf{/66P/} (especially for night births), the native will be rich and well liked by women. Some will be royal governors, rulers of towns, because the goddess $<$Venus$>$ has been assigned the Lot of Fortune in the House of the Goddess. 

If Mercury is with the \Moon\xspace in the Sign of the Goddess and rules the Lot of Fortune or the Ascendant, the native will foretell everyone’s future and will share in the mysteries of the gods.

\newpage