\section{The II Place, Called the Gate of Hades. The Place Rising After the Ascendant (14K,15P)}
\index{places!2nd}
\index{planets!benefics}
\index{planets!malefics}
In this Place the benefics do no good, the malefics make men sluggish and injured, unable to wade through their lives to the end. 

\index{lots!Fortune}
If the Lot is in this Place, and if malefics are the houserulers of the Lot or the Ascendant, the native becomes a cemetery guard, living his life outside the city gates. 

\index{planets!Saturn}
Saturn ruling the Lot of Fortune and in this Place makes dead-souled men, those weak in body and suffering
chains/imprisonment for a long time, until the completion of the chronocratorship of the star. 

\index{planets!Jupiter}
Jupiter in this Place causes expenditure of the native’s resources until the end so that nothing is left; it brings the gift of children, but not with good fortune. 

\index{planets!Mars}
Mars in this Place and houseruler of the Lot and of the Ascendant makes men who are prone to give offence, are subject to penalties, and whose actions are hindered. Some become captives, but are later freed. If \Mars\, (in its own degrees or signs) is in charge of the Lot of Fortune, when the Lot is in this <II> Place, men become jailers, making a livelihood in prisons or a living among the cells. 

\index{planets!Sun}
If the Sun is in this Place, and if it is houseruler of the Lot or the Ascendant, and in its own house, <with \Mars\, being in the Ascendant> or in the places of \Saturn, the native will lose his sight in the chronocratorship of \Mars, will be plundered of his ancestral property, and will become a beggar. 

\index{planets!Venus}
If \textbf{/69K/} Venus is in this Place and is houseruler of the Lot or the Ascendant, it will bring public, disreputable occupations if \Venus\, happens to be at its morning rising. 

\index{planets!Mercury}
Mercury in this Place and located under the rays of the \Sun\, makes stupid, illiterate men. If it is also ruler of the Second Fortune (the one called Daimon), it makes men deaf and dumb. If it is rising, men engage in curious arts, attempting what they have not learned <from others>, \textbf{/67P/} but still succeeding in their science. 

\index{planets!Moon}
If the Moon is in this Place with \Saturn\, in the Ascendant, the opposite happens: the native will suffer from cataracts and glaucoma.

\newpage