\section{The Trine Influences of the Stars on Prosperity or Poverty. The Configurations of Trine, Sextile, and Opposition (16K,17P)}
\index{planets!aspects}
\marginnote{\Jupiter \Trine \Sun}[0.2cm]
\index{planets!Jupiter!aspect}
Jupiter trine with the Sun indicates great and glorious men. If the \Sun\xspace is in the Ascendant, the
indication applies to the father and to the nativity. If it is at an angle, it applies to the father: it indicates that he is famous, but less so than under the previous configuration. It indicates nothing unusual for the nativity if no other factor improves the outlook. 

\index{planets!Saturn!aspect}
\marginnote{\Saturn \Trine \Sun}[0.2cm]
If Saturn is trine with the Sun from the left and the \Sun\xspace is in the Ascendant, the rank will be higher: such men will own much land, have many estates, and become rich. If \Mars\xspace is also in aspect along with \Jupiter, the configuration indicates tyrants; especially if the \Sun\xspace is in the Ascendant, such men will control many districts and armies. If \Saturn\xspace \footnote{This doesn't make sense as \Saturn\xspace is already \Trine\Sun. Maybe he means if \Saturn\xspace also aspects \Mars\xspace or \Jupiter?}
is also in aspect, the native’s father will be great, the leader of arms and armies (if indeed the rest of the aspects work \textbf{/70K/} towards his greatness), but he will not be a tyrant, warlike, or ferocious. 

\index{planets!Mars!aspect}
\marginnote{\Mars \Opposition \Sun}[0.2cm]
If Mars is in opposition to the Sun, with \Jupiter\xspace and \Saturn\xspace trine with the \Sun\xspace from the right, the native will lead the masses magnificently and with high rank. 

\index{planets!Saturn!aspect}
If Saturn is in opposition to the \Sun\xspace (under the stated conditions), the native will be opposed by family and friends, but he will prevail and subdue
them. 

\marginnote{\Saturn\xspace \Mars \Trine \Sun}[0.2cm]
If \Saturn\xspace and \Mars\xspace are trine with the \Sun, with \Jupiter\xspace in opposition in its own degrees or signs, the native is imperious and noble. If the configuration is sextile, the forecast is less <spectacular>.

\index{planets!Venus!aspect}
Venus \marginnote{\Venus \Sextile \Sun} sextile to the \Sun\xspace in the morning sky indicates that the father and the native will be charming and distinguished. \textbf{/68P/} If \Venus\xspace is configured in Good Daimon or in Good Fortune, the native will be thought worthy (by women) of the purple and of golden ornaments.

\index{planets!Saturn!aspect}
Saturn \marginnote{\Saturn \Square \Sun} square with the \Sun\xspace and on the left harms the ancestral property while the native’s father is still alive, especially when \Saturn\xspace is in feminine signs or in opposing degrees. If \Saturn\xspace is in opposition, the situation is much worse: the native will be overwhelmed by wounds and suffering, and will be betrayed by relatives and clients. If \Saturn\xspace is on the right, the forecast will be worse. If it should be in the Ascendant or at MC, the reversals will be less.

\index{planets!Mars!aspect}
Mars \marginnote{\Mars \Square \Sun} square with the \Sun\xspace is bad for the father and the native. It brings injuries and suffering. \Mars\xspace in opposition or in afflicted signs or degrees causes injuries to the joints. If \Mars\xspace is square on the right in the tenth <sign from the \Sun>, worse will happen: in addition to everything else, he will go insane.

\index{planets!Jupiter!aspect}
Jupiter \marginnote{\Jupiter \Square \Sun} square with the \Sun\xspace and in base degrees or signs becomes unpleasant: <this configuration> ruins the star’s good influence and turns it to the opposite. But, \Jupiter\xspace in glorious degrees or signs, and especially at an angle, is productive of rank and wealth. 

Jupiter \marginnote{\Jupiter \Opposition \Sun} in opposition to the \Sun\xspace in most unpleasant: not only is all of Jupiter’s good influence quenched, but the native will feel the anger of superiors and the hostility of the masses. The \mndl exact-to-the-degree positions of square and opposition are
harsh.

\index{planets!Mars!aspect}
For night nativities, Mars \marginnote{\Mars \Trine \Sun} trine with the \Sun, especially when in \textbf{/71K/} feminine signs and on the right, indicates great and famous men, masters of life and death—provided that the rest of the aspects in the nativity agree. In addition, if \Jupiter\xspace is trine to the right, it makes great dynast[y]s, rulers of cities and leaders of the masses. If the nativity is female and \Venus\xspace is in conjunction, the native will be a queen and will have power over many districts; she will become a benefactor and be unsurpassed. For male or female nativities, if the one star occupies its proper place and the other happens to be in its own triangle, there is
no opposition: they become king of kings, provided the one <star> is houseruler and the other is co-houseruler and master of the nativity, and that they both rule the Lot of Fortune and the Ascendant. If they are in masculine signs, fortune will be less, in fact much worse. \index{aspects!sextile} Sextile \mndl configurations have a weaker effect, both for good or for the opposite.

\ldots

\index{planets!Mars!aspect}
For day nativities, \textbf{/69P/} if Mars \marginnote{\Mars \Square \Moon} should be square with the \Moon\xspace while on the left and in another’s degrees or signs, it will be the cause of many reversals and afflictions for the mother, as well as reduction in rank. Men will be subject to travel; some become soldiers, toilsome and violent. These things happen, provided that the nativity is not base-born in other respects and that the master of the star, or its helper, or a fellow sect-member are not in places which do not have the Ascendant in aspect. If this condition does obtain <the Ascendant is not in aspect>, men become captives and die by execution. 

If Mars is in opposition (the other configurations being the same), bad results are stronger and more difficult to avoid. Indeed if it should appear square to the right, men suddenly lose everything. (The difference between square and opposition is great!) \mndl If Mars is in Aries <its sign> and the \Moon\xspace in Cancer <its sign>, the results are quite different and are like those for trine. Likewise if \Mars\xspace is in Scorpio <its sign>, in opposition to the \Moon\xspace in Taurus, not only will there be no reversals of fortune, but in fact the stars will produce success and high rank.

\index{planets!Venus!aspect}
For night nativities, Venus \marginnote{\Venus \Trine \Moon} trine with the \Moon\xspace and in feminine signs makes men charming and fortunate. Some rule the masses \textbf{/72K/} and are thought worthy of the purple and of golden ornaments—depending on the greatness of the nativity. They become philosophers, artists, scholars, and members of
the circle of king’s friends. If both <\Venus\xspace and the \Moon> indicate the the birth is “royal,” because one is
the houseruler and the other the master of the nativity, the configuration is dictatorial: men become king of kings, famous, merry. When sextile with each other, they have a more moderate power. When <the stars> an equinoctial sign lies between; even more so, if the configuration beholds \Pisces\xspace and \Taurus.

Venus \marginnote{\Venus \Square \Moon} square with the \Moon\xspace makes men successful, charming, and wealthy, all that the trine configuration provides—especially if \Venus\xspace is in its own sign or degree—but with some ups and downs. \mndl What these stars give is easily lost. If the stars are not in their own signs, not in their own sect, or are in contrary degrees, they become the cause of violence, unsteadiness, and infamy due to women or \textbf{/70P/} vice.
If they are in opposition under these circumstances, worse results.

\index{planets!Mercury!aspect}
For day nativities, Mercury \marginnote{\Mercury \Trine \Moon} as a morning star trine with the \Moon\xspace makes men inventive, successful, clever, and excitable. If the nativity is quite elevated, it makes secretaries of kings, rulers of cities or districts, scholars, orators, mathematicians.

Mercury as an evening star, especially for night births, makes erudite men, philosophers and initiates of the mysteries. If the birth is lofty because of the other stars’ <influences>, it makes noble men, those honored by the masses and acquainted with the great and with kings. \Mercury\xspace does this by being co-ruler with the star which supplies the primary influence.\footnote{``as a helper it causes these effects--marginal note [Riley]''}
If it is in an inoperative place, it cannot apply any of its own influence. (\mndl In general it will be seen of all nativities that any star has the same effects in \Trine\xspace as it does when in \Conjunction\xspace in the same sign.)

\Mercury\xspace sextile with the \Moon\xspace has a duller and weaker influence than do the previous configurations. \Mercury\xspace \Square\xspace makes men keen and shrewd, but this keenness turns to criminality and the men become \textbf{/73K/} malicious, slanderers, acting with trickery and violence, inspired by nothing healthy. In addition to the previous <malign> influence, if the two are in \Opposition, the native is contrary-minded and ungracious in his activities, and so is harmed by what befalls him.

Mercury \marginnote{\Mercury \Trine \Saturn} trine with \Saturn, especially if they are in their own triangles, makes royal stewards, procurators, and those who supervise shipping, estates, and similar operations. They become shrewd,
intelligent, and single-minded. \Mercury\xspace and \Saturn\xspace square with each other make everything dull: they make men sluggish, quarrelsome, and self-willed, slow in action, and feeding off calumny, treachery, trickery, and violence. They also become practically mute and hard of hearing. \Mars\xspace in aspect with \Saturn\xspace
or \Mercury\xspace cancels the previously mentioned handicap in speaking, if they are not in their houses or terms,
if they are not exchanging domiciles, if the \Moon\xspace is not in aspect from the right, if they have no contact with it <the \Moon>, and if they are not the overall houserulers or co-houserulers. \mndl That’s how strong these slight changes are! If they are in \Opposition, they separate sisters by death.

Mercury in the Ascendant or at MC makes young men \textbf{/71P/} learned, intelligent, educated. They do
not, however, get the benefits of their talents, because the gifts of these stars will be frozen by the opposing configuration of the stars. If they are precisely in \Opposition, to the \mned degree, their effects will reach much further: the native will be handicapped in hearing and in speech; he will take refuge in temples, prophesying
or even being mentally distracted.

Mercury \marginnote{\Mercury \Trine \Jupiter} trine with \Jupiter\xspace is indicative of great deeds, especially if \Mercury\xspace is at morning rising. Men become secretaries of kings, of cities, or of the masses, or they become financial officials. Since \Mercury\xspace is
altogether concerned with occupations and provides the active influence, the native will have a high status and the possession of a livelihood, especially if \Mercury\xspace is in operative signs. If the stars are \Sextile, \textbf{/74K/}
they have the same effects, but to a lesser degree. If they are \Square\xspace and configured well, to some extent
they bring possessions and status, but with hatred. If they are configured badly, they bring ruin along with hatred, and the opposition of superiors. If the stars are in \Opposition, they bring even greater slander, and men are at cross purposes and suffer ups and downs. If the stars are in \Opposition\xspace in the Bad Daimon, men will be crushed by the supreme authority, they will feel the effects of mass insurrections, and they will have few brothers, or will have quarrels with their brothers, children, or relatives.

Mercury \marginnote{\Mercury \Trine \Mars} trine with \Mars\xspace or sextile to the right is indicative of quite varied activities: sometimes it makes secretaries, sometimes merchants, translators, mathematicians, lawyers, philosophers—all of them malignant, bitter, intelligent, lying. This star also makes arms instructors and gladiators. If \Jupiter\xspace is configured with these, especially in operative places, it makes military men, often augurs, sacrificial priests,
seers, and those who know more than men should. \Mercury\xspace \Square\xspace causes even more varied activities than has been mentioned: magi, wanderers, sacrificial priests, doctors, astrologers, demagogues, bankers, counterfeiters, forgers, those making their living by crime, violence, and trickery. Men become thieves, perjurers, atheists, and those who prey on their fellows, are greedy for gain, who are defrauders—in short, those who have nothing admirable in them. As a result, they are involved in many evils and \textbf{/72P/} have experience of captivity, exile, and prison. <\Mars\xspace and \Mercury> cause even worse, especially when they are in inoperative places or degrees. If both are at IC or in the Descendant, or if one is in the Descendant while the other is at  IC, they cause murders; the native will be an accomplice and will make his living as a
bandit. A few will be fratricides and their final end will be violent, especially if the stars include the \Moon\xspace in their configuration. They will die violently/as suicides and will lie unburied. If the stars are in fourfooted signs, men will be taken by beasts; if in anthropomorphic signs, by bandits; if in \textbf{/75K/} solid signs, men will die by falls from heights; if in fiery signs, from fires; if in moist signs, by shipwreck; if in tropic
signs, in the arena. \mndl The stars do the same things when changing domiciles or in conjunction. 

If one is houseruler and the other is master, and if \Mercury\xspace is \Sextile\xspace or in \Conjunction\xspace with \Venus, it will make the native intelligent, charming, artistic, fond of games, endowed with a sense of humor; sometimes poets, songwriters, declaimers, actors, mimes; sometimes athletes and victors in sacred games. These stars are productive of quite varied occupations. If the nativity is feminine, the women become musicians, promiscuous, living like prostitutes, of a literary bent, fond of recitations.

\ldots

\index{planets!Venus!aspect}
Venus \marginnote{\Venus \Trine \Saturn} trine with \Saturn\xspace makes men severe, humorless, supercilious, rough in love and promiscuous, yet lying with base-born or elderly women, or with prostitutes. These men lie with the wives of their brothers or patrons, with those of their fathers, or with their stepmothers. Their wives sneak off and lie with their husbands’ slaves or friends. \mndl It is, of course, necessary to note that predictions can change greatly
in accord with the changes of sign and degree: the same configuration, even if the stars occur together, can
indicate sordid men, those sleeping in their lusts and sometimes promiscuous; but often it can also indicate
those who are unaffected by love, who only take enjoyment by themselves. <\Venus\xspace and \Saturn> \Square\xspace are much worse: the effects mentioned for the trine configuration become worse. Men take prostitutes as wives, and they become loathsome and depraved. It is even worse if \textbf{/73P/} the configuration is in the Descendant or at IC. The deterioration noted above becomes even worse if \Mars\xspace in in \Conjunction, \Square, or \Opposition: men then act shamefully and are denounced by everyone. Often because of this they become a subject of scandal, are imprisoned, and meet a bad death. If these stars are in “lurking” signs or degrees,
\textbf{/76K/} men enjoy impure passions and unnatural pleasures. If these stars are \Sextile\xspace with each other, their effects are the same as those attributed to the \Trine\xspace configuration, but dim and weak. If both are at morning rising in the East, they masculinize women, so that the women not only act like men in their daily life, but
they even do the work of men when lying with other women. If these stars are evening stars, they feminize men: sometimes men serve as women when lying with men, but often they lose their sex organs.

\index{planets!Saturn!aspect}
Saturn \marginnote{\Saturn \Trine \Jupiter} trine with \Jupiter\xspace indicates a favorable configuration. These stars make men landowners, masters of grainland and vineyards, grainfarmers, constructors of buildings, villages, and towns—but they are austere and supercilious. If the configuration is more exalted, with \Mars\xspace in aspect from the right
\footnote{``as well as the sun and moon - a marginal note [Riley]''},
\Saturn\xspace and \Jupiter\xspace make men generals, leaders of land and sea forces, and they raise a few men to the
kingship or to tyranny. If the configuration happens to be in the triangle of \Saturn\xspace <\Gemini\xspace \Libra\xspace \Aquarius>, especially if \Jupiter\xspace is in \Aquarius\xspace with \Mars\xspace turned away, the stars make men humble and fearful, not brilliant in anything or sharing in any office, but rather choosing a retired, rustic life. \mndl The variations in occupations occur in accord with the differences of sign and place—but the stars do have the same effects when they are together in operative signs.

Saturn \Square\xspace with \Jupiter\xspace dulls the good influence of \Jupiter, especially if \Saturn\xspace is on the right and rising. Then men succeed with great difficulty, they are subject to penalties, they make gains only with
toil and pain, and they suffer loss in their children: some are childless, others see the deaths of their children. The Place of Brothers is damaging to them: these stars separate close, loving brothers by death and make the other brothers hateful and vicious, especially when the stars are not at the angles. When in opposition, these stars are most harsh and bring misery and setbacks.

\textbf{/77K;73P/} Saturn \marginnote{\Saturn \Trine \Mars} trine with \Mars\xspace points to those who are insecure in their livelihood and unable to endure hardships. They are stupid but violent in their actions. They either have few children or lose those that are born. These men become captives or are injured. \Saturn\xspace \Square\xspace <with \Mars> is much worse: their children are destroyed, also their brothers; brothers are separated from each other by hatred; they become incorrigible or are injured. They are prone to give offense in their actions and are encompassed by the hostility of great men and are plotted against by them. This configuration falls into great danger: men die violently from attacks of bandits or the enemy, or by shipwreck. A few go into captivity. They are often endangered by fire or sword. If \Saturn\xspace and \Mars\xspace are in \Opposition, they make the previously mentioned influences much stronger. In addition to the above, men become poor, distressed, unlucky; a few become porters, beasts of burden; they have toilsome and despised jobs. 

There \mndl is, however, much variation in these configurations, not only with respect to the individual characteristics of the signs and degrees, but also with respect to the greatness of the nativity. If \Jupiter, the
\Moon, and the \Sun\xspace do not behold this configuration, the birth is lowly. If they are in aspect from the right
and one is the master of these stars and the other is the houseruler, then the previously mentioned effects happen: quite bad in <the IX Place of> the God and <the III Place of> the Goddess; to a lesser and fainter degree in <the XI Place of> Good Daimon and <the V Place of> Good Fortune; but worse and more intense in <the XII Place of> Bad Daimon, <the VI Place of> Bad Fortune, the Inactive and Shadowy Place. If the nativity is exalted and royal\ldots

\index{planets!Jupiter!aspect}
Jupiter \marginnote{\Jupiter \Trine \Mars} trine with \Mars, if one is the houseruler and the other the master, indicates great men, leaders and dictators, especially when these stars are in their own signs, triangles, or degrees, in operative signs, or when they have exchanged domiciles or terms, especially if they rule the Lot of Fortune or its houseruler. They make great affairs: kings, those in charge of the military (navies or armies), those who rebuild cities
\textbf{/78K/} or those who destroy them. When \Sextile, these stars are less strong, just as with the former configurations, but if they are at an \mndl angle, they indicate that the evils which are mentioned do not loom over the native but \textbf{/75P/} over others. They become bunglers of army and naval battles; they become bandit chiefs, violent leaders, sadists, drinkers of blood. If the nativity is professional, e.g. a notary or a lawyer, the native becomes an informer. If the configuration includes \Mercury, and if the \Moon\xspace has contact with \Mars, the situation is quite terrible: such men become worse than wild beasts. \Jupiter\xspace \Square\xspace with \Mars\xspace is strong, if one is in the Ascendant and the other is either at MC or in <the
XI Place of> Good Daimon. This configuration will be stronger than that of \Trine, especially if a tropic
sign is between. (If \Jupiter\xspace and \Mars\xspace are in the same sign, they are even stronger.) When \Square, they
have the same effect as when \Trine, but with dangers and setbacks. When in \Opposition in inoperative signs, they become harsh. If the rest of the nativity’s factors point to leadership for the native, he will fall into great dangers and be betrayed by his relatives and by enemies. \mndl If neither star is houseruler or master or co-houseruler, the \Trine\xspace configuration is mediocre. The native becomes a military/government official. If high rank seems to be hinted because of the other stars which are helpers or have the power of helpers, the native will advance in rank. These stars make men rulers of cities and judges on the bench. If the horoscope is military because of the \Sun, the \Moon, or \Saturn, the native becomes a decurion and a centurion, <a commander> in short campaigns and of small cities. If the horoscope is base because of the the \Sun, the \Moon, and the rest of the stars, or if \Mars\xspace and \Jupiter\xspace are \Trine\xspace with them, men become base: slaves \textbf{/79K/} of officials, subordinates of governors; they are frequently hunters, gladiators, and weapon makers. \mndl These things are indicated by the alteration of the signs’ <positions>: if they are at the angles, they cause greatness from youth; if they rise just after an angle, they cause greatness beginning in adulthood; if they rise before an angle, they cause lowliness and degradation.\textbf{/76P}

\newpage