\section{The Lot of Fortune as the Ascendant (17K,18P)}
\index{lots!Fortune}
Having explained the trine arrangements, I will move on to the Lot of Fortune\footnote{``And of Daimon; concerning prosperity - a marginal note [Riley]''}. 

First of all it is necessary to determine the Lot of Fortune and to see in what part of the cosmos it is located: at an angle, just following an angle, or just preceding an angle. Likewise look for the ruler of the Lot. If it is in the Ascendant during the day or is in some other operative place, with the \Sun, the \Moon, or benefics in aspect, it will make the native noble, distinguished, and fortunate. Its effects are more moderate when it is found at the other angles or just following an angle. \index{places!declines} \mndl When it precedes an angle, assume <the nativity to be> stillborn or abandoned—these are the disagreeable places which bring crises and ruin.

\index{places!Fortune houses}
In addition, after finding the Place which has been assigned to Fortune, examine the points square with it and the other aspects, just as with the angles in the natal chart. The Lot itself will be equivalent to the Ascendant and will mean “Life;” the tenth place from it will be equivalent to MC and will mean “Rank;” the seventh will be the Descendant; the fourth IC. The other places will have the same effects as the <original> XII Places. 

Some astrologers have mystically hypothesized that the astronomical Ascendant and the points square with it are the Cosmic Angles, while the Lot and the points square with it are the Natal Angles, and they have revealed this in their treatises as follows: “When assigning the influence of the
Lot among all the multifarious configurations of the angles\ldots \textbf{/80K/} neither the tropic nor the solid nor the bicorporeal signs will have the same overall effects. It is therefore necessary to examine the aspects or the
conjunctions of the stars relative to the Lot: for example, a benefic in conjunction or in aspect with the Lot will be a sign of good and a giver of property. A destructive star <in conjunction or in aspect> will be responsible for loss of goods and sickness of the body. \textbf{/77P/}

\newpage