\section{The Lot of Fortune and Daimon. Their Influence on Prosperity and the Outcome of Actions (19K,20P)}
\index{lots!Fortune} \index{lots!Daimon}
For the reason mentioned above, the Lot of Fortune and Daimon have great influence on undertakings and their outcomes. The former gives information about matters concerning the body and concerning the work of hands. Daimon and its ruler give information about spiritual and intellectual matters and about the activities of giving and receiving. It will be necessary to examine the places and the signs in which their houserulers are located and to correlate their natures, in order to learn the type of activity and fortune and the quality of activity <to be expected>. Nativities will be considered glorious, distinguished, and vigorous \textbf{/78P/} if they are from the \Sun\, and \Moon, and if benefics are in conjunction or incline to these places or houserulers. The nativities from \Saturn\, and \Mars\, are mediocre, inglorious, ruined, or adverse. 

It is best to find the ruler of Daimon at the Lot of Fortune or at its 10th Place (=Midheaven)\footnote{So that it is at MC relative to the Lot. Note that <the author> defines “to be at an angle” as the same or as equivalent to “to be in its proper place.” In the same way he makes “to just preceed an angle” equivalent to “to not be in its proper place.” “Having malefics in aspect” is in the same category as “being turned away” i.e. in the 8th place <relative to the Lot> - a marginal note [Riley].}. If so, then the nativities are illustrious and
distinguished. 

If it is in its proper place or at another angle, the nativities will be as distinguished and vigorous as they can be under the circumstances. 

If it is turned away from its proper place, just precedes an angle, or has malefics in aspect, it indicates exile and distress abroad. 

If it is in conjunction with a benefic or has benefics in aspect, the native will live abroad for a long time, having a varied and fluctuating livelihood. 

If \textbf{/82K/} it has a malefic in aspect, the native will become needy, destitute, experiencing trials and imprisonment. Likewise if <the ruler of the Lot or of Daimon> is in opposition to this place, it indicates men who reside abroad and become distressed. Often the goods of such men are not inherited by their own families, but by strangers.

\newpage