\section{The 11th Place [Relative to the Lot] of Fortune and its Influence on Prosperity (20K,21P)}
\index{places!Fortune houses!accomplishment (acquisition)}
We have found the 11th Place <relative to the Lot> of Fortune to be the Place of Accomplishment\footnote{Both Robert Schmidt and Dorian Greenbaum translate this as the \textsl{Place of Acquisition}.}, the bestower of property and goods, especially if benefics are in this Place or in aspect. 

\index{planets!Sun} \index{planets!Jupiter} \index{planets!Venus}
The Sun, Jupiter, and Venus provide gold, silver, jewelry, and very great property, as well as gifts from the great and from kings. They cause men to spend money on the masses for noble purposes and to become benefactors of many
people. 

\index{planets!Moon} \index{planets!Mercury}
The Moon and Mercury bring ups and downs of livelihood, bringing changes and sometimes making men liberal and generous, at other times needy and burdened with debts. This happens because of the \Moon’s waxing and waning, and because \Mercury\xspace shares qualities of good and bad. 

\index{planets!Mars}
Mars takes away what was gained and possessed, causing reductions, thefts, burning, trials, confiscation for public or royal use, or proscriptions \textbf{/79P/} and condemnations. If, however, the nativity is in government or otherwise distinguished, then men will become successful due to an <astrological> impulse, from violent and dangerous action, and from theft—provided that the star is in its proper place, Even so, the star will make the occupation risky and will cause losses. 

\index{planets!Saturn}
Saturn when configured in its proper places makes men rulers of estates and property; if out of place and in the wrong sect it brings disaster, ruin, shipwreck, poverty, and
debt. \Saturn\xspace with \Mercury\xspace and \Mars\xspace forecasts men who are abused by the onslaughts of trials or of criminals, or because of religious or violent matters. \Saturn, \Mercury, \Mars, and \Venus forecast men who are wronged by poisons or by females, and who are accused. \Saturn, \Mars, \Mercury, \Venus, \Jupiter, and the \Moon\xspace forecast men who benefit from legacies and who profit from shipping, overseas trade, or moist matters. \textbf{/83K/}

\index{planets!Saturn} \index{planets!Mars}
In general, Saturn and Mars at MC or rising just after MC and ruling the Lot and the Place of Accomplishment indicate exile.

\mndl [0.2cm]
It is necessary to review the nature of each star and to make predictions according to its specific contribution and property relative to each other star. It is not just the stars in conjunction with the Place of Accomplishment which supply the indications previously mentioned. The sign itself will be influential according to the star’s nature, as well as its own.

\newpage