\section{Notable and Distinguished Nativities. Also Ignoble and Debased Nativities (22K,23P)}

I must append the following powerful places in order to clarify the topic of in notable and distinguished nativities. 

\index{delineation!notable}
If the \Sun\, and the \Moon\, are in operative signs and are attended by most of the stars which are rising, with no malefics in opposition, they make fortunate and notable nativities of governors and kings. The same is true if their rulers happen to be at an angle. 

\index{delineation!SAN}
\index{delineation!fortunate}
If the sign of the new or full moon or the ruler of this sign happens to be in the Ascendant or at MC, the native will be fortunate. 

\index{delineation!ruin}
If the \Sun\, or the \Moon\, or most of the stars are found at IC, the native will be distinguished and rich, but <the stars> will ruin his life terribly or involve him in hatred, lawsuits, and slander.

Since \mndl we wish to make very clear judgments about the Place/topic of prosperity, I will explain it further by citing many proven methods. Each planetary configuration is effective in its own way, but when comparing one with another, you will find that one elevates the native’s rank when it is exalted, another
utterly overthrows it when it is afflicted. Therefore we append this discussion to reinforce <our teachings about> the previously mentioned pattern of influences, not to abandon them.

\subsection{\textit{[Interperating Fortune, Daimon, Basis, and Accomplishment]}}
\index{lots!Daimon}
\mn{Lot of \\Daimon}[0.3cm]
So it will be necessary to calculate the effects of the Lot of Daimon in the same way we described for the Lot <of Fortune>. For day births, this Lot is found by determining the distance from the \Moon\, \textbf{/84P/} to the \Sun\, (for night births, from the \Sun\, to the \Moon), then counting this distance from the Ascendant\footnote{By day: Asc + (\Sun\,\, - \Moon). By Night: Asc + (\Moon\,\, - \Sun), essentially the reverse of the Lot of Fortune calculation}. Now examine the ruler of the Lot and its place—whatever that happens to be. 

\index{lots!Basis}
\mn{Lot of \\Basis}[0.3cm]
Do the same for the Lot of Basis: it is found by determining the distance from Fortune to Daimon <for day births> or from Daimon to Fortune <for night births>, then counting that distance from the Ascendant. \textbf{/88K/} (The distance will not exceed the number 7 <=7 signs> for night or day births but it is necessary to take the distance from the nearest Lot to the other Lot\footnote{Take the \textsl{shortest} distance between the two lots. This results in the Lot of Basis always falling below the horizon}.) Then determine the place and its houseruler.

Now then, if the houserulers exchange places—i.e. if the ruler of the Lot of Fortune is in the Lot of Basis, the ruler of Basis is in the Lot of Daimon, and the ruler of Daimon is in the place of Fortune—the native is fortunate, royal, noted. 

If the ruler of Basis, together with the ruler of Daimon, is in the place of Daimon, the native is fortunate and great-hearted. 

If the rulers of Daimon, of Fortune, and of Basis are in
their proper places, in such cases as well the native is fortunate. 

If Daimon \mn{Daimon} is in conjunction with the \Sun\, and its ruler is rising, the native is fortunate. 

Likewise if \Venus\, rules Fortune, Daimon, or Basis and is found to be rising and in its proper place, the native is fortunate. If its \textsl{[\Venus's]} ruler is in Basis and the \Moon\, is in conjunction with it, the native will be fortunate and distinguished. If its \textsl{[\Venus's]} ruler is in Daimon and the \Sun\, is in conjunction with it, the native will be fortunate, distinguished, and dictatorial.

If \Mars\, is found to be in Daimon and in the places of the \Moon, with the \Moon\, in conjunction, the nativity is ruling, governing, and distinguished. 

If \Mercury\, is found in Daimon, rising, and with benefics in aspect in the places of the \Moon, the native will gain fortune from letters and education; he will have
many friends and be renowned, be thought worthy of honors, gifts, and high rank, and will be called blessed by many. 

If \Jupiter\, rules Daimon with \Mars\, in superior aspect, the native will not suffer misfortune, but will be vigorous and distinguished. He will, however, meet with reverses, be ruined, and experience arrest and exile. If the ruler is in Daimon and is rising with the \Moon, the native will be fortunate, rich, and generous. 

If the \Sun\, is in Daimon, in its own sect, and with its houseruler in its proper place, the native will be distinguished, elegant, and will have many friends. If it is in another place, the native will be fortunate after the chronocratorship of its adversary\footnote{Schmidt translates this as ``if in the sect of the other, he will be fortunate later \textsl{[in life]} after times of adversity'' (VRS2 p44)}. \textbf{/89K;85P/}

If the rulers of Daimon and of Fortune are found in the place of Basis, with the houseruler in conjunction, the nativity will be illustrious and renowned. 

Likewise if the rulers of Basis and of Fortune are found in Daimon, with the houserulers in conjunction, the nativity will be great and fortunate. 

Men who have the rulers of Fortune and of Daimon at morning rising in their proper places, with the \Sun\, and \Moon\, in aspect, will become famous and distinguished. Associating with kings and priests, they will be thought worthy of gifts and high rank. 

\subsection{\textit{[Unfortunate Indications]}}
If \Venus\, (or any one of the other stars) is found to be ruling the Lot <of Fortune> or Daimon along with the \Sun\, and the \Moon\footnote{Does this imply that the \Moon\, always has a share in the rule of Fortune and the \Sun\, in Daimon? That their condition but be taken into account along with the Lot ruler?}, and is not in its proper place, but is unfavorably situated, the native will have hard luck and be ineffective in his efforts. If some of them are in their proper places, the native will associate with great men, will be at court, and will receive positions of trust, but in the matter of women he will be grieved and childless.

\index{lots!Accomplishment}
If the rulers of Fortune and of Accomplishment \mn{Accomp-\\lishment} do not happen to be in their own places, exaltations, triangles, or degrees, although they are at angles or proceeding with their proper motion, then they ruin nativities, especially when malefics are in aspect or in opposition to these places. 

If benefics happen to be at angles, rising, and proceeding with their proper motion, they make the native illustrious and famous. 

If the stars just follow an angle, the native lives off his own revenues.

If Accomplishment is afflicted, even though the Lots of Fortune, Daimon, and Basis are favorably situated, men lose their property in the course of their youth. 

If Fortune is in an unpropitious place and [if] the rulers of Fortune or of Accomplishment happen to be at the lower angles <Descendant IC> or just following them, men will acquire prosperity and reputation in the course of their youth. 

If malefics are in conjunction with or in opposition to Accomplishment, when this Place is not at an angle, and if they are alien to the nativity\footnote{Of opposite sect?} and in alien signs and degrees, they then cause destruction of property, even if the Lot of Fortune and its ruler are favorably situated. \textbf{/90K/}

Whenever the ruler of Fortune and the ruler of Accomplishment are in opposition, \textbf{/86P/} even if they are benefics, they cause property to look like a mirage and to be infirm and at risk. If the rulers are malefics, they bring disaster. 

If Accomplishment is in opposition to Daimon, they bring failures of enterprises, loss, and damage, if they do not have benefics in conjunction. 

If the ruler of Accomplishment is in opposition to Accomplishment, it makes wealth useless. If it happens to be malefic, so much the worse. \mnbm If benefics are retrograde, they do the same thing, and in such circumstances they cause disasters. 

If Accomplishment is in opposition to the houserulers, especially if they are malefic and not in their own sect, the native comes close to disaster. 

If \Mars\, is in conjunction or opposition to Accomplishment, the native wastes his substance in pleasures and drink. Likewise if the ruler of Accomplishment is in
opposition to it <\Mars>, the native is extravagant. The same is true if the ruler of Accomplishment is itself retrograde in motion, not at an angle, or in another’s degrees or house.

\newpage