\section{The Lot of Deceit (25K,26P)}

For day births, determine the distance from the \Sun\xspace to \Mars, then count the same distance from the Ascendant; for night births, the opposite <=from \Mars\xspace to the \Sun>. 

If the rulers of the Lots of Fortune, Accomplishment, or Daimon are located in the Lots of Deceit or Theft, the native will gain his livelihood from violence and crime, or from someone’s help. If the rulers of all these Lots are in conjunction, they
have the same effect. 

If the rulers of theft or Deceit are in conjunction either with the Lot of Fortune, Daimon, or Accomplishment, the native’s livelihood will be from these same activities. 

If benefics are in aspect with these places, especially in their proper places or in their own sect, they give the native good moral tone. \mndl If malefics are in opposition or square, the interpretation must be carefully considered\footnote{Implication is the ``good moral tone'' may be compromised if the malefics are in hard aspect}.

\subsection{\textlangle Ignoble and Debased Nativities\textrangle}
We must now discuss nativities which are ruined and debased after knowing good fortune. 

If the Place of Rank and Exaltation has malefics not appropriate to the nativity\footnote{Not of the same sect?} in opposition, or if its ruler does not have \Jupiter\xspace in aspect, especially if the luminaries just follow an angle or if the \Moon\xspace is afflicted, the native’s standing and his high position will be ruined. 

The ruler of the Lot of Fortune, when in opposition to Exaltation or to the ruler of Exaltation, makes the native’s standing and high position precarious. Likewise the ruler of Daimon and the Lots <in opposition> to each other are unpleasant and destructive of rank.

\textbf{/92K/} If the places of the Lot of Exaltation and the Lot of Standing\footnote{No definition for this has been given as yet.} are in opposition, and if the Lots or
their rulers are beheld by malefics, \textbf{/88P/} they afflict themselves: the native will become disgraced, ruined, and insulted. 

If the rulers of the Lot of Fortune, Daimon, or Exaltation are in opposition to the Lot of Standing—either to the Lot itself or to its ruler—or if malefics are in aspect, particularly in superior aspect, to these Lots, the native will be ruined and insulted. The same is true, especially when a malefic is in
aspect to the Lot of Standing: it will then bring degradation of livelihood and status on the native, especially when the malefic is at an angle. In such a case it is clearly obvious that evil portends for the native.

The luminaries are ill-omened when in opposition to their exaltations or to the ruler of Exaltation, particularly when the luminaries are afflicted and are not in their own sect, either one or both of them. They then bring infamy and ruin on nativities. If Exaltation is at MC and a malefic is at IC, the native will succeed in his early years and be honored by many, especially if a benefic is in aspect on the right, but later he will be ruined. If the opposite situation obtains, he will be renowned later, despite having had ill fortune in his early years. If the places are completely afflicted, they indicate ill-fortune from the native’s youth—just as (the opposite case) if benefics are in aspect with the places, good clearly portends, all according to the specific natures and locations of the signs and stars.

Or again: if Daimon is in opposition to Exaltation, it will ruin the nativity. For any nativity, whenever most of the places or their rulers are afflicted, or whenever the new moon, the full moon, or the Lot of Standing have the Lots of Justice, Hostility, or Necessity in conjunction, in opposition, or in
square, then the nativities meet with great upheavals and are harmed with respect to their standing. 

If the afflicted places are few, or if only the Place of Exaltation or its ruler is afflicted, the native will end up unsuccessful, obscure, and contemptible. 

Malefics in opposition or in superior aspect to the Place of Status\footnote{No definition has been given for this. It is not clear if it is a ``place'' (i.e. house) or a lot.} bring ruin to \textbf{/93K/} nativities. If the ruler of Exaltation and the ruler of Status are in opposition, as well as the Lots and their masters, the native is held in contempt. 

If \Jupiter\xspace is in conjunction with Exaltation and
is at an angle, or if it is the ruler of an angle, it makes men renowned. If it is in the signs of Mars <\Scorpio, \Aries> or in its [own] degrees, or if it happens to be \textbf{/89P/} in its own signs <\Sagittarius, \Pisces>, the native will be master of life and death.

As a result,\mndl the previously mentioned places and stars, when found in operative signs, make glorious, governing, royal nativities. When found in moderately active signs, they make noble and famous men who take control. When found in signs which just precede an angle, they make wealthy and vigorous men, stewards of others, men thought worthy of positions of trust and responsibility.

\newpage