\section{[Another Method.] About Parents, from Timaios (31K,32P)}

\subsection{\textit{[Operative Planets, Signs]}}
Prediction about fathers are done as follows: for day births, the \Sun, the sign where the \Sun\, is located, the ruler of the sign where \Jupiter\, is located, and the sign itself which holds \Jupiter, all are operative

Predictions about the mother are made as follows: <for night births>, from the \Moon’s sign (=the sign where the \Moon\, is located) and the houseruler of the \Moon; for day births, from \Venus\, and the sign where \Venus\, is located. 

Whenever these operative stars are found in their own sects, in their own houses, in their own exaltations, with any benefic in superior aspect (or in fact in aspect at all), and when they do not precede an angle or are not afflicted by any malefic in the place where they rejoice, then these stars indicate that the parents’ affairs will be famous, distinguished, and illustrious. 

If the star that should indicate parents’ affairs has any malefics in aspect, either by projection of rays or by superior aspect, or if it is found in a place where it does not rejoice, it will indicate lowly and humble parents.

\textbf{/103K/} The houserulers, along with the specifically indicative star, will also indicate good or bad concerning parents according to the position and aspect of the other stars. If the star indicative of parents’ affairs or its houseruler is unfavorably situated\mndl in its place or is afflicted by any harmful aspect—because it is found to be setting under the rays of the sun, or because it is in <the XII Place of> Bad Daimon, or because the ruler and the afflicted indicative star is not operative in the Place of Parents but is \textbf{/98P/} turned away—if this is the case, it will indicate lowly, humble, and base parents. 

If in addition to being inoperative, these stars are afflicted by having malefics in aspect on the right or in conjunction, this will indicate that the parents are slaves or subjugated people. If however the star indicative of parents just precedes an angle or is afflicted in some other way, but the houseruler is favorably situated and operative\ldots in the Place of Parents, having an indicative star operative in a place not afflicted by any malefic, they indicate harm, punishment, doom, or disaster for the parents. 

\Saturn\, at MC and \Jupiter\, at IC indicate the
father to be a slave, a subjugated person, or an exile, especially when the sun is afflicted.

The Lot of the Father\mn{Lot of the Father} is found as follows: for day births determine the distance from the \Sun\, to \Saturn\, and count this distance from the Ascendant. (Some determine the \Sun\, to \Jupiter\, and count from the Ascendant.) \textsl{[To calculate the Lot of the Mother]}\mn{Lot of Mother} For night births, determine the distance from \Venus\, to the \Moon\, and count this distance from the Ascendant. 

The Lot of Parents\mn{Lot of Parents} is found as follows\footnote{The source text has a lacuna here. Paulus gives it as ``from the \Sun\, to the \Moon'' (PAH p124).}\ldots Concerning a stepfather, take the point directly opposite the Lot. If the ruler of the Lot of the Father happens to be at the point in opposition or if the ruler of the point in opposition happens to be at the Lot, this indicates a stepfather. Likewise if the <ruler of> the Lot of the Mother is found in opposition and the ruler of the point in opposition to the Lot of the Mother is found at the Lot of the Mother, this will
correspondingly indicate a stepmother.

\newpage