\section{The Loss of Parents (32K,33P)}
\index{planets!\Mars-\Sun-\Saturn}
\index{bereavement}
\Mars\, in conjunction with the \Sun\, and \Square\, with \Saturn\, causes bereavement. 

\index{planets!\Saturn-\Mars-\Mercury}
\index{planets!\Saturn-\Jupiter}
\index{orphans}
\Saturn\, and \Mars\, configured with \Mercury, if \Jupiter\, is not in aspect on the right, likewise make orphans. 

\Saturn\, setting with \Jupiter\, makes orphans. 

\index{planets!\Moon-\Jupiter}
The \Moon\, in a bicorporeal sign and with \Jupiter\, in aspect indicates children with two fathers. 

If \Venus\, is in the Ascendant, \textbf{/104K/} and if the \Moon\, is at IC, in the house of \Mars, and if \Jupiter\, is in unfavorable aspect and out of its own house—this too will make children who have two fathers.

\index{parents!character}
The character of the parents can be determined from the stars which are configured together. \Saturn\, will show them to be surly, envious, depraved, suspicious, foul, involved in secret passions, ugly, spending their money on religious matters, friends of great lords. 

\Jupiter\, will show them to be lovers of the good, illustrious, generous, frank and open, cheerful. 

\Mars\, will show them to be bold, \textbf{/99P/} hot tempered, rash, insolent, reckless, restless, risking all, drunkards, toilsome. (Concerning mothers: if \Mars\,
as houseruler overpowers the \Moon\, or \Venus, it shows the mother to be rough, a whore, troubled acutely by bleeding or consumption, if no benefic in aspect relieves the situation.) 

\Venus\, in aspect with the luminaries shows the parents to be cheerful, musical, fond of good cheer, affectionate, religious. 

\Mercury\, shows them to be joiners, sociable and thrifty, sharers in some account or skill, lying most of the time and
wronging their inferiors.

<When making this determination about parents> it is necessary to consider the places <of the stars>
as well: the \Sun\, in a masculine sign and having a masculine star in aspect shows the father to be noble; in a
feminine sign and having the \Moon\, in aspect shows him to be slack and effeminate. 

The \Sun\, in a feminine sign and having \Saturn\, or \Venus\, in aspect shows the father to be not unharmed and not without a bad reputation. 

The \Moon\, in a feminine sign and having feminine stars in aspect shows the mother to be dictatorial and wrathful; in a masculine sign and with masculine stars in aspect, it shows the mother to be hot-tempered and uncontrollable; in a feminine sign and having \Jupiter\, in aspect, it shows the mother to be mild and kindly.

\newpage