\section{The Separation of Parents (33K,34P)}

\Mars\xspace and \Saturn, when intercepting\mn{Aspect Intercept} the luminaries or when situated between the <signs> which contain the luminaries, or between their rays, separate parents. 

Whenever one of the illuminators is in its sect but is unfavorably located, and the other is not in its sect and is malefic relative to the other, this separates parents. 

\Saturn\xspace in conjunction with the \Sun, if the \Moon\xspace is estranged, separates parents. 

If the ruler of the Ascendant is operative, the Ascendant is afflicted, and its co-houseruler \textbf{/105K/} is unfavorably
situated, the parents will be separated, the native himself will be much disturbed and unfortunate, and his parents’ property will be reduced. 

Parents will be in harmony whenever the luminaries and their
houserulers are in harmony with each other. Whenever the houseruler of the \Sun\xspace is in harmony with the \Moon, and the houseruler of the \Moon\xspace with the \Sun, the parents will be in harmony.

\textbf{/100P/} When one of the illuminators is not in its own sect, is nullified by a malefic or is in inferior aspect, and is in either conjunction with or opposition to the malefic, then <the parent corresponding to> the luminary which sets first or to the luminary whose place is more unfavorably situated will die first. 

If the \Moon\xspace is waxing, and if the nativity is at the full moon, and if some malefic beholds the first full moon,
and if this full moon happens in a feminine sign, the mother will die first; if it happens in a masculine sign, the father will die first. 

If the nativity is at the full, moon, the next new moon must be examined: if it happens in a feminine sign with a malefic beholding, then the mother will die first; if in a masculine sign, then the father will die first.

If the Sun is below the earth, in most cases the father will die abroad. 

If Jupiter has a malefic in aspect, and if it <\Jupiter> just precedes with the malefic just following, this indicates that the father will die abroad. 

If Saturn is just leaving an angle, and if it is just approaching \Mars, and if either of them is in aspect with \Jupiter\xspace or the \Sun, the father will die abroad.

For day births, if the Moon is afflicted above the earth or just precedes an angle with a malefic approaching, or if \Venus\xspace is afflicted in the same ways, the mother will die first. 

If the houseruler of the Sun and the Sun itself do not behold the Ascendant, the father will die abroad. 

If the Sun is afflicted by a malefic and \Jupiter\xspace is in inferior aspect, the father will die violently. 

If only Saturn afflicts the previously mentioned stars, the cause of the violent death will be suffocation, dropsy, fluxes, chills, poisoning, shipwreck, or old matters. 

If only Mars afflicts them, the cause will be sword slashes, stings, bloody wounds, consumption, miscarriages, burns, or falls. 

If both malefics afflict the \Sun\xspace and \Jupiter, the violence of the death will be worse in proportion to the natural blending of each star’s inclination.

\newpage