\section{More About Marriage. Examples. (38K)}

\index{lots!Marriage!men}
\index{lots!Marriage!women}
<To find the Marriage Lot:>\mn{Other Marriage Lots} for men determine the distance from the \Sun\, to \Venus\, (for women from the \Moon\, to \Mars), then count this distance from the Ascendant. 

\index{planets!\Venus}
\index{planets!\Mars}
\Venus\, and \Mars\, “depress” both luminaries because the \Sun\, has its exaltation in \Aries\, and its depression in \Libra, where it causes the day to become shorter. The \Moon\, has its exaltation in \Taurus\, and its depression in \Scorpio, where it causes the cosmic disappearance of light.\mn{Marriage Bringer} So, \Venus\, will be the Marriage-bringer for men, \Mars\, the Marriage-bringer for women—generally speaking. 

For men the Place of Marriage should accord with Daimon; for women it should accord with the Lot of Fortune, because of the conjoining and uniting of the \Sun\, and \Moon. <If the Places do accord with the Lots>, the marriage will be judged harmonious and legitimate. 

If many stars are in conjunction or in aspect with the Marriage-bringer, there will be many marriages. 

If the stars are linked with the \Moon\, and have \Jupiter\, in aspect, the marriages will be legitimate. 

If \Saturn\, is in aspect, the marriages will end in death. 

If \textbf{/114P/} \Mercury\, is in aspect without \Jupiter, the native will be criticized for marrying a slave. 

If \Jupiter\, is in aspect with \Saturn, a legitimate marriage is indicated—some will even be ennobled by marriage. 

If in addition these stars are linked to or have some relationship with \Venus, the marriage will result from a seduction. 

If \Jupiter\, is in aspect, the marriage will be legitimate, profitable, and harmonious. 

If \Jupiter\, is absent, but \Saturn, \Mercury, and \Mars are in aspect, the marriage will be with streetwalking, sterile, degraded, or crippled women. 

If the \Moon\, is with \Venus, whorish and lecherous qualities arise as well as jealousy and quarrels; this sort of union is full of pretense. 

\textbf{/120K/} If the \Sun\, rules the Marriage-bringer and is configured favorably, and if \Jupiter\, is linked with the \Moon, the marriage will be legitimate, secure, and respected. 

If the \Moon\, is beheld by \Saturn, the marriage will be with an orphan or under the direction of a guardian. 

If \Venus\, and \Mars\, are together or are linked with the \Moon, the marriage will be with a woman the native has raped or seduced. 

If the \Moon\, and \Venus\, are configured with \Jupiter\, and the \Sun, with no other stars in aspect, the native will marry once.

\index{Fortune!marriage}
\index{Daimon!marriage}
For men and women it will be necessary to examine the Lot of Fortune and Daimon, their squares and oppositions, their houserulers and its ruler, to see whether they are benefics or malefics. If they are configured in their own sects, the marriage will be fine and harmonious. If the places and their rulers are in opposition and are espied by malefics, then there will be setbacks, quarrels, jealousy, hostility, and trials concerning the marriage. Occasionally the native will suffer the compulsion of legal penalties. 

If \Saturn\, is in aspect while all other stars are properly configured, death will separate the mates. 

If \Mercury\, is the ruler of Daimon, the \Moon\, the ruler of the Marriage-bringer, and both are in conjunction or aspect with each other, the native will marry great ladies or women prominent for their money or rank. If \Jupiter\, is also in some aspect, the union will be profitable and harmonious, but if \Saturn\, or \Mars\, is in aspect, upset, hatred, and separations will occur and damaging accusations will follow. 

\index{lots!mother}
If \Jupiter\, is houseruler, is configured with the \Moon, and has \Saturn\, in aspect, the native will unite with his mother or step-mother, but if the \Moon\, has no relationship with the Lot of the Mother, he will unite with elderly women. 

If \Jupiter\, is the houseruler of Daimon and \textbf{/115P/} \Venus\, of the Marriage-bringer, the native unites with sisters or relatives.

If \Saturn\, is in aspect, all this will happen secretly; if \Mercury\, and \Mars\, are in aspect, divorces and public exposure will occur. 

If the \Sun\, is in aspect while \Saturn\, is absent, the marriage will be legitimate and loving, harmonious and profitable. 

If the \Sun\, is the houseruler, the \Moon\, is the ruler of the Marriage-bringer and configured with the \Sun, and \Jupiter\, is in aspect, the marriage will be harmonious, characterized by equality on both sides, legitimate, respected, and illustrious. 

If the \Sun\, is the houseruler, \Venus\, is the ruler of the Marriage-bringer, and \Saturn\, is in aspect, the native will be criticized for marrying a daughter. \textbf{/121K/} 

If the Marriage-bringer is located with \Saturn\, and <\Saturn> or \Mars\, is the ruler of Daimon, the native will remain unmarried. 

If \Saturn\, is the houseruler of Daimon, and \Venus\, holds the Place of Marriage and is found to be with \Mercury\, and to have \Mars\, in aspect, the native will marry barren women or those of bad reputation. 

Whenever the Marriage-bringer is away from an angle or is turned away from Daimon, the native marries foreigners or aliens, or gets a wife from abroad—what sort <of wife> will be clear from the nature of the signs and stars.

\index{Fortune!marriage}
In the same way, for women it will be necessary to examine the Lot of Fortune and the Marriage-bringer (=from the \Moon\, to \Mars) and to interpret their influences. 

If the \Moon\, rules the Lot <of Fortune>, and if \Mercury\, rules the Marriage-bringer and is in conjunction or aspect with the \Moon, the native will unite herself to a slave or a freedman; if \Jupiter\, is in some aspect, this marriage will be legitimized. If under the preceding circumstances \Jupiter\, is in the Place of Children and \Saturn\, is also in aspect, the native will unite herself to a child or some youth in the position of a child. If the Place of Child belongs to \Saturn\, and the \Moon\, itself is in conjunction with \Saturn, the native will remain unmarried. 

If the \Moon\, is houseruler, and if \Saturn\, is the Marriage-bringer and is in conjunction or aspect with the \Moon, she will marry, but will hate her husband and live a disorderly life. 

If the \Moon\, rules the Lot of Fortune and \Mars\, the Marriage-bringer, and if they are in aspect with each other, the marriage will be by force, by kidnapping, or by war and captivity. If \Jupiter\, is also in aspect, later the marriage will be legitimized. 

\index{homosexual}
If \Mars\, is in opposition to the \Moon, with \Saturn\, and the \Sun\, in aspect, the husband will be an acknowledged homosexual. 

For feminine nativities, if \Venus\, rules the Lot, with the \Sun\, in conjunction and holding the Marriage-bringer and the Father’s Lot, and with \Saturn\, in aspect, the native will marry her father. If the \Sun\, rules the Father’s Lot, she will marry an older man in the position of a father. 

If \textbf{/116P/} \Venus\, is the houseruler, \Mercury\, holds the Place of Marriage, and \Saturn\, is in aspect with both, the native will be
promiscuous and live in brothels—but if \Jupiter\, is also in aspect, she will be purchased and become a loving wife. If \Jupiter\, is not in aspect, she will live shamelessly, in misery.  If in the preceding configuration, \Venus\, is found in \Pisces\, or \Capricorn, she will also be depraved. 

\index{rape}
If \Mars\, holds Daimon \textbf{/122K/} and the \Moon\, holds the Marriage-bringer, the marriage will be by rape. If the two are in opposition and have \Saturn\, or the \Sun\, in aspect, the perpetrator will be recognized and caught. 

If \Venus\, rules the Marriage-bringer and \Mars\, the Lot of Fortune, the marriage will be the result of seduction. If in addition \Saturn\, is in aspect with \Mercury, and \Jupiter\, is absent, the native will be convicted of adultery.

As for the rest of the configurations, whatever has been said of the masculine nativities should be applied to the feminine as well. Even if this exposition seems quite complicated, it will become most clear to these who read <attentively>.

\newpage