\section{Children and Childlessness}
The Place of Children\mn{Lot of Children}, which is figured from \Mercury\, and \Venus, must be examined: if afflicted by \Saturn\, and \Mars, they cause childlessness or the loss of children, but if helped by \Jupiter, they cause fine offspring\ldots

Therefore,\mn{Lots for Boys or Girls} it is necessary to examine the houseruler of this Lot of Children, which is found as follows: for male nativities, this Lot is found by determining the distance from \Jupiter\, to \Mercury\, (for female, from \Jupiter\, to \Venus), then counting this distance from the Ascendant. 

If the ruler of the Lot of Children has malefics in aspect, it destroys children; if it has the Givers of Children in aspect, it is indicative of fine offspring.

Petosiris\mn{Petosiris} says:\begin{quote}Whenever Jupiter, Venus, and Mercury are not afflicted, they are indicative of fine offspring. When the opposite is true, they cause lamenting and the deaths of children. If the stars that are in aspect with the Givers of Children are in bicorporeal signs, or if <the Givers> themselves are in bicorporeal signs, the number is doubled. Feminine stars in aspect with the Child giver grant female children; male stars grant male children.\end{quote}

For male nativities: if Jupiter is with Mars as Mars’s houseruler or if \Mars\, is \Jupiter’s houseruler, and if Saturn is in aspect with Venus or is in Venus's house, the configuration is “productive” of childlessness and cuts off those already born.

For female nativities: the Moon in the places of Mercury, and \textbf{/117P/} Venus in a masculine sign with Saturn in aspect or as houseruler cause childlessness and destroy those already born. 

If Jupiter beholds the \Moon\, or \Venus, if the Moon is in the places of \Mercury, if \Saturn\, is in opposition or at MC, and if \Mars\, is in aspect with \Saturn, the native will \textbf{/123K/} bear only one child or be barren. 

Venus with Jupiter in aspect and afflicted by \Saturn\, causes a difficult childbirth of one infant. If the Moon is also afflicted, the native will be completely childless. 

Saturn and Mars at MC, or one at MC, the other at IC, bring childlessness, unless a benefic is in some aspect.

\newpage