\section{Brothers}

The Sun in the Ascendant causes the native to have few or very few brothers. 

Saturn in the Descendant causes the native to have few or very few brothers. 

Jupiter, Mercury, and Venus at the angles are the bestowers of brothers, but Saturn in opposition kills the oldest brother. 

Saturn in conjunction with Mars is destructive of brothers or makes them sickly. 

Venus and the Moon domiciled in the III Place from the Ascendant, the Place of Brothers, grants sisters, especially if the sign is feminine. 

If the Sun, Jupiter, and Mercury are in a masculine sign <in the III Place>, they grant brothers. 

Malefics in aspect with the Place of Brothers, if that Place is unfavorably situated\footnote{VRS wording is somewhat different: ``And when the destroyers are witnessing the place concerning siblings, if they should be poorly situated,''. The ``unfavorably situated'' applies to the malefics, not the ``Place of Brothers'' (VRS Volume 3, p.11)}, kill the brothers who have been born or cause the native to have few or no brothers. Benefics in aspect with the Place of Brothers not only grant brothers, but make them prosper. 

Mars, when operative in the Place of Brothers and favorably situated—especially when it has a benefic in aspect and is beholding the \Moon—becomes a Giver of Brothers.

Some\mn{Lot of Brothers} astrologers calculate the Place of Brothers in the same manner as the Lots: for day births, determine the distance from \Saturn\xspace to \Jupiter\xspace (for night births the reverse), then count this distance from the Ascendant.

\newpage