\section{Making Connections. The Mutual Transmissions of the Stars.}
\index{delineation!planets!distributions}
\index{distribution!\Sun,\Moon\, to \Saturn}
The connections\footnote{This section describes what to expect when a planet hands off to the ruler of its opposite sign i.e. \Leo\, to \Aquarius (\Sun\, to \Saturn), \Cancer\, to \Capricorn (\Moon\, to \Saturn), \Gemini\, to \Sagittarius\, or \Virgo\, to \Pisces\, (\Mercury\, to \Jupiter), etc. Schmidt refers to it as the ``loosing of the bond'' (VRS4 p9).} made will have differing effects because of the nature of the stars: the \Sun\, and \Moon\, when transmitting to \Saturn\, \textbf{/155P/} are indicative of setbacks and anxieties, and they bring hostility from the great and threats due to old religious matters, losses, trials, confrontations, suspicions, dubious livelihoods and ranks, ruin, as well as bodily disorders and dangers, shipwrecks, sudden collapses, and very many crises—all this unless a benefic in conjunction or aspect weakens the onset of the crisis.

\index{distribution!\Mercury\, to \Jupiter}
\Mercury\, when transmitting the chronocratorship to \Jupiter\, from \Virgo\xspace or \Gemini\xspace brings changes in business and innovations in activities. If the places or \Mercury\xspace itself are afflicted at the nativity, and if the overall chronocratorship is contrary, the connection which is made will turn affairs to the better and will be
indicative of employment. On the other hand, if the places are protected by benefics and are bringing a good chronocratorship, after <one> cycle the connection which is made will be disturbing and harmful.

\index{distribution!\Saturn\, to \Sun, \Moon}
\Saturn\, making the connection from \Capricorn\xspace and \Aquarius\xspace to \Leo\xspace and \Cancer\xspace \textbf{/164K/} indicates that the chronocratorship will be vigorous: it brings matters from darkness into the light, and since it is
transmitting the distribution of the chronocrators to the ruling signs, it is most active—depending on the basis of the nativity. It also supplies rank and profits in a way appropriate to the stars in conjunction with it\ldots

\newpage