\section{How Many Years Each Sign Allots. The Maximum Years of Each Star.}

Aquarius allots 30 years, Capricorn 27. The reason: the \Sun\xspace rules a maximum period of 120 years,
half of which is 60. Half of this, 30, is assigned to \Aquarius, the sign in opposition <to \Leo, the \Sun’s
sign>. 

The Moon rules a maximum period of 108 years, half of which is 54. Half of this, 27, is assigned to \Capricorn, the sign in opposition <to \Cancer, the \Moon’s sign>. The total for these two signs is 57, which is the maximum period of \Saturn.

The rest of the stars take their maximum assignment of years from the \Sun\xspace and the \Moon. The \Sun\xspace assigns to \Jupiter, which is a member of the same sect <diurnal> and which has sympathy with the \Sun, being a member of the same triangle <\Leo-\Sagittarius-\Aries>, half of its 120 years plus the length of its minimum period, 19 years. The total for \Jupiter\xspace is 79 years. The \Moon\xspace allots to \Jupiter\xspace in the same way, because they are both benefics and both are in cosmic sympathy, \Jupiter\xspace being in \Pisces, in the same triangle <as \Cancer, the \Moon’s sign>. The \Moon\xspace allots half of its 108 years, 54, plus its minimum period, 25. The total is also 79.

\textbf{/156P/} The \Moon\xspace allots to \Mars, a member of the same sect <nocturnal> 54 years. The \Sun, however,
refuses to allot to \Mars\xspace because of \Mars’ fiery nature which imitates <the \Sun> and because of its malefic
ways, and so the task of allotting passes to the next ruler in the triangle <\Leo-\Sagittarius-\Aries>, \Jupiter, and it allots its minimum period, 12 years. The total is now 66 years.

Likewise the \Moon\xspace allots to \Venus, because of its nocturnal sect and because of the sympathy derived from being <exalted in \Pisces> in the same triangle <\Cancer-\Pisces-\Scorpio>, its 54 years, and \Saturn\xspace allots 30 years, because its exaltation in \Libra\xspace is opposite \Venus’. The total is 84 years.

\Mercury\xspace gets the maximum period, 57 years, from \Saturn, because they are co-houserulers <in the triangle \Virgo-\Capricorn-\Taurus>, plus the minimum period of the \Sun, 19. The total is 76.

\newpage