\section{The Distribution of the Chronocratorships Using the Lot of Fortune and Daimon. The Transits of the Stars and Houserulers. The New and Full Moon, with Examples. Mutual Transmission.}

\index{delineation!distributions}
\textbf{/165K/} This having been established, it will be necessary to examine the transmitter and the receiver of the
distribution to see if they are at an angle or are preceding an angle, or if they are in harmony or are contrary.

If the distribution, when calculated by sign, is from a place at an angle to another place at an angle, and if at the same time, the houserulers of these places are at angles, in the same sect, and have benefics in aspect, they bring a noble and distinguished chronocratorship. 

If the places are at angles, but their rulers precede angles or have malefics in aspect, they indicate that the chronocratorship will be disturbed, subject to ups and downs.

If every relevant point is found to be preceding an angle, the chronocratorship will be terrible, bringing charges and penalties; the native will be involved in travels and changes in activities during these periods.

If under these circumstances <the transmitter and the receiver> are benefic or have benefics in aspect, the native will gain profit and attain success in business abroad, but if they are malefic, he will be entangled in disturbances and penalties abroad or be betrayed by foreigners or slaves. (Therefore we say that the points preceding the angles are indicative of foreigners.) 

If <the transmitter and the receiver> are found at the angles and in their proper places they indicate delays in certain places <abroad> or residence there: \Mercury\xspace and \Venus\xspace cause residence abroad which is not long or extended, since these stars are never far from the \Sun. \Saturn, \Mars, and the \Moon\xspace indicate that the native will live dangerously abroad on land and sea, wandering or living in alien climes. 

The \Sun\xspace indicates \textbf{/157P/} a glorious, honored, and amiable native. 

\Jupiter\xspace indicates that the native will live abroad comfortably and pleasantly with many friends.

If a star which is controlling the chronocratorship relevant to health\footnote{Robert Hand says this means the chronocratorship is from the Lot of Fortune (VRS4 12).} is passing through a sign which is not at an angle, or if its ruler is not at an angle and has malefics in aspect, the native will be sickly, subject to bleeding and dangers. 

If a star which is controlling the chronocratorship <of the matters> governed by Daimon <=occupation> is not at an angle and has a malefic in conjunction or in aspect with the houseruler of its sign, the native will act ineffectively, will be unfortunate, and will be mentally unstable and ruined in
his activities and enterprises. 

If the star controlling such a chronocratorship is found in a fiery sign \textbf{/166K/} with malefics in conjunction or in aspect, he will suffer a great nervous breakdown, and will act against his own will, being mentally unstable. 

If the star is in an airy sign or if the sign or its ruler are afflicted, the native will be distracted and troubled, and will suppose that he is accomplishing something other than what he really is. 

If the star is in an earthy sign, he will bear the blows of fortune nobly, and will survive most things philosophically because of his endurance. 

If the star is in a watery sign, the native will have a mind which can be easily reassured, will come into vicissitudes in many affairs, but will manage to succeed and be successful in his dealings.

In many cases predictions about specific activities are to be derived from Daimon and its houseruler. Some men are involved in bodily activities (e.g. handicrafts) or in physical toil (e.g. as porters or in training). Others have activities involving speech, knowledge, or mental effort. To whichever place, Fortune or Daimon, the majority of stars incline, in that place the type of activity will be revealed. 

It is necessary to take into consideration the activities and the basic character of the nativity (noble, average, fortunate, poverty-stricken, disputed, subject to ups and downs) so that the results of the allotments may be quite obvious. Some stars forecast activities: \Mars, \Venus, \Mercury. \Saturn\xspace forecasts personal talents, plus whatever happens through moist substances, labor, and legacies. 

\index{distribution!\Saturn\, or \Mars}
The chronocratorships from \Saturn\xspace and \Mars, with \Jupiter\xspace not in the configuration, are considered to be base and humble. 

\index{distribution!\Sun\, or \Moon}
The chronocratorships are noble and prosperous when derived from the \Sun\xspace and \Moon\xspace with benefics in
conjunction or in aspect from the right.

If the distribution goes from Daimon to MC (MC relative to the Lot of Fortune) or to the Lot itself, and if the ruler <of Daimon> is there, with \textbf{/158P/} benefics, the \Sun, or the \Moon\, in aspect, and if the basis of the nativity is full of glory, the native will come to power and great rank, and will be distinguished, ruling, and prominent in those chronocratorships. He will be called blessed by many because of his prosperity. 

A distribution which comes at the Ascendant, at MC, or at the other angles forecasts high rank, but not to the same extent, because the places square with the Lots are most efficacious.

If the transmissions occur as specified, and if the basis of the nativity is found to be average, the native will be involved in occupations and profits; he will be a friend of great men; \textbf{/167K/} he will be thought worthy of gifts and offices. He will live happily and successfully in proportion to the level of his occupation, especially if benefics are in conjunction or in aspect. 

If malefics are in aspect, the influence of the places will be visible in the manner just described, but because of the malefics in aspect, the native will meet with reverses and penalties, and will experience only transitory benefits from the benefics.

\index{nativity!basis}
Each star\mn{General} is located in the zodiacal circle according to its house. In a similar way, each star becomes associated with another by its configuration at the nativity.

\newpage