\section{The Universal Year. The Year with Respect to the Distribution: How Many Days It Has and How It Must Be Calculated.}

Since the universal year has 365 1/4 days, while the year with respect to the distribution has 360, we subtract the 5 intercalary days and the one-fourth of a day, then we find the number of years. Only then will we make the distribution. (We calculated in this way for the previous nativity.) 

For example: a person in his 33rd year was born on Tybi 15; we are investigating Mesori 20 of his 33rd year. I multiply 30 years
times the 5 <intercalary> days for a total of 150. Now I add 10 <intercalary days> for the two complete years <31, 32> plus one-fourth of 32 (=8) for a total of 168. Next I take the number of days from Tybi 15 to the day in question, Mesori 20 (=215), and I add this amount to 168 for a grand total of 383. From this sum I subtract 360, and the remainder is 23. So the nativity will be in its 33rd full year with respect to the distribution, plus 23 days. I consider this number of years and days when making the distribution of the chronocratorships.

\begin{mdframed}[backgroundcolor=cyan!5]
\scriptsize
Essentially Valens is trying to find how many days the native has lived to the moment in question and convert that into days according to the distribution which is based on 360 days per year rather than 365 1/4 days per year. He is looking at a specific day (Mesori 20) in the year in which the native turns 32 (his 33rd year).

Thirty-two universal years (32 x 365.25 = 11688) minus thirty-two distribution years (32 x 360 = 11520) leaves 168 days. He then adds the days from the natives birthday on Typbi 15 to the required day of Mesori 20 which he tells us is 215 days: 168 + 215 = 383. Subtracting 360 distribution days leaves 23 days so, in distribution days, the native has lived 33 years and 23 days while in universal time he has lived 32 years and 215 days (32 x 265.25 + 215 = 11,903 = 360 x 33 + 23). 

It's easier to take (age on birthday x 365.25 + days in current year) / 360 i.e. (32 x 365.25 + 215) / 360 = 33.06 = 33 years 23 days.

\end{mdframed}

\newpage