\section{The Names of the Twelve Places. The Twelve-Fold Division.}

\index{places!significations}
\index{places!01@1st}
\textbf{/170P/} Let us begin with I the Ascendant, life, steering-oar, body, breath. 

\index{places!02@2nd}
II Life, the Gate of Hades, shadowy, giving and receiving, association.

\index{places!03@3rd}
III Brothers, travel abroad, kingship, authority, friends, relatives, rents/revenue, slaves.

\index{places!04@4th}
IV Rank, children, one’s own wife and older individuals, activity, city, home, possessions, lodgings, alterations, change of place, dangers, death, confinement, religious matters.

\index{places!05@5th}
V The Place of Children, friendship, association, slaves, freedmen, the completion of some good deed or benefaction.

\index{places!06@6th}
VI Slaves, injuries, hostility, disease, sickness.

\index{places!07@7th}
VII The Descendant, marriage, success, an affair with a woman, friendship, travel.

\index{places!08@8th}
VIII Death, benefits from the deceased, the Inactive Place, law, sickness.

\index{places!09@9th}
IX Friendship, travel, benefits from foreigners, God, king, magnates, astrology, oracles, appearances of the gods, mystic and occult matters, associations.

\index{places!10@10th}
X Occupation, rank, success, children, women, change, innovation in business.

\index{places!11@11th}
XI Friends, hopes, gifts, children, slaves, freedmen.

\index{places!12@12th}
XII Foreign lands, hostility, slaves, injuries, dangers, tribunals, disease, death, sickness.

Each Place acts in the way specified, and the nature of the Place in opposition also acts cooperatively\footnote{This was something Morinus was also keen to point out.}.

\index{delineation!distributions}
When the transmission of the year has been found, we examine the Place where the transmitter is found and the Place where the receiver is found (using the twelve-Place system described above and the properties of the sign and the Place). The transmission of the stars \textbf{/180K/} will have its own causative influence as well, which we will append at the end of <our section> on the distribution.

An example: \Saturn\xspace or \Mars\xspace is in the Ascendant and is either transmitting or receiving. We can say that during this year there will be bodily troubles, danger, or bleeding. 

If these stars are in the VII Place from the Ascendant, there will be a turn to the worse because of a wife, or danger to a wife, or an upsetting crisis because of marriage. 

If they are in the IX Place from the Ascendant, there will be hazardous travel, trouble abroad, or betrayal at the hands of foreigners. 

If they are in the XII Place, there will be grief because
of slaves or enemy revolts. 

In other words, the star will activate those matters which each Place influences.

\textbf{/171P/} If benefics are in these Places, they indicate something good: rank, profits, longed-for purchases, travel.

Determinations should also be made by taking into consideration the stars receiving from or in aspect with the Places, noting that the type of influence and the outcome of affairs will be determined by the transmitter, the receiver, and their Places.
It will also be necessary to look at the ruler\footnote{The ``dispositor'' or domicile ruler of the sign the planet occupies; another important influence stressed by Morinus.} of the transmitter or of the receiver and the sign in which it is located, because this star too will be influential on the type of effect <to be expected>. 

\index{places!02@2nd} \index{places!08@8th}
The II and the VIII Places from the Ascendant will be considered inactive and fatal. Whenever the transmission or
reception is in these Places, the native will benefit from aspects relating to death. Greater benefics will accrue when benefics are in conjunction or aspect. 

If malefics are in conjunction or aspect, disputatious lawsuits will arise because of a legacy, and the year will be dangerous, calamitous, or impropitious.

Occasionally it happens that when only malefics are <in the Places> or are with the \Sun, the \Moon, or \Mercury, the native will be charged with murder or will bring something dangerous on his own head. If in addition \Venus\xspace is in conjunction or aspect, the native’s life will be even more in upheaval because of poisonings, or he will be denounced as a conspirator. 

\index{distribution!\Saturn\, to \Jupiter}
Note that the places of \Saturn\xspace are indicative of death and inheritances, and the transmission to \Jupiter\xspace forecasts inherited property and benefits from the deceased.
If this transmission coincides with the first chronocratorship, without question there will be inheritances and great benefits proportional to the basis of the nativity. 

If the distribution is in the <II Place>, the Gate of Hades, and if the transmission is from \Saturn\xspace to the house of \Jupiter, there will be an inheritance. If only
the transmission occurs, there will be benefits from the deceased—likewise \textbf{/181K/} if \Saturn\xspace and \Jupiter\xspace are in the same sign and are transmitting or receiving.

If the transmission is from <the XII Place of the> Good Daimon, <the V Place of> Good Fortune, or from the Lot of Fortune, and if benefics are in aspect, there will be inheritances, gifts, or a cause of some good. 

If the fatal Places transmit to Places which precede the angles or vice-versa, the native will hear of someone’s death while abroad or as a result of travel. (The four Places which precede the angles serve as Places of Foreigners and of Slaves.)

\index{signs!significations!Thema Mundi}
 Likewise in any nativity \Gemini\xspace and \Sagittarius\xspace have the same general effect as the Place of Slaves because of their zodiacal position: when \Cancer\xspace is in the Ascendant\footnote{This is the reference to the \textsl{Thema Mundi} or the chart of the world which has \Cancer\, on the Ascendant and \Aries\, on the MC. In this chart, \Gemini\, is on the 12th, \Sagittarius\, is on the 6th.}, the Place of Slaves falls in these signs. So even when a native has the Place of Slaves in another sign, \textbf{/172P/} but has malefics in these <\Gemini\xspace [or] \Sagittarius>, he will experience disturbances and injuries from slaves, even penalties, death, and flight, especially if \Saturn\xspace is in these Places\footnote{This would support the idea that signs carry a hint or echo of their whole sign house significations but as they are found in the \textsl{Thema Mundi} and not as they are found by modern astrologers, who equate them to houses in a chart that starts with \Aries\, on the Ascendant.}. 
 
 If benefics are in these Places, the native will be thought well of <by slaves> and will receive benefits from them, and he himself will be a benefactor of slaves, or will indeed raise some, treating them as his children.
 
Consider the same to be true for the rest of the Places which precede centers.

\newpage