\section{The Transmission From an Exaltation to an Exaltation.}
\index{distribution}
A transmission from an exaltation to an exaltation with benefics in conjunction or aspect is productive of rank and profits, especially if the rulers are in their own places. Similarly a transmission from <the star’s> own house to its exaltation or vice-versa with the rulers in aspect indicates vigorous, noteworthy results. 

A transmission from a depression to a depression indicates a mediocre and variable nativity.

\index{distribution!malefics}
If \Saturn\xspace and \Mars\xspace are properly configured and are transmitting to and receiving from their own houses,
exaltations, or operative places, they bring great public services and high rank. \Saturn\xspace provides inheritances, landed property, estates, rents, stewardships, and it brings success in religious undertakings and affairs of ancient lore. \Mars\xspace controls the governing aspect. If benefics are watching and if the \Sun\xspace and the \Moon\xspace are properly configured with them, they bring great and profitable distinction to men. But if benefics are absent and if the luminaries are in opposition or are unfavorably configured, and if \Mercury\xspace is involved, \textbf{/182K/} they bring accusations, reversals, great dangers, plots, riots, and ruin.
If the transmission or reception is to or from another star’s exaltation, or even to or from its own when it is unfavorably
situated, the native will be thrown from high places or from animals, will suffer wounds, bleeding, and dangerous diseases, or be involved in fires and shipwrecks. Even if the nativity is helped and has an allocation of years <left to live>, the native will experience the ruin of his livelihood or rank.

\index{sect!configurations}
\index{rank}
\index{distribution!benefics}
One must observe whether the stars of the night or of the day sect are configured with their sect mates\mn{Sect mates}. If they are, they will be more effective for good than the other stars and will be a cause of great good fortune at the times of their own transmissions and transits. If they are not so configured, \textbf{/173P/} they will prevent any advancement in rank and will hinder any benefits. Because of this they have been named “malefic,” since they are “malefactors” of life, but benefactors in other respects. Even \Jupiter\xspace and \Venus, when found to be setting at the time of transmission or transit, when unsuitably configured, or when unfavorably
situated, cause a disturbed period, unsuccessful and full of delays; they are “malefactors” of hopeful expectations or benefits. In addition, they even bring penalties, spiritual torment, and criticism for one’s accomplishments.

\newpage