\section{The Phases and Transits of the Stars.}

\index{planets!condition}
For all stars the following general factors must be observed: if they are found to be rising when transmitting or receiving, and to be ruling the year or acting as the overall chronocrator, and if they are rising when they arrive at operative places in their transits, they clearly bring occupation. Their power is aroused then, and each star will cause the results appropriate to its nature. Whatever influence and effects it has at the nativity or whatever the year indicates—in whichever sign it is located, those are the effects it will activate.

\index{planets!retrograde}
If the stars are passed the first stationary point and are found to be \mn{retrograde} retrograde, they delay expectations, actions, profits, and enterprises. In the same way they will be rather weak and thwarting when in opposition to the \Sun; they hold out only appearances and hopes. \textbf{/183K/} 

\index{planets!direct}
If they are at <or passed> the second stationary point, they cancel any delay and reinstate the same activities. They then bring stability and success in life. 

\index{planets!visibility}
\index{rank}
If the stars are at their \mn{visibility} last visibility, they bring obstacles and pains in one’s accomplishments, as well as bodily crises, illnesses, and afflictions of the hidden parts. Often they hold
out rank and great hopes only to turn them to the worse. 

If a \mndl malefic forecasts something for a nativity and has the year <=is chronocrator>, and if <another> malefic transits the year, it intensifies the evil; if a benefic
transits, it brings relief and help. Assume the same is true for benefics.

\index{distribution!\Jupiter}
In any nativity \Jupiter\xspace has an extraordinary effect. If it transits the year, the points square, or those in opposition, and if the chronocrator is well situated or in operative places, it will bring great public services and high rank, \textbf{/174P/} particularly so when it is rising; then it has special power over the stars which seem
to control the chronocratorship. 

If the chronocrator is unfavorably situated while \Jupiter\xspace is in transit, it will be somewhat weak and unsettled and will delay the public services and high rank. If it is rising, it will relieve or help moderately.

\newpage