\section{The III Place and the IX Place from the Ascendant.}

The III or the IX Place from the Ascendant, when transmitting or receiving with benefics in those Places, causes travel under favorable circumstances, or occupation and association abroad or with foreigners. If the Place happens to be in a bicorporeal sign, the native will profit or will travel many times. Some men $<$with a star$>$ in these Places receive messages from God, know the future, and are in charge of sacrifices, prayers, and offerings to God. Others avoid illness, imprisonment, accusation, disease, or danger through the foresight of God, and they bless Him for it. 

If the nativity’s basis is great and if the overall chronocrator is supportive, the native receives gifts from a king, governing responsibilities, or authority, or—having escaped from troubles and crises with royal good fortune—he becomes renowned. Some prepare shrines, temples, and royal images and in so doing win eternal fame. But if malefics are in conjunction or aspect \textbf{/184K/} with these Places, the native is despitefully treated abroad and falls into penalties or poverty. He does not succeed abroad, but is involved in wanderings and danger, and comes to his end cursing his fate as if he were suffering the wrath of God. 

\enlargethispage{2\baselineskip}
Some men during these times will deny God’s power, will engage in bizarre religious acts or eat unclean food. They will become soothsayers, seers, or prophets, or they will be considered mad. Those endowed with a more lofty fortune or rank will endure disturbances abroad or because of foreigners, as well as scandal, riots, and revolts of mobs or cities, because of which they undergo extraordinary dangers, hostility, and betrayal because of their responsibilities. Sometimes they meet with accusations, are terrorized by the king, and are ruined in rank and livelihood.

\newpage