\section{The Transmissions of the Stars and the Ascendant. The Results.}

Continuing this topic, we must append the transmissions of the stars.

\subsection{[The Distributions of the Sun]}
\index{delineation!distribution!\Sun}
The \Sun\, transmitting to \Saturn\, brings a bad year. It indicates unemployment, setbacks, hostility and
rejection, damage from superiors or elders, rebellions of the lower classes, diseases and eye infirmities, ups and downs of livelihood and terrifying upheavals, attacks of subject peoples, the deaths of fathers or of men in the place of fathers. If the transmission is unfavorably situated, it brings convictions and imprisonment.

The \Sun\, transmitting the year to \Jupiter\, indicates a brilliant year: the father’s high rank (for those who have a living father), association with superiors, prosperity, gifts, prominent occupations, offices. It brings
the begetting of children and marriage (for the unmarried) and brings enterprises to fruition. It brings success and foretells great expectations.

The \Sun\, transmitting to \Mars\, indicates a sickly and hazardous year: danger to the father or to those in
the role of a father,\ldots For him an effective period<?> and success in business, but with many quarrels, expenses, inopportune penalties, hostility from the great or from fathers, harm from subordinates, cuts, bleeding, loss of blood, troubles of the intellectual faculties, blindness, crises due to hatred, abuse.

The \Sun\, transmitting to \Venus\, indicates a good, affectionate period: it brings associations and friendships, gifts, enjoyment, affections, marriages, \textbf{/180P/} childbirths, buying of jewels or slaves. To men of superior rank it brings offices, distinguished rank, a vision of great expectations, and freedom from trouble and every crisis.

The \Sun\, transmitting to \Mercury\, is good, effective, advantageous, associative, beneficent to subordinates, and productive of giving and receiving. If it is beheld by malefics, it brings trials and tribulations, anxiety because of money or documents, the condemnation of slaves and friends, as well as untimely expenses and penalties.

The \Sun\, transmitting to the \Moon\, is vigorous and kindly: \textbf{/190K/} it brings acquisition, benefits from males and females, associations, marriages, unions, distinguished births, prosperity and gifts from foreigners or from abroad.

The \Sun\, distributing to itself and being favorably configured brings brilliant prospects and activities:
associations with and unexpected benefits from superiors and the great. 

If the \Sun\, is in conjunction or in aspect with benefics, it brings even greater rank and benefits. 

If however the birth is at night, the forecast will be less optimistic: disturbed, with hostility, crises, or envious accusations. 

If a malefic is in conjunction or aspect, it brings reduction of livelihood, ruin of status, hazardous travel, the hostility of or danger to the father, and the disruption of activities.

\index{planets!condition}
First of all it is necessary to examine the nature and relationships of the stars: each star in its own sect and favorably configured will show a causative influence depending on the basis of the nativity. 

The aspects and transits of the other stars will have great power to weaken or postpone a bad influence or to benefit and elevate <the native>. It is better if they are found rising and in operative signs; if they are in the Descendant, or are inappropriately or badly situated and afflicted, they will turn to the worse.

\newpage