\section{The Distributions of the Moon.}

The \Moon\xspace distributing to itself is unpleasant: it brings hostility and lawsuits from the great, ups and downs of livelihood, and confrontations with relatives or wives. A malefic in aspect from the right brings bodily weakness \textbf{/181P/} and sudden dangers. In such a chronocratorship, it is necessary to examine the sign in which the \Moon\xspace is located, in order to see if a malefic in transit will cause something worse. 

If a benefic is in transit, it brings relief from the crisis, but it also brings travel and change of place. At the same time it brings renewed success for the indigent and a cure for their miseries.

The \Moon\xspace distributing to the \Sun\xspace brings the waning of livelihood and great expenses. Especially if malefics behold the transmission, the failure of actions and vain hopes are foretold, as well as upheavals, disturbances, domestic disorders, and affairs or marriage with women. For those who have a solidly established rank in life, $<$this distribution brings$>$ expenditures resulting in purchases or renewed success in business, \textbf{/191K/} and advancement or some gifts and benefactions.

The \Moon\xspace distributing to \Saturn\xspace brings a complicated and fluctuating year: the sickness or death of the
mother (if she is still alive), hostility, disarray in business, changes of place, chilling of activities, bodily
dangers, troubles of the hidden parts or of the sensory faculties—especially if the \Moon\xspace is waning. If it is
waxing, the damage will be less, except that the period will be harmful and grievous.

The \Moon\xspace distributing to \Jupiter\xspace indicates a good and productive period, one full of accomplishment and association with the great, rank and offices, benefits and gifts from females. It brings marriage to the unmarried, children to the married, alliances and friendships, or the increase of the mother’s livelihood and rank (for those who have a mother living), success in business, and the fulfillment of hopes and expectations.

The \Moon\xspace transmitting to \Mars\xspace brings a hard year, especially if the \Moon\xspace is waxing (for day births): it causes dangers and illness, bleeding, falls, accidents with fire, penalties, domestic disorder, the deaths of or separations from females, hostility, trials, imprisonment, and upheavals of the masses. 

If the moon is waning or is approaching new (especially for night births), and since the chronocratorship is passing to the troublesome and active $<$star$>$, it forecasts that men will succeed—but only with anxiety and labor.

The \Moon\xspace distributing to \Venus\xspace indicates a period which brings success and accomplishment: rank,
association, alliances with men and women, and marriage. If the stars are inappropriately situated and are beheld by malefics, \textbf{/182P/} they bring about unpleasantness, hatred, expenses, and breaches of promise towards female individuals. 
Overall, this transmission generally brings jealousy, quarrels, disorders, and hostility towards relatives, family, and friends.

The \Moon\xspace distributing to \Mercury\xspace brings an effective and successful period with respect to females and
political associations, especially if $<$the transmission$>$ is configured with benefics; if with malefics, men will endure lawsuits and disturbances because of money, documents, and accounts, and they will suffer great struggles. If \Mercury\xspace is found situated in its rightful place, they will survive; if not, they will be condemned and will make great expenditures.

\newpage