\section{Distributions of the Ascendant}

\index{distributions!Ascendant}
\textbf{/192K/}The Ascendant transmitting to a malefic brings a very bad period, especially if the transmission is to \Saturn\xspace (for night births) or to \Mars\xspace (for day births). It brings bodily dangers, ups and downs of livelihood, anxiety, disturbing crises, falls, and injuries.

The Ascendant transmitting to \Jupiter\xspace indicates a brilliant and profitable period, high ranks, and distinguished positions. Some are helped and promoted by the great; some escape dangers and crises and their troubles are relieved; others attain freedom.

The Ascendant transmitting to \Venus\xspace indicates a good, lovely time: associations and affairs with women, buying, good cheer, an escape from evils.

The Ascendant transmitting to the \Sun\xspace indicates that men will be well received by the great and by superiors, and that the year will be successful. For those of high rank, it brings even higher positions and
advancement.

The Ascendant transmitting to the \Moon\xspace indicates a steady and effective period: help from and associations with women, innovations, occupations, travel with a successful outcome, and (especially if benefics are in aspect) prosperity abroad. If malefics are in aspect, it indicates the opposite—and with disturbances.

The Ascendant transmitting to \Mercury\xspace indicates an effective, profitable, and successful period. If the
transmission is harmed by malefics, the period will be subject to the law and to penalties.

Stars transmitting to the Ascendant show the same results; a forecast will be made of good or bad according to the position of each star, whether appropriate or the opposite.

\newpage