\section{The Distributions of Saturn}

\index{delineation!distribution!\Saturn}
\textbf{/183P/} \Saturn\xspace distributing to itself points to trouble and unemployment, hostility from elders or the great, and disgrace. Men will fail in their attempts or, if they do accomplish anything, it will be insecure. If \Mercury\xspace or \Mars\xspace beholds \Saturn, men will be denounced and have trials because of documents; they will suffer the subversion of matters concerning religion or legacies, will suffer from malignity and tricks, and they will come to an end like those suffering the wrath of God. <If benefics are in aspect,> the results will be milder: <troubles> will come more slowly, mixed with some success.

\Saturn\xspace transmitting to the \Sun\xspace brings danger to the father or his death, if he already has some infirmity.
It brings an uncertain year: \textbf{/193K/} hostility, penalties, lawsuits, troubles of the sense organs, recurrence of disease, meanness on the part of friends and relatives. For day births, if the transmission happens to be favorably configured, men will succeed with wearisome labor and expenditures, or they will profit from deaths. 

\Saturn\xspace distributing to the \Moon\xspace indicates danger to the mother—if she is still alive; if not, to female
individuals. It <brings about> hostilities, separations, damage, criminality, disturbances in business, dangerous movements, bodily weakness, intermittent fevers, internal and nervous disorders, feebleness, dimming of vision, unexpected diseases.

\Saturn\xspace distributing to \Mars\xspace indicates a terrible and dangerous year: it brings about illnesses, plots,
troubles, dangers, the deaths of family members and suffering or disturbances and lawsuits on behalf of family members, the ingratitude of friends, family upheavals, defense speeches/disputes, fears and hatreds with respect to the great, the deaths of fathers (if they are still alive) or of older individuals, hazardous and profitless travel. If the stars are unfavorably situated, they bring about shipwreck and ruin, diseases and injuries. If they are well configured in operative signs or have benefics in aspect, most of the trouble will
be dissipated.

\Saturn\xspace distributing to \Jupiter\xspace indicates a fine and effective period: men receive inheritances and legacies. They receive help from older people or from wills. They control estates and property. Some gain profit from moist matters: they own ships, they purchase ships, they demolish and \textbf{/184P/} rebuild, they restore old matters and are adorned with a livelihood. If \Mars\xspace or \Mercury\xspace are together and in aspect with this distribution, men will endure trials and lawsuits, and will have untimely expenses.

\Saturn\xspace distributing to \Venus\xspace indicates those who separate from wives or are wronged by females. Some will see the deaths <of wives> or will be inconstant in their marriages and love affairs. Some will be the victims of plots and will experience poisoning. They suffer internal troubles, are plagued by weakness, chills, attacks of the flux, and endure reversals, lawsuits, and changes in their affairs. If the nativity is of a women, she will live in pain, especially if she is pregnant. \textbf{/194K/} She will also have affairs with her husband’s friends.
\enlargethispage{2\baselineskip}
\Saturn\xspace distributing to \Mercury\xspace indicates disputes about old or religious matters, about money or
accounts, about giving and receiving. It indicates obstacles to accomplishing anything, penalties, betrayals, and hatred. Men will see the deaths of family members, will become accomplices or meddlesome persons during these periods, will be involved in loans and debts, will suffer upheavals because of documents, all according to the proper or improper configuration of these stars in the horoscope. They are most terrible and ruinous when in square or opposition <with each other>; they then bring anxiety and upset instigated by the dead/legacies.

\newpage