\section{The Distributions of Jupiter}

\Jupiter\xspace distributing to itself brings a good and effective period: help from friends, gifts, successful activities, trusts, stewardships, associations with the great, and the begetting of children. If it is beheld by \Mars, it brings ups and downs and untimely expenses.

\Jupiter\xspace distributing to the \Sun\xspace indicates a brilliant period, full of accomplishment for superior
personages: it brings popular success, offices, advancement. It makes men worth of honors, garlands, the offices of governor and general, and indicates the attainment of wealth—all proportional to the <stars’> arrangements and positions in the horoscope. For men of average rank, it indicates employment, escape from evils, freedom, beneficial associations, changes, as well as sympathetic friendships, childbirths, the acquisition of slaves—all this especially when \Jupiter\xspace is well configured for day births.\textbf{/185P/}

\Jupiter\xspace distributing to \Saturn\xspace makes movements that can produce good or bad, expenses, domestic distrust. To some it brings deaths, changes of residence or business, unsteady associations, hostility of friends. It makes men fail to succeed in enterprises or to succeed only after delay. It makes men petition and plead <for justice> and to be involved in troubles.

\Jupiter\xspace distributing to \Mars\xspace indicates a harmful and disturbing year: it controls hostility from superiors, slanders, condemnations, betrayals, hazardous travel, dangerous diseases, critical periods or deaths of family members, ups and downs in livelihood, expenses. If the nativity is found to be of the public or governing class, and if the configuration is favorable, it brings political ties and advancement, along with expenses, gifts, and promises. These men will live with anxiety and suspicion. \textbf{/195K/}

\Jupiter\xspace distributing to \Venus\xspace is profitable and full of gain: it brings affectionate associations, gifts, help from or because of women. Men are involved in intimacy, love affairs, and friendships. It brings marriage to the unmarried and conception or childbirth to the married. To noble nativities, it brings the honor of wearing garlands, distinguished rank, state offices, gifts to the masses, great advancement and preeminence, the possession of slaves and ornaments.

\Jupiter\xspace distributing to \Mercury\xspace is effective and profitable: it develops business and becomes helpful to
those concerned with words, accounts, or documents. It brings friendship with the great, gifts or conveyances, and profits from deposits or treasure troves. As a result men purchase slaves and become elegant. Some advance in rank, especially if the stars are favorably situated. As a rule, however, the native is slandered among the masses and is disturbed, or he endures scandal. Especially if the stars are badly configured or have malefics in opposition, conjunction, or square, the native suffers extraordinary trials and lives in anxiety.

\Jupiter\xspace distributing to the \Moon\xspace indicates a successful period full of accomplishment: ties with and help from women and the great, rank, offices, preeminence, escape from dangers, the acquisition of ornaments or slaves, conception or childbirth, affairs with women, gifts, conveyances, and benefits for the mother (if she is still alive). If the configuration is favorable, \textbf{/186P/} men will control deposits. It causes men to find treasures and to become wealthy, to bless God, and to escape harm or slavery.

\newpage