\section{The Distributions of Mars}

\index{planets!\Mars!distribution}
For day births, \Mars\xspace distributing to itself will be unpleasant and disturbing: it brings hostility, harm, abuse connected with public business, or expenses for the public. So, some are abused or imprisoned by officials or by the wealthy. For night births \Mars\xspace is not bad: it promotes success and becomes helpful, especially if it is in operative signs, particularly for those who participate in martial affairs or in public or official life.

\Mars\xspace transmitting to the \Sun\xspace indicates danger to the father—if he is alive; \textbf{/196K/} if not, danger to the one who is like a father. It causes hostility from the great, separations from friends, dangerous diseases, troubles of the sense organs, danger from fires, heights, or animals, bleeding, amputations, and falls. It brings envy, disputes, and risky travels. If <the stars> happen to be in operative signs or have benefics in aspect, they bring employment, benefits, rank, political ties with superiors, but at the same time they bring anxiety, upset, plots, hatred and obstacles in the employment.

\Mars\xspace distributing to the \Moon\xspace is hazardous, prone to fail: it causes disorders, confinements, lawsuits,
anxieties, hazardous travel, attacks and abuse from foreigners, danger to the mother or to females, battles, separations. It disturbs the masses or the city. It brings weakness, bleeding, falls, relapses of diseases, danger from fire, and shipwreck. Especially if the nativity is during the day, and if the moon is waxing and unfavorably situated, the previously described effects will become worse: even blindness, wounds, the
breaking of bones, troubles and injuries to the eyes. If the stars happen to have benefics in aspect and are in operative places, they cause risky activities and advancement. To females they bring bodily dangers, bleeding and consumption, abortion, and troubles of the generative organs. \textbf{/187P/}

\Mars\xspace distributing to \Saturn\xspace indicates a terrible and disturbed year: men come into lawsuits and
abuse, penalties and breaches of faith; they see dangers to or the deaths and destruction of family members; they are involved in violent disruptive deeds, in harmful or painful travel, in bandit attacks, in illnesses and sudden dangers, revolts of their enemies, injury or grief from slaves. After meeting with imprisonment, anxiety, and the need for defense speeches, they will be treated miserably—unless the stars bring about these crises just to a minor degree, because they are in their proper signs or have benefics in aspect.

\Mars\xspace distributing to \Jupiter\xspace indicates a fine and effective year: it brings success, help from and association with the great, good hopes and the fulfillment of wishes. If the native has some connection with the military, he will campaign and be successful. Those of lofty fortune will be distinguished in their governorships and high rank;\textbf{/197K/} they will change their position for the better and will be adorned with the prerogatives appropriate to them, even though they had been involved in ups and downs and expenses
previously. If the star is in opposition, it is indicative of reversals and penalties.

\Mars\xspace distributing to \Venus\xspace indicates hostility with and separation from females, family upheavals, the death of the mother (if she is still alive), or of females, intimacy and whoring, impermanent friendships, and denunciation. Even if the stars have an affinity, men suffer chills <=inactivity> and will be confounded in their <business> affairs. Women live endangered by bleeding and miscarriage.

\Mars\xspace transmitting to \Mercury\xspace indicates a disturbed year: it controls dangers, penalties, and disputes
because of documents, money, or accounts, crime by magic, loans, debts, legal attacks and defenses. If the stars are in bicorporeal signs, men will display this same behavior towards others and will commit any crime. If the three aphetic points <\Sun\xspace \Moon\xspace Ascendant> are preserved, men will survive these effects. If, however, they are badly situated, men will be unsteady in their accomplishments. If they get into lawsuits, they will be worsted, will suffer very great losses, and will be involved in extraordinary crises.

\newpage