\section{The Distributions of Venus}

\index{delineation!distribution!\Venus}
\Venus\xspace distributing to itself when favorably situated brings friendships and associations, agreements between men and women, gifts, enjoyable intimacies, marriage, family harmony, pleasures, and profits. If the star is found with \Saturn\xspace or \Mars, is beheld by them, or is in inoperative signs, it brings criticism, denunciation, whoring, penalties, breaches of faith, treachery from women, trials, and disorder. Women suffer the same treatment from men.

\Venus\xspace distributing to the \Sun\xspace brings a glorious period, full of accomplishment, a period characterized by associations and help from males and females: intimacy, marriage, childbirths, the purchase of ornaments and slaves, or gifts of these same items, high rank for the father (if he is still alive), or sympathy and help from father-like figures—all of this especially if the stars are favorably configured. To those of superior rank it brings the honor of wearing garlands, high-priesthoods, advancement, offices, \textbf{/198K/} and
gifts to the masses. It brings oracles, association in religious or divine matters, charm, and joy.

\Venus\xspace distributing to the \Moon,when <\Venus> is favorably located and configured in auspicious places, indicates a profitable period, full of gain: it decorates men with spectacular livelihoods and bestows on them distinguished ranks—except that <this rank comes> accompanied by envy, jealousy, quarrels, and secret hatred from some men. It usually brings incomplete or partial acquisition and benefits. If \Venus\xspace is unfavorably configured, it causes injustice and hatred from males and females, and uncertainty and disorder
in regard to relatives and friends. Overall, the transmission from \Venus\xspace to the \Moon\xspace is basically envious and jealous.

\Venus\xspace distributing to \Saturn\xspace indicates an uncertain and damaging period: it brings separations from
women, fights, violence, denunciation, injustices even from the mother or from females, the hostility of relatives, disgrace, disputes with older people or associates. It entangles men in gossip and shameful passions, unstable friendships and intimacies. Men are at law with women and endure confrontations. They experience <changes> of place and a chilling of business. They fall into weakness and troubles of the hidden parts or of the sense organs. \textbf{/189P/} They are threatened with plots, poison, and recurrent fevers,
especially if \Mars\xspace and \Mercury\xspace are in aspect.

\Venus\xspace distributing to \Jupiter\xspace indicates a good year, full of gain: it brings association with the great,
gifts, offices, civic and social magnificence, rank and advancement, marriage and contacts with females, friendships, conception and childbirth, and graciousness in all activities. Even if a man is of mediocre fortune, he will succeed and will gain release from his miseries or from subjugation; he will be thought worthy of trust and honor and will be adorned with the prerogatives appropriate to him.

\Venus\xspace distributing to \Mars\xspace indicates an uncertain year: fights and separations from women, bleeding,
consumption, the deaths of women or mothers. Men plead cases because of women, and they endure jealousy, hostility, denunciation, gossip, and whoring. They are wronged, are betrayed, and when acting against their real intentions or in pretense, they suffer punishment. Occasionally they think that the breakup \textbf{/199K/} of their marriage is what they have prayed for, and they go through with it because of some
anticipated good; <but they suffer> scandal in the mouths of everyone.
\enlargethispage{2\baselineskip}
\Venus\xspace distributing to \Mercury\xspace indicates an effective period, full of attainment in the areas of giving,
receiving, and trade. For those active in letters or education, it makes friendships, the purchase of ornaments and slaves, alliances and agreements with males and females, ranks and honors, success in business, association in religious matters, trusts consisting of deposits, and the harmony of relatives.

\newpage