\section{The Distributions of Mercury}

\index{delineation!distribution!\Mercury}
\Mercury\xspace distributing to itself is effective and helpful in enterprises and trusts: it causes men who achieve their goals, who are superior to their enemies, who operate as actors or religious figures, who are successful in business, and who gain prosperity from words or accounts. Especially if \Mercury\xspace is rising, is in operative signs, or is beheld by \Jupiter\xspace and \Venus, it indicates greater trusts and profits. If it is beheld by malefics, it is indicative of anxieties and reversals.

\Mercury\xspace transmitting the year to the \Sun\xspace is associative, effective, and full of accomplishment: it brings
association with the great, requests, gifts (but with delays and obstacles), stewardships, preeminence, and knowledge of religious \textbf{/190P/} matters. It is glorious and beneficial to those involved in letters and education. For the most part, men gain advantage through religion or acting.

\Mercury\xspace distributing to the\Moon\xspace indicates an effective year, especially if the \Moon\xspace happens to be
rising and favorably configured and if <both are> in operative places: it brings associations with males and
females, profits in business, successes, trusts, achievement of goals, and an understanding with the great. If \Mercury\xspace is inappropriately situated and is beheld by malefics, it brings trials, expenses, abuse, threats from the great, imprisonment, anxieties, and the <unholy> revealing of mysteries.

\Mercury\xspace distributing to \Saturn\xspace indicates a disturbed and dangerous year: it brings the ruin of business,
abuse, penalties and trials because of religion, documents, or debts. Men become enfeebled, consumptive, or diseased; they are burdened with bile or attacked with poison. \textbf{/200K/} They see the deaths of family members, brothers, or children, and go to court or have disputes about legacies. If these stars are in opposition or square, or are unfavorably situated and beheld by \Mars, men contrive something dangerous for themselves; they are involved in shipwrecks or typhoons and live miserably. If the stars are suitably configured, they bring rank and success in business—after expenses and delays. If the stars are turned away, they have a moderately crisis-producing effect.

\Mercury\xspace distributing to \Jupiter\xspace is effective and successful: it brings political ties and friendships,
success in business, stewardships and the office of prophet, prosperity in letters or accounts. In general, however, men will have bad reputations among the masses, will suffer scandal and anxieties, will be involved in untimely expenditures, will be disordered in regard to family, friends, or relatives, and will suffer struggles for their own health—if not their own, then for others’.

\Mercury\xspace distributing to \Mars\xspace is not good: it brings hostility and trials, penalties and crime, forgery,
loans, debts, attacks and plunderings, disorder and betrayal, family upheavals. Occasionally men will inflict all this on others: they become bold and active in their assaults; they make their attempts in all directions and contrive assaults; they live in anxiety and upheaval, suspecting crises and anticipating ruin. \textbf{/191P/} \Mercury\xspace distributing to \Venus\xspace indicates a good and effective period, lovely with respect to giving and receiving, purchasing and exchanging. It is helpful to those involved in letters, education, or stewardship. Men acquire ties, new friendships and intimacies, and are involved in affairs with males and
females. To those standing in high fortune it brings the acquisition of slaves and ornaments, and it makes men successful in their requests, friendships, and advancement, and it makes them beneficent to their own people.

\newpage