\section{The Distributions of the Four Lots}

\index{delineation!distribution!lots}
The \mn{Fortune}Lot of Fortune transmitting or receiving in operative places, with benefics in conjunction or aspect, indicates good fortune, advancement, employment, rank, \textbf{/201K}/ success in business, fulfillment of expectations, and profits from legacies. When it precedes an angle or has malefics in aspect, it provides lower employments or ranks; whatever men accomplish will be impermanent and accompanied by reversals and dangers, trials and abuse.

Daimon \mn{Daimon} transmitting or receiving in operative signs, with benefics in aspect brings opportunities which accord with one’s wishes, discerning and easily accomplished plans, helpful advice/contributions from friends, ties with the great, gifts, and rank. It makes men who succeed in their attempts and who are inflated with much self-esteem. If Daimon is unfavorably situated with malefics in aspect it brings
changeable fortunes and emotional anguish, insensibility, cross-purposes. It makes men consider their own mistakes as successes, and makes them lay the blame on others, missing the mark in most respects. As a result such men lose heart; they sometimes contrive danger for themselves, are treated like the insane, and are struck mad.

<The Lot of> Love \mn{Love} transmitting or receiving in operative signs, with benefics in conjunction or aspect, brings about moral desires and makes men lovers of the good: some turn to education and physical or artistic training; they are softened by their delight in their hopes and they do not consider their forethought/goal a matter of difficulty<?>. Others are enchanted by love \textbf{/192P/} and intimacy with men and women, and they consider <this life> to be good. \Mars\xspace and \Mercury\xspace in aspect or in conjunction with this place (especially if they are in their own signs) make homosexuals, men criticized <for affairs> with both sexes, or those who are fond of weapons, hunting, or wrestling. \Venus\xspace <in aspect or conjunction brings> intimacy with women; men when loved will sometimes love in return.

In the same way each star, when allotted this place <Love>, when in aspect, or when receiving the chronocratorship, will bring about the type of desire appropriate to its nature. In general, if malefics are in conjunction or aspect, desires will result in torment, penalties, and danger. Specifically, if \Saturn\xspace is in conjunction or aspect with \Venus\xspace and the \Moon, men will have shameful and unnatural loves, will be criticized for affairs with men and women, \textbf{/202K/} will suffer under scandal, or (even though repenting) will return to their old practices, overcome by passion. If \Jupiter\xspace is also in aspect, what happens will be respectable, powerful, or religious. But if \Mars\xspace and \Mercury\xspace are in conjunction or aspect, or are receiving the chronocratorship, men will love wicked, criminal deeds: they become forgers, robbers, burglars, gamblers, and have a savage character. If \Venus\xspace is also in aspect, they become poisoners, lechers, suicides, and so (according to the applicable chronocrator) they are entangled in loans, debts, and villainy, experience imprisonment and trials, and live in danger. This place is strong in many respects, and so pay much attention to it\footnote{The Lot of Love (for day births) is found by determining the distance from the Lot of Fortune to the Lot of Daimon, then counting that distance from the Ascendant; for night births, the reverse - marginal note [Riley]. \textsl{[According to Paulus it is from Daimon to \Venus (PAG ch.23)]}}.

\enlargethispage{\baselineskip}
<The Lot of> Necessity \mn{Necessity} transmitting or receiving in operative signs, with benefics in conjunction or
aspect, brings family ties, associations with the great, and the downfall or deaths of enemies. If malefics are in conjunction, it brings lawsuits, judgements, and expenses. As a result men fail in their goals and live miserably. If the configuration is afflicted, men are condemned or ruined\footnote{To find it: take the distance from Daimon to Fortune; for night births, the reverse - marginal note [Riley].}.

These result have been determined for the nativities and chronocratorships of men; they will also apply to nativities of women when the configurations of the transmissions are appropriate and the results described can happen <to women>. \textbf{/193K/}

\newpage