\section{The Calculation of the Days}

“You will find the days as follows: multiply the completed full years from the nativity by 5 1/4.
Then add to the result of this multiplication the days from the birth date to the day you are investigating.
If the date is in the Alexandrian calendar, add the intercalary days (i.e. one-fourth of the total years). Then divide this sum by 12. Count the remainder from the sign which has been given control of the month, \textbf{/195P/} giving one to each sign. Examine the ruler of the sign where the count stops, and forecast the quality of the day from the stars which behold it.

“Find the hours as follows: count from the sign which has been given control of the day, giving two to each sign, from the hour of birth. \textbf{/205K/} Then you will know the good and propitious hours. 

This method is excellent for the initiation and beginning of any activity. More particularly, you will accurately
know the sickly and relapsing <hours> from the Ascendant’s relationship to the luminaries and to the other angles of the stars.

“Whatever is necessary for a ready calculation has been declared above; whatever one gains from this brief disclosure, he will make a great contribution to his own welfare, if he has a soul of genius and if he introduces into his inner being the reasoning that man’s mind can attain.

“…If you make the progression <=transmission>, use the hourly <factors> 8, 7, 6, 5, 4, or if <you
use> the year starting with the \Sun\xspace or the month (and this is found by determining the distance from the \Sun\xspace at the time in question to the \Moon\xspace at the nativity, then counting the same distance from the Ascendant of the year), or as I, Hermes, have prescribed. It is necessary to make the progression\footnote{ =vital sector - marginal note [Riley]} from all the stars to all the other stars according to the rising times of the signs in each klima. 

For example: for a wife, daughters, or female individuals, calculate from \Venus; when forecasting concerning actions or related matters, calculate from \Mercury; when forecasting about dangers, death, sickness, or bleeding, calculate from the malefics in aspect with the Ascendant, the \Sun, or the \Moon. Similarly for the other matters. 

It is also necessary to note the terms in which the progressions are located, which stars are casting rays, and which stars are transiting the sign of the progression. Likewise note how the transmitter and the receiver relate to the nativity, how they rose, and how they were at the nativity.

“Another method for the year <=chronocrator>. You will get the years as follows: from the \Sun, which reveals mental matters; from the \Moon, which indicates physical matters and matters about the mother; from the Lot of Fortune. 

It is necessary to inspect how these relate to each other. If they are benefic and appear harmonious, they indicate a good year; if they are malefic, the opposite. 

If they are both benefic and malefic, they forecast that the year too will be varied. The so-called Dog-Star year must be used.” \textbf{/196P/}

\newpage