\section{The Lot of Fortune and Daimon. Their Relationship to the Topics of Propitious and Impropitious Times and of Life (1K, 2P)}

The Lot of Fortune and Daimon have been explained by us in the preceding. Now again we will return to them to confirm that these places are powerful and controlling. To make a comparison: just as in
the universal rotation, the all-seeing sun, whirling in its tireless course, galloping through a time of immense eons, leads the dance of the stars in their varied courses back to the same place, then separates them once again. 

The Sun causes their tropics, their seasons, and their phases, starting where it stopped and stopping where it started. Likewise the Sun charms and arouses the souls of men and becomes the cause of rank, of occupation, and of all success. In a corresponding way the Moon, the Fortune of the universe, waxing and waning under the influence of the Sun’s power, goes through phases, causes the variations in the weather, ripens fruits, and becomes a cause of life for men. 

In the same accusor in every nativity, The Lots of Fortune and of Daimon must be examined to see from which parts \textbf{/332K/} of the universe they emanate. As for their causative force: if these Lots are in operative signs with benefics in aspect, they make nativities propitious, distinguished, and profitable. Particularly if the Lots occur in
masculine signs and their rulers are operative in masculine (or feminine) houses and behold \textbf{/319P/} the place from the right, they cause the greatest and most glorious nativities, those endowed with unparalleled success and advancing to an unsurpassed fortune. 

If the Lots are in masculine signs while their rulers are inoperative in feminine signs and have malefics in opposition or in superior aspect, the place is indicative of decline and ruin and is conducive to poverty and crises of every type. It causes men to be confounded by public, infamous, or royal evils; the end of such men is found to be bad.

With reference to lifespans: the two Lots, when calculated with reference to the Sun and Moon and to their distance <from each other> in degrees, and with reference to the Ascendant, the planet under consideration, and its degree-position, will make clear the span of life: they will measure one-half of the distance/interval forward or back, and will either add to the magnitude of the hour or subtract from it, since the two degrees are operative in the sign by necessity, and since the nativity (although being mortal) takes in the life giving spirit which is in sympathy with the universe. These places must be studied religiously, not carelessly, because from these can be seen and  apprehended the things which heap on men, after much time and toil, the consequences of the influences of these Lots. 

Petosiris did not speak irrelevantly about the sympathy of the Sun and Moon in his book \textit{Oroi} <Factors>: “Whether you measure from the Sun to the Moon and take that distance from the Ascendant,
or from the Moon to the Sun and do likewise, you will find it <the Lot> located at the same point <!>. The Lot controlling the matter in question is seen there, the Lot with reference to which everything
happens and occurs.” 

The King also said in the beginning of his <XIII> Book: “Next in order, it will be necessary to count the distance from the Sun to the Moon, then to measure off an equal distance in the reverse direction (some count forward) from the \textbf{/333K/} Ascendant, and to inspect the ruling place that has been determined: which star is its ruler and which stars are in that place. From the interpretation of these places make a clear determination of the native’s affairs.” (His calling the place “ruling” means “powerful,” and the next phrase “the whole can be seen” means that it is controlling.) 

In addition, in the course of his exposition he often speaks strongly in affirmation of this Lot: that if benefics are in conjunction or in aspect,
\textbf{/320P/} they are indicative of good and givers of property; if malefics, they bring the loss of property and cause bodily wasting, crises, etc.

If the Moon is in a feminine sign at a nativity, this does not bring a good nature to men, but for women born at the same time a <good> basis exists. (This applies to the Sun for those who have the
places and their rulers in masculine and feminine signs.) 

If malefics alone are in conjunction with the  places or incline there, they bring burning, shipwreck, falls from high places, injuries to limbs, bleeding and—particularly when they are in solid signs—either disease symptoms or convulsions. 

Things turn to the worse whenever <malefics> rule the places. We will however explain these matters as we proceed in our exposition, and we will show in varied ways what power is assigned this <Lot> with respect to the propitious times and to the length of life.

Make special note if the Lots are located in \Cancer, \Leo, \Capricorn, or \Aquarius, and are aspected by benefics or by their own stars in operative signs. If the nativity has a illustrious basis, then governors,
kings, and rulers arise, men having the power over life and death, men who have the king’s attention, men thought worthy of gifts and high rank, men successful in their enterprises. Such men are ineffective at first, endure a downtrend in their fortunes and are in despair, but later their fortunes change, and they attain unexpected support, are blessed and called happy by the multitude. 

Those who are assigned a moderate basis are trusted with royal business, are stewards and superintendents—but are subject to ups and downs and hatred. 

Some become or are associated with governors; some receive stipends at the royal \textbf{/334K/} court or in public offices. They are not however elevated so high in their livelihoods as they are sunk in
inglorious display and in careworn, broken misery.

\newpage