\section{Horoscopes for Illnesses. The Initiatives (5K, 6P)}

The determination of forecasts when a patient takes to his bed must be made in the following way: determine the number of days from the new moon <preceding> the nativity to the birth date; divide this by
4. Make a note of the remainder of the division by 4. 

Now we take the days from the new moon of the current \textbf{/326P/} year to the birth date, and we divide that figure by 4. Note the remainder. 

As the third step, it is necessary to take the days from the new moon preceding the illness to the day when the patient took to his bed. Divide this by 4, and compare the remainder with the previous remainders. If the three figures are the same, the time must be judged fatal. If they are different, the danger resulting from the disease, the sickness, or the injury will be escaped.

Through experience we have decided to consider as operative Initiatives not only for the onset of illnesses, but also for the beginning of each and every activity, base or distinguished, elevating or debasing,
average—in short, not only actions that happen to men, but also actions caused by men, e.g. the beginnings of buildings and dedications, expeditions, governorships and commands, base and noble
enterprises. If I wished to speak about each type of enterprise, my discourse on these matters would become endless. Therefore the horoscope will be cast only for the time of the beginning of the enterprise (i.e. the hour), and for the \textbf{/340K/} type of enterprise only (i.e. good or the opposite, enduring or transitory, profitable or damaging).

<I will not be> like some charlatans, who try to predict all activities from one beginning—not only activities but also lifespans—in their attempts to deceive the souls of their clients. It were preferable for
<the astrologer> to cast the horoscope and then to begin to interpret it with sober reasoning, taking into account all the relative positions and the angles, not with a multitude of words, but with brevity leading to
the truth. Such a man then would appear to be a guide to life, a good advisor and and unerring prophet of Fate. Some things however happen to these ignorant men, lovers of money: these flatterers bring false delights and dull man’s reason; while they have the ethereal soul in their keeping, they snatch it from the heavens and dash it to the earth. As a result, most <of their clients> suffer grievous harm and gain for themselves foreknowledge with no foundation.
 
\newpage