\section{That It Is Necessary to Establish Accurately the Hour and Fraction of an Hour of the Nativity}

Since the Ancient Poet, the wise man devoted to the Muses, has hypothesized two Strifes, one of which is warlike and frightful, delighting in bloodshed, \textbf{/358K/} pain, death, battles, hatred, and afflicting crises; the other of which is a hard worker and a lover of beautiful things, peaceful and not unpleasant in her works because she transforms work into pleasure. This god is good, and I myself have become her devotee because I wished to gain victory over my malicious opponents by means of my experience and my scholarship. Because of this I was not satisfied to leave the preceding methods as a pledge to future generations of scholars. No, I have found another powerful method, and I have explained it in such a way that those who confirm the accuracy of my generous gifts step by step with all freedom and sacred striving can silence the malignant and blasphemous voices of my enemies. (The anger fed by hatred and pain is, in fact, dying away, especially when the hostile party comes to defeat.) So, by training themselves with all enthusiasm by means of our compilations, our students will turn criticism of this art to praise, knowing that this science brings pleasure and delight, profit and happiness, and intellectual insight beyond <the reach of> most men. But let us turn our thoughts to the matter at hand.

Take the distance in degrees from the <preceding> new or full moon to the Moon’s position at the delivery. Subtract the distance in signs. Treat the remainder as the “fraction” of the Ascendant. Therefore <make> the precise degree-position of the Moon evident. From this the goal of the investigation will be intelligible, since the Sun referees the length of days and hours according to the differences in klima and the changes of season\footnote{Now even if my statements have received a concise and brief explanation, still the readers should not ignore them and treat them as trivial. They should inquire into them with all care and zeal. In my experience, need, toil, poverty, ambition, self–control, and desire teach most things. We have experienced all of these, and (even if we seem to boast) it has been through these that we have succeeded in attaining the best part of virtue. \textbf{/344P/} Some have failed in this, have been scorned, and have faced misfortune. They have gained an empty fame despite their attempts. - a misplaced fragment}. By itself this “fraction” has the force of an Ascendant. 

Alternatively, take the distance in degrees from the new moon to the moon’s position <at the delivery> according to the rising times. Subtract the distance in signs. Then consider the resulting degree
to be the Ascendant. Do the same from \textbf{/359K/} the full moon to the Moon’s position, or (as seems better to me) from the Moon’s position <at the delivery> to the next new moon. Taking this distance and subtracting the distance in signs, treat the degree that has been determined as the Ascendant. Complete the total of years by adding or subtracting first the equinoctial times. By adding the two gnomons and
dividing by two, you will determine the desired sum according to the real, complex science.

(<“Complex” because> the beginning of any type of thing is simple, variable, and hard to understand, but research into it is complicated and difficult.) If the distance is capable of precise determination, this fact
indicates that the chronocratorship is uniquely determined. 

Wherefore, my dearest Marcus, if you know the numerical tables and the methods of their composition—and you have proven that you do by word and deed and through the traditions handed down to you by me—and if you apply your natural powers of analysis, and if you make it your goal to carry out your operations with all precision, viz. when you visit the many nations and climes of the world and when you display your talents there, then you will make me worthy of undying fame, and you yourself will be glorified among the people as worthy of this heavenly art. 

You, having laid a foundation with the abundance of your learning, will attain the status of treatise writer yourself. For you have the nature, the energy, and the self-mastery necessary for this, and you possess the illuminated, mystic initiation into this art, having found the sacred and holy entrance to it. I urge you by the previously mentioned oaths to guard this art and to hide it from the unworthy or the uninitiate, and never to act contentiously against them. For it is better for you to be silent and be defeated, rather than to win victory while showing disrespect for divine matters.
\newpage