% Section 1 of Book 1

\section{The Nature of the Stars}

\subsection{\textit{[Sun]}}
\marginnote{{\tiny Sun} \Sun}[0.2cm]
In a nativity the all-seeing \index{planets!Sun}
\Sun\index{Sun!significations}, nature’s fire and intellectual light, the organ of mental \index{perception}perception.

\textbf{Indicates:} \index{king}kingship, rule, \index{intellect}intellect, intelligence, \index{beauty}beauty, motion, \index{fortune}loftiness of fortune, the ordinance of the gods, \index{judgment}judgment, public \index{reputation}reputation, action, \index{authority}authority over the masses, \index{father}the father, \index{master}the master, \index{friendship}friendship, \index{nobles}noble personages, \index{honors}honors consisting of pictures, statues, and garlands, high priesthoods, <rule over> one’s country <and over> other places. \\
\\
\textbf{Of the parts of the body:} the \Sun\, rules the \index{head}head. \\
\textbf{Of the sense organs:} it rules \index{eyes!right}the right eye. \\
\textbf{Of the trunk:} it rules the \index{heart}heart.\\
\textbf{Of the spiritual (i.e. the perceptive) faculties:} the \index{nerves}nerves.\\
\textbf{Of materials:} it rules \index{gold}gold. \\
\textbf{Of fruits:} it rules \index{wheat}wheat and \index{barley}barley. \\
\\
\textbf{Sect:} \index{sect!day}day. \\
\textbf{Colour:} \index{color!yellowish}yellowish. \\
\textbf{Taste:} \index{taste!bitter}bitter.
% ---------------
\secbr
\subsection{\textit{[Moon]}}
\marginnote{{\tiny Moon} \Moon}[0.2cm]

The \index{planets!Moon}\Moon\index{Moon!significations}, lit by the reflection of the \Sun’s light and possessing a borrowed light, in a nativity \ldots \\
\\
\textbf{Indicates:} man’s \index{life}life, \index{body}body, \index{mother}the mother, \index{conception}conception, <beauty>, \index{appearance}appearance, \index{sight}sight, \index{marriage}living together (i.e. legitimate marriage), \index{nurture}nurture, \index{brothers!older}the older brother, \index{housekeeping}housekeeping, \index{queen}the queen, \index{household!mistress}the mistress of the house, \index{possessions}possessions, \index{fortune}fortune, \index{city}the city, \index{people}the assembly of the people, \index{gains}gains, \index{expenses}expenses, \index{household}the household, \index{voyages}voyages, \index{travel}travel and wanderings (it does not provide straight pathways because of \Cancer
\footnote{Schmidt, in his translation of Valens has this line as ``for, it does not maintain a straight line through \Cancer.''(VRS1)}). \\
\\
\textbf{Body:} The \Moon\, rules the parts of the body as follows: \index{eyes!left}the left eye, \index{stomach}the stomach, \index{breasts}the breasts, \index{breath}the breath, \index{spleen}the spleen, the dura mater, \index{marrow}the marrow (as a result it causes dropsy/moist syndromes). \\
\\
\textbf{Of materials:} it rules \index{silver}silver and \index{glass}glass. \\
\\
\textbf{Sect:} It is of \index{sect!night}the night sect \\
\textbf{Color:} \index{color!green}green in color, and, \\
\textbf{Taste:} \index{taste!salty}salty in taste. \textbf{/2K/}
% ----------------
\secbr
\subsection{\textit{[Saturn]}}
\marginnote{\tiny{Saturn} \Saturn}[0.2cm]

\index{planets!Saturn}\Saturn\index{Saturn!significations} makes those born under him \index{petty}petty, \textbf{/2P/} \index{malignant}malignant, \index{care-worn}care-worn, \index{self-depreciating}self-depreciating, \index{solitary}solitary, \index{deceitful}deceitful, \index{secretive}secretive in their trickery, \index{strict}strict, \index{downcast}downcast, with a \index{hypocrite}hypocritical air, \index{squalid}squalid, black-clad, \index{importunate}importunate, \index{sad}sad-looking, \index{miserable}miserable, with a nautical bent, \index{jobs!waterside}plying waterside trades. 

Saturn also causes \index{humblings}humblings, \index{sluggishness}sluggishness, \index{unemployment}unemployment, \index{business!obstacles}obstacles in business, \index{lawsuits}interminable lawsuits, subversion of business, \index{secrets}secrets, \index{imprisonment}imprisonment, \index{chains}chains, \index{griefs}griefs, \index{accusations}accusations, \index{tears}tears, \index{bereavement}bereavement, \index{capture}capture, \index{children!exposure of}exposures of children. 

\Saturn\, makes \index{jobs!serf}serfs and \index{jobs!farmer}farmers because of its rule over the land, and it causes men to be renters of property, tax farmers, and violent in action. 

It puts into one’s hands great \index{rank}ranks and distinguished positions, supervisions, \index{jobs!manager}management of others’ property, and the fathership of others’ children. \\
\\
\textbf{Of materials:} it rules \index{lead}lead, \index{wood}wood, and \index{stone}stone. \\
\textbf{Of the limbs of the body:}, it rules the \index{legs}legs, the \index{knees}knees, the \index{tendons}tendons, the \index{lymphs}lymph, the \index{phlegm}phlegm, the \index{bladder}bladder, the \index{kidneys}kidneys, and the \index{organs!internal}internal, hidden organs. \\
\\
\textbf{Indicates:} \Saturn\, is indicative of injury injuries arising from cold and moisture, such as \index{dropsy}dropsy, \index{neuralgia}neuralgia, \index{gout}gout, \index{cough}cough, \index{dysentery}dysentery, \index{hernia}hernia, \index{spasms}spasms. It is indicative of these syndromes: \index{possession}possession, \index{homosexuality}homosexuality, and \index{depravity}depravity. 

\Saturn\, makes \index{bachelors}bachelors and \index{widows}widows, \index{bereavement}bereavements, and \index{childlessness}childlessness. It causes \index{death!violent}violent deaths by water, \index{strangulation}strangulation, \index{imprisonment}imprisonment, or \index{dysentery}dysentery. It also causes falling on the face. It is the star of \index{Nemesis, star of}Nemesis. \\
\\
\textbf{Sect:} it is of the \index{sect!day}day sect.\\
\textbf{Colour:} It is like \index{color!castor}castor in color and \\
\textbf{Taste:} \index{taste!astringent}astringent in taste.

% -----------------
\secbr
\subsection{\textit{[Jupiter]}}
\marginnote{\tiny{Jupiter} \Jupiter}[0.2cm]
\noindent
\textbf{Indicates:} \index{planets!Jupiter}\Jupiter\index{Jupiter!significations} indicates \index{childbearing}childbearing, engendering, \index{desire}desire, \index{love}loves, \index{politics!ties}political ties, acquaintance, \index{friendship}friendships with great men, \index{prosperity}prosperity, \index{salaries}salaries, great \index{gifts}gifts, \index{crops}an abundance of crops, \index{justice}justice, \index{politics!offices}offices, office holding, \index{rank}ranks, \index{temples, authority over}authority over temples, \index{arbitration}arbitrations, \index{trusts}trusts, \index{inheritance}inheritance, \index{brotherhood}brotherhood, \index{fellowship}fellowship, \index{beneficence}beneficence, \index{possessions}the secure possession of goods, \index{relief}relief from troubles, release from bonds, \index{freedom}freedom, \index{deposits}deposits in trust, \index{money}money, \index{stewards}stewardships. \\
\\
\textbf{Of the external body parts:} it rules the \index{thighs}thighs and the \index{feet}feet. (Consequently in the games \Jupiter\, governs the \index{games!racing}race.)\\
\textbf{Of the internal parts:}  it rules the \index{sperm}sperm, the \index{uterus}uterus, the \index{liver}liver, \index{body!right side}the parts of the right side. \\
\textbf{Of materials:} it rules \index{tin}tin. \\
\\
\textbf{Sect:} It is of the \index{sect!day}day sect. \\
\textbf{Color:} In color it is \index{color!gray}gray verging on white and \\
\textbf{Taste:} is \index{taste!sweet}sweet in taste.

% ---------------
\secbr
\subsection{\textit{[Mars]}}
\marginnote{\tiny{Mars} \Mars}[0.2cm]
\noindent
\textbf{Indicates:} \index{planets!Mars}\Mars\index{Mars!significations} indicates \index{force}force, \index{war}wars, \index{plunder}plunderings, \index{screams}screams, \index{violence}violence, \index{whoring}whoring, \index{property!loss}the loss of property, \index{banishment}banishment, \index{exile}exile, \index{parents!alienation from}alienation from parents, \textbf{/3P/} \index{capture}capture, \index{death!wife}the deaths of wives, \textbf{/3K/} \index{abortion}abortions, \index{love!affairs}love affairs, \index{marriage}marriages, \index{possessions!loss}the loss of goods, \index{lies}lies, \index{hopes}vain hopes, strong-armed \index{theft!robbery}robbery, \index{bandits}banditry, \index{loot}looting, \index{friends!quarrels}quarrels among friends, \index{anger}anger, \index{fights}fighting, \index{abuse!verbal}verbal abuse, \index{hate}hatreds, \index{lawsuit}lawsuits. 

\Mars\, brings \index{murder}violent murders, \index{slaghing}slashings and \index{bloodshed}bloodshed, \index{fever}attacks of fever, \index{ulcers}ulceration, \index{boils}boils, \index{burns}burns, \index{chains}chains, \index{torture}torture, \index{masculine}masculinity, \index{oaths}false oaths, wandering, \index{embassy!difficult}embassies under difficult
circumstances, actions involving \index{fire}fire or \index{iron}iron, \index{jobs!craftwork}craftwork, \index{jobs!masonry}masonry. 

In addition \Mars\, causes \index{jobs!commands}commands, \index{campaigns}campaigns and \index{leadership}leadership, \index{jobs!infantry}infantrymen, \index{jobs!governor}governorships, \index{hunting}hunting, \index{game!wild}wild game, \index{falls}falls from heights or from animals, \index{eyes!weak}weak vision, \index{strokes}strokes. \\
\\
\textbf{Of the body part:} \Mars\, rules the \index{head}head, \index{seat}the seat, the \index{genitals}genitals. \\
\\
\textbf{Of the internal parts:} it rules the \index{blood}blood, the \index{sperm!ducts}sperm ducts, the \index{bile}bile, the elimination of \index{excrement}excrement, the parts in the \index{rear}rear, the \index{back}back, and the underside. It controls the hard and the abrupt. \\
\\
\textbf{Of materials:} it rules \index{iron}iron, \index{clothing!decoration}decoration of clothing (because of \Aries), as well as \index{wine}wine and \index{beans}beans. \\
\\
\textbf{Sect:} It is of the \index{sect!night}night sect. \\
\textbf{Colour:} \index{color!red}red in color and \\
\textbf{Taste:} \index{taste!acid}acid in taste.

% --------------
\secbr
\subsection{\textit{[Venus]}}
\marginnote{\tiny{Venus} \Venus}[0.2cm]
\index{planets!Venus}\Venus\index{Venus!significations} is \index{desire}desire and \index{love}love. \\
\\
\textbf{Indicates:} It indicates the \index{mother}mother and \index{nurture}nurture. It makes \index{jobs!priests}priesthoods, \index{jobs!school adminstrator}school superintendencies, \index{rank!high office}high offices with the right to wear a \index{ring!gold}gold ring or a \index{crown}crown, \index{cheerfulness}cheerfulness, \index{friendship}friendship, \index{companionship}companionship, the \index{propery!acquisition}acquisition of property, the purchase of \index{ornaments}ornaments, \index{agreements}agreements on favorable terms, \index{marriage}marriages, pure trades, \index{voice!fine}fine voices, \index{music}a taste for music, \index{singing}sweet singing, \index{beautry}beauty, \index{painting}painting, \index{colors!mixing}mixing of colors both in \index{embroidery}embroidery, \index{dyeing}dyeing, and unguent making. <\Venus\, makes> the \index{jobs!inventor}inventors and masters of these \index{jobs!craftsman}crafts, as well as craftsmanship or trade, and work in \index{jobs!jeweller}emeralds\index{emeralds}, \index{stones! precious}precious stones, and \index{ivory}ivory. 

\mndl[0.2cm]
Within its terms and degrees in the zodiac, \Venus\, causes men to be \index{jobs!goldsmiths}gold-spinners, gold workers, \index{jobs!barbers}barbers, and people fond of \index{cleanliness}cleanliness and \index{jobs!toy makers}toys. 

It bestows the \index{jobs!weights and measures}office of supervisor of weights and measures, the standards of weights and measures, \index{jobs!marketer}markets, \index{jobs!factory worker}factories, \index{gifts}the giving and receiving <of gifts>, \index{laughter}laughter, good cheer, \index{ornaments}ornamentation, and \index{hunter}hunting in moist places.

\Venus\, gives benefits from \index{royals!women}royal women or from one’s own, and it brings very high \index{rank!high}rank when it operates in such affairs. \\
\\
\textbf{Of the parts of the body:} it rules the \index{neck}neck, the \index{face}face, the \index{lips}lips, the sense of \index{sense!smell}smell, the \index{body!fron from head to foot}front parts from the feet to the head, the \index{organs!sexual}parts of intercourse. \\
\\
\textbf{Of the inner parts:} \textbf{/4P/} it rules the \index{lungs}lungs. It is a recipient of \index{support}support from others and of \index{pleasure}pleasure.\\ 
\\
\textbf{Of materials:} \textbf{/4K/} it rules \index{stones!precious}precious stones and \index{jewelry}fancy jewelry. \\
\\ 
\textbf{Of fruits:} it rules the \index{olive}olive. \\
\\
\textbf{Sect:} It is of the \index{sect!night}night sect.\\
\textbf{Color:} \index{color!white}white in color. \\
\textbf{Taste:} \index{taste!greasy, very}very greasy in taste.

% ----------------
\secbr
\subsection{\textit{[Mercury]}}
\marginnote{\tiny{Mercury} \Mercury}[0.2cm]
\noindent
\textbf{Indicates:} \index{planets!Mercury}\Mercury\index{Mercury!significations} indicates \index{education}education, \index{letters}letters, \index{disputes}disputation, \index{reason}reasoning, \index{brotherhood}brotherhood, \index{interpretation}interpretation, \index{embassies}embassies, \index{number}number, \index{accounts}accounts, \index{geometry}geometry, \index{markets}markets, \index{youth}youth, \index{games}games, \index{theft}theft, \index{association}association, \index{communication}communication, \index{service}service, \index{gain}gain, \index{discovery}discoveries, \index{obedience}obedience, \index{sport}sport, \index{wrestling}wrestling, \index{declamation}declamation, \index{certification}certification, \index{supervision}supervision, \index{weights and measures}weighing and measuring, the testing of \index{coins}coinage, \index{sense!hearing}hearing, \index{versatility}versatility. 

It is the bestower of \index{forethought}forethought and \index{intelligence}intelligence, the lord of \index{brothers}brothers and of \index{children!young}younger children, and the creator of all \index{marketing}marketing and \index{banking}banking. 

In its own character, it makes \index{jobs!builder!temples}temple builders, \index{jobs!modeler}modelers, \index{jobs!sculptor}sculptors, \index{jobs!doctor}doctors, \index{jobs!secretary}secretaries, \index{jobs!advisor, legal}legal advisors, \index{jobs!orator}orators, \index{jobs!philosopher}philosophers, \index{jobs!architect}architects, \index{jobs!musician}musicians, \index{jobs!prophet}prophets, \index{jobs!diviner}diviners, \index{jobs!augur}augurs, \index{jobs!interpreter, dreams}dream interpreters, \index{jobs!braider}braiders, \index{jobs!weaver}weavers, \index{jobs!physician}systematic physicians, those in charge of \index{jobs!strategist}war and strategy, and those undertaking any unusual, systematic work in \index{jobs!accountant}accounting or \index{jobs!logician} with reasoning. 

\Mercury\, makes \index{jobs!weight lifters}weight lifters and \index{mimes}mimes, those making their livelihood with \index{jobs!gambler}displays of skill, \index{jobs!con artist}deception, gambling, or \index{jobs!magician}sleight of hand. It also rules those \index{jobs!astrologer}skilled interpreters of the heavens, those who by \index{jobs!actor}using pleasure or winning charm, earn fame for their amazing feats—all for the sake of gain. 

\mndl[0.2cm]
This star’s effects go in many directions, depending on the changes of the zodiac and the interactions of the stars, and yields quite varied results: knowledge for some, selling for others, service for others, trade or \index{jobs!teacher}teaching for others, farming or temple service or \index{jobs!public office}public <employment> for still others. 

To some it grants authority, rentals, labor contracting, \index{jobs!performer}rhythmical performance, the display of public service, the acquisition of personal attendants or the \index{jobs!priest}right of wearing temple-linen, robed in the luxury appropriate to gods or rulers. 

\mndl[0.2cm]
As for the end result—\Mercury\, will make everything \index{capricious}capricious in outcome and quite disturbed. Even more, it causes those having this star in malefic signs or degrees to become even worse. \\
\\
\textbf{Of the parts of the body:} it rules the \index{hands}hands, the \index{shoulders}shoulders, the \index{fingers}fingers, the \index{joints}joints, the \index{belly}belly, the sense of \index{senses!hearing}hearing, the \index{arteries}arteries, \textbf{/5P/} the \index{intestines}intestines, the \index{tongue}tongue. \\
\\
\textbf{Of materials:} it rules \textbf{/5K/} \index{copper}copper and all coins used in buying and selling—for the god makes exchanges.\ldots\footnote{Information on \Mercury's sect is missing. Ptolemy says he is diurnal when rising, as the ``morning star,'' and nocturnal when setting as the ``evening star'' (PTR I.7 p43).} <It is blue in color, sharp in taste.>

% ----------------
\secbr
\subsection{\textit{[General Indications]}}
\mndl[0.2cm]
The \index{planets!general} \index{planets!benefics!condition} benefic stars  which are appropriately and favorably situated bring about their proper effects according to their own nature and the nature of their sign, with the aspects and conjunctions of each star being blended. If however they are unfavorably situated, they are indicative of reversals. 

\mnmb[0.2cm] 
In the same way even the \index{planets!malefic!condition} malefic stars, when they are operative in appropriate places in their own sect, are bestowers of good and indicative of the greatest positions and success; when they are inoperative, they bring about disasters and accusations.

\mnm[0.2cm]
\ldots Each star is the ruler of its own “element” in the universe with reference to <the stars’> sympathy or
antipathy or mutual influence. Their <aspects> are blended according the their “applications” or
“separations,” their “superior aspects” or “blockages,” their “attendance,” their “ray-shooting,” or the
“approach” of their masters. \\
\\
The \Moon\, \index{Moon!significations} becomes the ruler of \index{foresight}foresight. \\
The \Sun\, \index{Sun!significations} the ruler of \index{light}light. \\
\Saturn\, \index{Saturn!significations} the ruler of \index{ignorance}ignorance and \index{necessity}necessity. \\
\Jupiter\,\index{Jupiter!significations} the ruler of \index{rank}rank, \index{crowns}crowns and \index{zeal}zeal. \\
\Mars\,\index{Mars!significations} becomes the ruler of \index{action}action and \index{effort}effort. \\
\Venus\,\index{Venus!significations} the ruler of \index{love}love, \index{desire}desire, and \index{beautry}beauty. \\
\Mercury\,\index{Mercury!significations}  the ruler of \index{law}law, \index{friendship}friendship, and \index{trust}trust. 

These stars have their own effects\ldots.

Now that these matters have been settled, the nature of the twelve signs must be mentioned.
\newpage