% Section 2 of Book 1 - Zodiac Signs

\section{The Nature of the Twelve Zodiacal Signs}
\subsection{\textit{[Aries]}}
\marginnote{\tiny{Aries} \Aries}[0.2cm]
\index{signs!Aries} Aries is the house of \Mars, a \index{signs!masculine} masculine sign, \index{signs!tropical} tropic, \index{signs!terrestial} terrestrial, \index{signs!governing}governing, \index{signs!fiery} fiery, free, upward-trending, \index{signs!semi-vocal} semi-vocal, \index{signs!noble}noble, \index{signs!changeable}changeable, procuratorial, public, civic, \index{signs!fertile}with few offspring, \index{signs!servile} servile, the Midheaven\footnote{Reference is to the \href{http://planetwavesweekly.com/dadatemp/1832374392.html}{Thema Mundi} where Aries is on the MC and Cancer on the the Ascendant (VRS1 p8)} of the universe and the cause of rank, two-toned (since the Sun and the Moon make white lichen). It is also unaspected and \index{signs!ecliptic}ecliptic. 

\mndl[0.2cm]
\index{character!\Aries}Depending on its relationship with the houseruler, men born under this sign will be \index{mind!brilliant}brilliant, \index{character!distinguished}distinguished, \index{character!authoritarian}authoritarian, \index{character!just}just, \index{character!hard}hard on offenders, free, governing, \index{mind!bold}bold in thought, \index{character!boastful}boastful, \index{character!great-hearted}great-hearted, \index{character!restless}restless, \index{character!unstable}unstable, \index{character!haughty}haughty, \index{character!inflated}inflated, \index{character!intimidating}intimidating, \textbf{/6K/} \index{character!changeable}quickly changing, wealthy. 

\mndl[0.2cm]
When the houserulers are favorably situated and have benefics in aspect, \index{jobs!king}kings and \index{character!powerful}powerful men are born, those having the say over life and death.

\index{signs!climate!\Aries}\textbf{Climate:} \textbf{/6P/} \Aries\, is by nature \index{climate!watery}watery, with \index{climate!thunder}thunder and \index{climate!hail}hail. From its first degree to the equinox, it is \index{climate!stormy}stormy, full of hail, \index{climate!windy}windy, \index{climate!destructive}destructive. The middle degrees up to 15\deg are \index{climate!mild}mild <and fruitful; the following degrees are \index{climate!hot}hot and cause \index{plagues}plagues> of animals. 

\index{fixed stars!Aries}\textbf{Fixed Stars:} This sign has 19 bright stars. On the belt are 14 bright stars, 27 dim, 28 somewhat bright, and 48 faint. 

\textbf{Paranatellonta:} The constellations that rise at the same time as \Aries\, are (in the north) the first part of \index{constellations!Perseus}Perseus, and the rear and the left parts of \index{constellations!Auriga}Auriga, and (in the south) the fin and tail of \index{constellations!Cetus}Cetus. <When Aries is rising,> the feet of \index{constellations!Bootes}Bootes (in the north) and the hind parts of \index{constellations!Lupus}Lupus (in the south) are setting.

\textbf{Zones:} The following zones are subject to \Aries: 
\begin{itemize}
\item to the front parts, \index{states!Babylon}Babylon; 
\item to the head, \index{states!Elymais}Elymais; 
\item to the rightside, \index{states!Persis}Persis; 
\item to the left, \index{states!Palestine}Palestine and the neighboring areas; 
\item to the turn of its head, \index{states!Babylonia}Babylonia; 
\item to its breast, \index{states!Armenia}Armenia; 
\item to its shoulders, \index{states!Thrace}Thrace; 
\item to its belly, \index{states!Cappadocia}Cappadocia, \index{states!Susa}Susa, \index{seas!Red Sea}the Red Sea and the \index{seas!Dead Sea}Dead Sea; 
\item to its hind parts, \index{states!Egypt}Egypt and the \index{seas!Indian Ocean}Indian Ocean.
\end{itemize}

% ----------
\secbr
\subsection{\textit{[Taurus]}}
\marginnote{\tiny{Taurus} \Taurus}[0.2cm]
\index{signs!Taurus} \Taurus\, is \index{signs!feminine} feminine, \index{signs!solid} solid, lying in the \Sun’s spring \index{sigsns!tropical}tropic, full of bones, with some limbs missing, rising backwards, setting straight down. 

\index{signs!climate!\Taurus}\textbf{Climate:} This sign lies for the most part in the invisible sky. It is \index{climate!calm}calm. From its first degree to 6\deg (the section of the Pleiades) it is worthless, even \index{climate!destructive}destructive, disease-producing, \index{climate!thunder}thundering, causing \index{climate!earthquakes}earthquakes and \index{climate!lightning}lightning flashes. The next two degrees are \index{climate!fiery}fiery and \index{climate!smokey}smokey. The right part (toward Auriga) is \index{climate!temperate}temperate and \index{climate!cool}cool. The left parts are worthless and changeable, sometimes \index{climate!chill}chilling, at other times \index{climate!hot}heating. The head (to 23\deg) is in a \index{climate!temperate}temperate atmosphere, but it causes disease and death for living things. The rest is\index{climate!destructive} destructive, worthless, disease-ridden.

\textbf{Fixed Stars:} It has 27 stars. \textbf{/7K/}

\textbf{Paranatellonta:} The constellations that rise with it are (in the north) the rear of \index{constellations!Auriga}Auriga and (in the south) the rear of \index{constellations!Cetus}Cetus and the first section of \index{constellations!Eridanus}Eridanus. \Venus, the \Moon, \index{Ceres}Ceres, \index{Vesta}<Vesta,> \Mars, and \Mercury. The constellations that set <when \Taurus\, is rising> are (in the north) \index{constellations!Bootes}Bootes up to the belt and the leg of \index{constellations!Ophiouchus}Ophiouchus up to the knees. In the south \index{constellations!Orioin}Orion rises with \Taurus; he is belted around the waist, extends his sword in his right hand, \textbf{/7P/} and holds in his left hand the so-called caduceus.

This sign is \index{signs!fixed}productive of order, \index{signs!earthy} earthy, rustic, related to \index{jobs!farmer}farming, a freedman, downward-trending, \index{signs!fertility}with few offspring, \index{signs!semi-vocal} semi-vocal and \index{signs!mute} mute, \index{signs!noble}noble, \index{character!stable}invariable, \index{character!energetic}energetic, \index{character!unfinished}unfinished, indicative of \index{estates}estates and \index{possessions}possessions. 

The ecliptic lies to the north, rising in line with its <\Taurus’s> highest point. \index{character!\Taurus}Men born under this sign are \index{character!noble}noble, \index{character!energetic}energetic, \index{character!toilsome}toilsome, good at keeping things, \index{character!pleasure-loving}pleasure-loving, \index{character!music-loving}music-loving, \index{character!generous}generous. Some are \index{jobs!laborers}laborers, \index{jobs!propagators}propagators, \index{jobs!planters}planters. 

If benefics incline toward this place or if the houseruler is favorably situated, men become \index{jobs!priests}priests and \index{jobs!school superintendants}school superintendants, as well as \index{jobs!leaders}those judged worthy of crowns and of the purple, of monuments and statues; also \index{jobs!temple supervisors}supervisors of temples and \index{character!distinguished}distinguished and \index{mind!brilliant}brilliant individuals.

\textbf{Zones:} The following zones are subject to \Taurus: 
\begin{itemize}
\item to its head,\index{states!Media} Media and the adjoining areas; 
\item <to its breast, \index{states!Babylon}Babylon; 
\item to the right side toward Auriga, \index{states!Scythia}Scythia;> 
\item to the Pleiades, \index{states!Cyprus}Cyprus; 
\item to the left side, \index{states!Arabia}Arabia and the surrounding areas; 
\item to its shoulders, \index{states!Persis}Persis and the \index{states!Caucasus}Caucasus mountains; 
\item to its truncated portion, \index{states!Sarmatia}<Sarmatia>; 
\item to its loin, \index{states!Africa}Africa; 
\item to its torso, \index{states!Elymais}Elymais; 
\item to its horns, \index{states!Carthage}Carthage; 
\item to its midparts, \index{states!Armenia}Armenia, \index{states!India}India,\index{states!Germany}Germany.
\end{itemize}

% -----------------------------------------------------------
\secbr
\subsection{\textit{[Gemini]}}
\marginnote{\tiny{Gemini} \Gemini}[0.2cm]

\index{signs!Gemini} \Gemini\, is \index{signs!masculine} male, \index{signs!bicorporeal} bicorporeal, \index{character!articulate}articulate, the house of \Mercury, upward-trending, celestial, feminizing, a freedman, \index{signs!sterile} sterile, \index{signa!public}public. 

Under it are born \index{jobs!scholars}scholars, those working in \index{jobs!educators}education and letters, \index{jobs!poets}poets, \index{jobs!music-lovers}music lovers, \index{jobs!rhetorician}declaimers\footnote{One who speaks rhetorically.}, \index{jobs!stewards}stewards, \index{jobs!trustee}those who receive trusts; also \index{jobs!translator}translators, \index{jobs!merchant}merchants, \index{jobs!judge}judges of good and evil, \index{mind!sensible}sensible people, \index{jobs!occultist}practicioners of the curious arts, and seekers after mystic lore\footnote{Occultists}. 

\mndl[0.2cm]
In general, whatever the houseruler usually produces according to its own nature, whether good or bad, greater or lesser, this it produces in each of the signs according to the operative or inoperative \textbf{/8K/} configuration of the houseruler. (I mention this so that we will not seem to be constantly writing the same thing.)

\index{signs!climate!\Gemini}\textbf{Climate:} This sign is \index{climate!calm}calm. Its first 3\deg are worthless and \index{climate!desctructive}destructive; from 3\deg to 7\deg it is \index{climate!wet}well-watered; good weather from 7\deg to 15\deg. The southern parts are well-watered. The last degrees are a combination of traits.

\textbf{Fixed Stars:} It has 21 stars. 

\textbf{Paranatellonta:} It lies toward the west wind. According to the Sphaerica, \textbf{/8P/} the tail of \index{constellations!Cetus}Cetus lies touching \Gemini\, at one of its southern points; also at its southern point, on the due-south line, is the \index{constellations!Orion}\index{constellations!Satyr!see {constellations, Orion}}Satyr <=Orion> touching it with its club, and it rises after the north part of Satyr, where the spear is. \index{constellations!Lyra}Lyra lies to the south; it lies on the due-south line, being midway between north and south. Under \Gemini’s feet on the due-south line (in the hemisphere visible to us) is the so-called \index{constellations!Canis}Canis in front of its right foot; Canis is cut by a line running from the south pole through \Gemini's head straight to the north pole. 
\Gemini\, rises with the rest of \index{constellations!Eridanus}Eridanus and \index{constellations!Orion}Orion in the south. The gods \index{gods!Apollo}Apollo, \index{gods!Hercules}Hercules, \index{gods!Vulcan}Vulcan, \index{gods!Juno}Juno, \index{gods!Saturn}Saturn are associated with it. To the north, \index{constellations!Bootes}Bootes, \index{constellations!Ophiouchus}Ophiouchus (except the head), and half of the \index{constellations!Crown}Crown set <when \Gemini\, rises>. 

\textbf{Zones:} The following zones are subject to \Gemini: 
\begin{itemize}
\item to the front part, \index{states!India}India and the adjoining areas and \index{states!Celtica}Celtica; 
\item to the breast, \index{states!Cilicia}Cilicia, \index{states!Galatia}Galatia, \index{states!Thrace}Thrace, and \index{states!Boeotia}Boeotia; 
\item to the midparts, \index{states!Egypt}Egypt, \index{states!Libya}Libya, \index{states!Rome}Rome, \index{states!Arabia}Arabia, \index{states!Syria}Syria.
\end{itemize}

% ------------------------------------------------------------
\secbr
\subsection{\textit{[Cancer]}}
\marginnote{\tiny{Cancer} \Cancer}[0.2cm]

\index{signs!climate!\Cancer}\textbf{Climate:} \index{signs!Cancer} \Cancer\, is \index{climate!calm}calm. The parts are as follows: under the two initial stars to the southeast, it is worthless, \index{climate!destructive}destructive, stifling, productive of \index{climate!earthquakes}earthquakes. From that point to 10\deg it makes the air \index{climate!damp}damp and \index{climate!hot}hot, having \index{climate!wet}heavy rains and constant \index{climate!thunderstorms}thunderstorms. The right parts are worthless and destructive. 

\textbf{Paranatellonta:} In the north the \index{constellations!Hare}Hare, the front part of \index{constellations!Canis Major}Canis Major, and \index{constellations!Procyon}Procyon rise with \Cancer. It has 4 stars. \Mars, \Mercury, \Jupiter, <\Neptune>, \Venus. To the north, the head of \index{constellations!Bootes}Bootes sets as \Cancer\, rises, as well as \index{constellations!Hercules}Hercules, \index{constellations!Aquila}Aquila, and half of the \index{constellations!Crown}Crown.

It is the house of the \Moon, \index{signs!feminine} feminine, \index{signs!solstitial} solstitial, the Ascendant to the universe\footnote{In the \textit{Thema Mundi}.}, \index{signs!servile} slavish, downward trending, \index{signs!mute} mute, \index{signs!watery} watery, \index{character!noble}noble, \textbf{/9K/} \index{character!changeable}changeable, \index{signs!public}public, \index{character!popular}popular, civic, \index{signs!prolific} prolific, \index{signs!amphibious}amphibious. 

\index{character!\Cancer}Men born under this sign are \index{character!ambitious}ambitious, popular, \index{character!changeable}constantly changing, \index{character!theatrical}theatrical, \index{character!cheerful}cheerful, easily downcast, \index{character!pleasure loving}pleasure loving, \index{character!party-giving}party-giving, public. 

\index{mind!unsteady}Unsteady of mind, they say one thing but think another, and not sticking to one activity or (at the most) two, they become \index{character!wanderers}wanderers and \index{character!travelers}travelers.

\textbf{Zones:} The following zones are subject to \Cancer: 
\begin{itemize}
\item to the front, \index{states!Bactria}Bactria; \textbf{/9P/}
\item to the left, \index{states!Zakynthus}Zakynthus and \index{states!Acarnania}Acarnania; 
\item to the back, \index{states!Ethiopia}Ethiopia and \index{states!Schina}Schina;
\item under the head are the \index{seas!Crimean Gulf}Crimean Gulf and the tribes surrounding it, the \index{seas!Read Sea}Red Sea, the \index{seas!Caspian Sea}Caspian Sea, the \index{seas!Hellespont}Hellespont, the \index{seas!Libyan Sea}Libyan Sea, \index{states!Britain}Britain, and \index{states!Thule}Thule. 
\item Under the feet are \index{states!Armenia}Armenia, \index{states!Cappadocia}Cappadocia, \index{states!Rhodes}Rhodes, \index{states!Kos}Kos. \item Under the tip of \Cancer\, (i.e. at the mouth) are \index{states!Troglodytia}Troglodytia, \index{states!Lydia}<Lydia>, \index{states!Ionia}Ionia, and the Hellespont.
\end{itemize}

% -----------------------------------------------------------
\secbr
\subsection{\textit{[Leo]}}
\marginnote{\tiny{Leo} \Leo}[0.2cm]

\index{signs!Leo} \Leo\, is \index{signs!masculine}masculine, the house of the \Sun, free, \index{signs!fiery} fiery, \index{signs!temperate}temperate, \index{signs!intellectual}intellectual, \index{signs!royal}kingly, \index{signs!stable}stable, \index{signs!noble}noble, upward-trending, \index{signs!changeable}changeable, \index{signs!solid} solid, \index{signs!governing}governing, civic, \index{character!imperious}imperious, \index{character!irascible}irascible.

\index{character!\Leo}Men born under this sign are \index{character!distinguished}distinguished, noble, \index{character!steady}steady, \index{character!just}just, haters of evil, \index{character!independent}independent, haters of flattery, \index{character!beneficent}beneficent, \index{character!inflated}inflated with their lofty thoughts. 

\mndl[0.2cm]
If the houseruler is at an angle or in aspect with benefics, then \index{character!brilliant}, \index{character!glorious}glorious individuals are born, \index{character!tryant}tyrants and kings.

\index{signs!climate!\Leo}\textbf{Climate:} \Leo\, is \index{signs!climate!hot}hot: the bright star in its breast <Regulus> is fiery and \index{signs!climate!stifling}stifling. The parts are as follows: to 20\deg it is stifling, causing diseases of animals in the zones and places subject to it. The right side is moveable, fiery; the south part is \index{signs!climate!wet}wet; the lower parts are \index{signs!climate!destructive}destructive to everything; the middle and the left are \index{signs!climate!temperate}temperate.

\textbf{Fixed Stars:} \Leo\, has … stars. 

\textbf{Paranatellonta:} According to the Sphaerica, in the north the left arm of \index{constellations!Bootes}Bootes rises with \Leo; in the south the prow of \index{constellations!Argo}Argo, the rest of the \index{constellations!Dog | see{Sirrius}}Dog, and \index{constellations!Hydra}Hydra, whose tail stretches to the claws of \index{constellations!Scorpio}Scorpio <=Libra> and its head to the claws of \index{constellations!Cancer}Cancer as far as the \index{constellations!Crater}Crater. Above \Leo\, lies the \index{constellations!Little Bear}Little Bear, and on line with it lies the head of \index{constellations!Draco}Draco, \textbf{/10K/} which \index{constellations!Ophiouchus}Ophiouchus touches. On the north are the \index{constellations!Dolphin}Dolphin, \index{constellations!Lyra}Lyra, \index{constellations!Zeugma}Zeugma, \index{constellations!Cygnus}Cygnus (except for the bright star in its tail) and the head of \index{constellations!Pegasus}Pegasus.

\textbf{Zones: } The following zones are subject to \Leo: 
\begin{itemize}
\item to the head, \index{states!Gaul}Gaul and the adjoining areas; 
\item to the fore parts, \index{states!Bithynia}Bithynia; 
\item to the right side, \index{states!Macedonia}Macedonia and the neighboring areas; \item to the left side, \index{states!Propontus}Propontus; 
\item to the feet, \index{states!Galatia}Galatia; 
\item to the belly, \index{states!Gaul}Gaul; 
\item to the shoulders, \index{states!Thrace}Thrace; 
\item to the flanks, \index{states!Phoenicia}Phoenicia, the \index{states!Adriatic}Adriatic, and \index{states!Lybia}Lybia; 
\item to the midparts, \index{states!Phrygia}Phrygia and \index{states!Syria}Syria; 
\item to the tail, \index{states!Pessinus}Pessinus.
\end{itemize}

% ----------------------------------------------------------
\secbr
\subsection{\textit{[Virgo]}}
\marginnote{\tiny{Virgo} \Virgo}[0.2cm]

\textbf{/10P/} \index{signs!Virgo} \Virgo\, is the house of \Mercury, \index{signs!feminine} feminine, \index{signs!winged}winged, \index{signs!anthropomorphic}anthropomorphic, \index{signs!luxurious}luxurious, standing like the figure of Justice, \index{signs!bicorporeal} bicorporeal,\index{signs!barren} barren, a freedman, \index{signs!infertile}with no offspring, downward-trending, \index{signs!earthy} earthy, \index{signs!common} common, \index{signs!semi-vocal} semi-vocal or \index{signs!mute} mute, concerned with the body, \index{signs!incomplete}incomplete, \index{signs!changeable}changeable, \index{signs!industrious}industrious, \index{signs!bicorporeal} two-natured. 

\index{character!\Virgo}Men born under this sign are \index{character!noble}noble, \index{character!modest}modest, \index{character!religious}religious, burdened with care, leading a quite varied life, \index{jobs!administrator}administrators of others’ goods, \index{character!trusted}trusted, \index{jobs!steward}good stewards, \index{jobs!secretary}secretaries, \index{jobs!accountant}accountants, \index{jobs!actor}actors, \index{jobs!occultist}practitioners of curious arts and seekers after mystic lore, \index{character!spendthrift}spendthrifts in their early years but prosperous later in life\ldots 

\noindent
[\underline{<A later supplement from Ms Laurentianus 86.18>}\footnote{Riley has this additional text from an alternate source as a footnote.} 

\index{signs!climate!\Virgo}\textbf{Climate:} As a whole \Virgo is soaking \index{climate!wet}wet and \index{climate!stormy}stormy. By part it is as follows: its first decan is \index{climate!hot}hot and \index{climate!destructive}destructive, the second \index{climate!temperate}temperate, the third rainy. Its northern parts are \index{climate!windy}windy, the southern temperate. 

\textbf{Zones:} The following regions are subject to it: \index{states!Mesopotamia}Mesopotamia, \index{states!Babylonia}Babylonia, \index{states!Greece}Greece, \index{states!Achaea}Achaea, \index{states!Crete}Crete, the \index{states!Cyclades}Cyclades, the \index{states!Peloponnesus}Peloponnesus, \index{states!Arcadia}Arcadia, \index{states!Cyrene}Cyrene, \index{states!Doris}Doris, \index{states!Sicily}Sicily, \index{states!Persis}Persis. 

Of the parts of the body it rules the \index{belly}belly and \index{organs!internal}all the internal and hidden parts.]
% ----------------------------------------------------------
\secbr
\subsection{\textit{[Libra]}}
\marginnote{\tiny{Libra} \Libra}[0.2cm]

\index{signs!Libra} \Libra\, is the house of \Venus, \index{signs!masculine} masculine, \index{signs!equinotical} equinoctial, \index{signs!anthromorphic} anthropomorphic, upward-trending, \index{signs!airy} airy, \index{signs!femininzing}feminizing, \index{signs!vocal} vocal, \index{signs!noble}noble, \index{signs!changeable}changeable, a diminisher of estates, the Lower Midheaven of the universe\footnote{In the \textit{Thema Mundi}.}, \index{signs!public}public, \index{signs!ecliptic}ecliptic, \index{jobs!farmer}the supervisor of \index{crops}crops, \index{vineyards}vineyards, \index{olives}olive groves, \index{aromatics}aromatics, \index{homesteads}homesteads, \index{measures}measures, and \index{jobs!artisans}artisans.

\index{character!\Libra}Men born under this sign are \index{character!noble}noble and \index{character!just}just, but \index{character!malicious}malicious, \index{character!covetous}covetous of others’ goods, average in fortune, losing their original possessions and falling into vicissitudes, living through ups and downs of fortune, being in charge of measures, posts, and the \index{grain}grain supply\ldots

\noindent
[\underline{<A later supplement from Ms Laurentianus 86.18>}
\footnote{Riley has this additional text from an alternate source as a footnote.}  

\index{signs!climate!\Libra}\textbf{Climate:} As mentioned, as a whole \Libra\, is \index{climate!tropical}tropic and \index{climate!changeable}changeable. By part it is as follows: its first and second decans are \index{climate!temperate}temperate, the third \index{climate!rainy}rainy. Its northern parts are \index{climate!windy}windy, the southern moist/dry text? and disease–ridden. 

\textbf{Zones:} The following regions are subject to it:
\index{states!Bactria}Bactria, \index{states!China}China, the \index{states!Caspian area}Caspian area, \index{states!Thebais}Thebais, the \index{states!Oasis}Oasis, \index{states!Troglodytia}Troglodytia, \index{states!Italy}Italy, \index{states!Libya}Libya, \index{states!Arabia}Arabia, \index{states!Egypt}Egypt, \index{states!Ethiopia}Ethiopia, \index{states!Carthage}Carthage, \index{states!Smyrna}Smyrna, the \index{states!Taurus mountains}Taurus mountains, \index{states!Cilicia}Cilicia, \index{states!Sinope}Sinope \textit{text?} . 

Of the parts of the body, it rules the \index{hips}hips and \index{buttocks}buttocks, the \index{groin}groin and \index{intestines}intestines, the \index{hind parts}hind parts and \index{rump}rump.]

% ----------------------------------------------------------
\secbr
\subsection{\textit{[Scorpio]}}
\marginnote{\tiny{Scorpio} \Scorpio}[0.2cm]

\index{signs!Scorpio} \Scorpio\, is the house of \Mars, \index{signs!feminine} feminine, \index{signs!solid} solid, \index{signs!watery} rainy, \index{signs!fertile}fecund, \index{signs!destructive}destructive, downward-trending, \index{signs!mute} mute, \index{signs!servile} servile, \index{signs!unchangeable}unchangeable, the cause of stenches, a destroyer of property, \index{signs!ecliptic} ecliptic, having many feet. 

\index{character!\Scorpio}Men born under this sign are \index{character!tricky}tricky, \index{character!base}base, \index{character!thieving}thieves, \index{character!murderous}murderers,  \index{character!traitorous}traitors,  \index{character!incorrigible}incorrigible,  \index{character!destructive}destroyers of property,  \index{character!conniving}connivers, \index{jobs!burglar}burglars, \textbf{/11K/}  \index{character!perjurious}perjurers,  \index{character!covetous}covetous of others’ property,  \index{character!criminal}accomplices in murder, poisonings, and other crimes, haters of their own family\ldots

\noindent
[\underline{<A later supplement from Ms Laurentianus 86.18>}
\footnote{Riley has this additional text from an alternate source as a footnote.}  

\index{signs!climate!\Scorpio}\textbf{Climate:} As a whole, \Scorpio\, is \index{climate!stormy}stormy and \index{climate!fiery}fiery. By part it is as follows: its first decan is \index{climate!cloudy}cloudy, the second \index{climate!temperate}temperate, the third indicative of \index{climate!earthquakes}earthquakes. Its northern parts are burning\index{climate!hot} hot, the southern dry/moist \textit{text?}. 

\textbf{Zones:} The following regions are subject to it:
\index{states!Metagonitis}Metagonitis, \index{states!Mauretania}Mauretania, \index{states!Gaetulia}Gaetulia, \index{states!Syria}Syria, \index{states!Commagene}Commagene, \index{states!Cappadocia}Cappadocia, \index{states!Italy}Italy, \index{states!Carthage}Carthage, \index{states!Libya}Libya, \index{states!Ammon}Ammon, \index{states!Sicily}Sicily, \index{states!Spain}Spain, \index{states!Rome}Rome. 

Of the parts of the body, it rules the \index{organs!sexual}unmentionable parts and the \index{rump}rump, the \index{groin}groin and seat. 

Because of its sting, it causes \index{illnesses!blindness}blindness, dimming of vision, \index{illnesses!stones}attacks of the stone, \index{illnesses!stranguary}strangury, \index{illnesses!ruptures}ruptures and strangulated \index{illnesses!hernias}hernias, unmentionable vices and promiscuity, \index{illnesses!fistulas}fistulas, \index{illnesses!cancers}cancers, and \index{illnesses!hemorrages}hemorrages.]

% ---------------------------------------------------------
\secbr
\subsection{\textit{[Sagittarius]}}
\marginnote{\tiny{Sagittarius} \Sagittarius}[0.2cm]

\index{signs!Sagittarius} \Sagittarius\, is the house of \Jupiter, \index{signs!masculine} masculine, \index{signs!fiery} fiery, upward-trending, \index{signs!vocal} vocal, \index{climate!moist}moist because of the constellation \index{constellations!Argo}Argo, \index{character!noble}noble, \index{signs!winged}winged, \index{signs!changeable}changeable, \index{signs!bicorporeal} bicorporeal, two-natured, \index{signs!mysterious}mysterious, \index{signs!fertile}with few offspring, \index{signs!half-finished}half-finished <=childless?>, \index{signs!governing}governing, \index{signs!roya}kingly. 

\index{character!\Sagittarius}Men born under this sign are \index{character!noble}noble, \index{character!just}just, \index{character!great-hearted}great-hearted, \index{jobs!judge}judges, \index{character!generous}generous, \index{character!loving}loving their brothers and their friends. They lose much of their original possessions but gain them back. They are superior to their enemies, seek a noble reputation, are \index{character!benefactor}benefactors, \index{character!prominent}prominent, and act mysteriously\ldots

\noindent
[\underline{<A later supplement from Ms Laurentianus 86.18>}
\footnote{Riley has this additional text from an alternate source as a footnote.}  

\index{signs!climate!\Sagittarius}\textbf{Climate:} As a whole, it is \index{climate!windy}windy. By part, it is as follows: its first decan is quite \index{climate!wet}wet, the second \index{climate!temperate}temperate, the third \index{climate!fiery}fiery. Its northern parts are windy, the southern \index{climate!moist}moist and \index{climate!variable}variable. 

\textbf{Zones:} The following regions are subject to it: \index{states!Etruria}Etruria, \index{states!Gaul}Gaul, \index{states!Spain}Spain, \index{states!Arabia Felix}Arabia Felix, \index{states!Cilicia}Cilicia, \index{states!Crete}Crete, \index{states!Sicily}Sicily, \index{states!Gaul}Gaul, \index{states!Italy}Italy, \index{states!Spain}Spain, \index{states!Cyprus}Cyprus, the \index{seas!Red Sea}Red Sea, C\index{states!Casperia}Casperia and the nations along the \index{states!Euphrates Area}Euphrates, \index{states!Mesopotmia}Mesopotamia, \index{states!Carthage}Carthage, the \index{seas!Libyyan Sea}Libyan Sea, the \index{seas!Adriatic}Adriatic, the \index{seas!Atlantic}Atlantic, the \index{states!Triballi}Triballi, \index{states!Bactria}Bactria, \index{states!Egypt}Egypt and the nearby places. 

It is \index{signs!masculine}masculine and \index{signs!autumn}. 

Of the parts of the body, it rules the \index{thighs}thighs and \index{groin}groin.

Because of its point, it often causes births with \index{limbs!extra}extra limbs, \index{baldness}baldness, \index{illnesses!epilepsy}epilepsy, troubles of the eyes, or \index{illnesses!blindness}blindness. It always causes danger from \index{animals}animals, the \index{limbs!loss of}loss of limbs, or dangers from \index{beasts!wild}wild beasts.]

% ----------------------------------------------------------
\secbr
\subsection{\textit{[Capricorn]}}
\marginnote{\tiny{Capricorn} \Capricorn}[0.2cm]

\index{signs!Capricorn} \Capricorn\, is the house of \Saturn, \index{signs!feminine} feminine, \index{signs!tropical} tropic, \index{signs!earthy} earthy, \index{signs!destructive}destructive, \index{signs!sterile} barren, downward-trending, \index{climate!chilling}, \index{signs!mute} mute, \index{signs!servile} servile, the cause of troubles, \index{signs!brutal}brutal, \index{signs!lurking}lurking, \index{signs!mysterious}mysterious, \index{signs!bi-corporeal}two-natured, \index{signs!moist}moist, \index{signs!half-finished}half–finished <=childless?>, a \index{hunchback}hunchback, \index{lame}lame, the Descendant of the universe\footnote{In the \textit{Thema Mundi}.}, indicative of \index{signs!misfortune} and \index{signs!toil}, a \index{jobs!sculptor}sculptor, a \index{jobs!farmer}farmer. \textbf{/11P/ }

\index{character!\Capricorn}Men born under this sign are \index{character!bad}bad, \index{character!warped}warped. They \index{character!insincere}pretend goodness and sincerity. They are \index{character!toilsome}toilsome, \index{character!burdened}burdened with care, \index{insomniac}insomniac, \index{character!joker}fond of jokes, \index{character!plotting}plotters of great deeds, prone to make unfortunate mistakes, \index{character!fickle}fickle, \index{character!criminal}criminal, \index{character!lying}lying, always \index{character!critical}criticizing, \index{character!shameful}shameful.

\index{signs!climate!\Capricorn}\textbf{Climate:} \Capricorn\, is \index{climate!temperate}temperate on both sides. By parts it is as follows: the first parts are \index{climate!destructive}destructive, the second \index{climate!moist}moist, \index{climate!stormy}stormy, \index{climate!changeable}changeable; the middle parts are \index{climate!fiery}fiery; the last destructive. 

\textbf{Fixed Stars:} It has … stars.

\textbf{Paranatellonta:}According to the Sphaerica, \index{constellations!Casseiopeia}Casseiopeia and the right part of \index{constellations!Pegasus}Pegasus rise with it in the north. In the south the rear of \index{constellations!Centaurus}Centaurus and the legs of \index{constellations!Hyrda}Hydra (up to the Crater) set <while \Capricorn\, is rising>. These are the gods: \Venus, the \Moon, Ceres, \Mercury. On the north there is nothing.

\textbf{Zones:} The following zones are subject to \Capricorn, all of them to the West and South: 
\begin{itemize}
\item To the flanks, the \index{seas!Aegean Sea}Aegean Sea, the inhabitants of its coastline, and \index{states!Corinth}Corinth; 
\item to its waist, \index{states!Sicyon}Sicyon; 
\item to its back, the \index{seas!Mediterranean}Mediterranean; 
\item to its tail, \index{states!Spain}Spain; 
\item to its head, the \index{states!Tyrrhenian Sea}Tyrrhenian Sea; 
\item to its belly, \index{states!Egypt}mid-Egypt, \index{states!Syria}Syria, \index{states!Caria}<and Caria>.
\end{itemize}

% -----------------------------------------------------------
\secbr
\subsection{\textit{[Aquarius]}}
\marginnote{\tiny{Aquarius} \Aquarius}[0.2cm]

\index{signs!Aquarius} \Aquarius\, is the celestial sign which is \index{signs!masculine} masculine, \index{signs!solid} solid, \index{signs!anthromorphic} anthropomorphic, \index{climate!damp}somewhat damp, \index{signs!single}single. It is \index{signs!mute} mute, \index{climate!cold}quite cold, \textbf{/12K/} free, upward-trending, \index{signs!feminizing}feminizing, \index{signs!unchanging}unchanging, \index{signs!base}base, \index{signs!fertile}with few offspring, \index{signs!athletic}the cause of troubles arising from athletic training, carrying burdens, or \index{jobs!artisan}work in hard materials, an artisan, \index{signs!public}public. 

\index{character!\Aquarius}Men born under this sign are \index{character!malicious}malicious, haters of their own families, \index{character!incorrigible}incorrigible, \index{character!self-willed}self-willed, \index{character!deceitful}deceitful, \index{character!tricky}tricky, \index{character!secretive}concealing everything, \index{character!misanthropic}misanthropic, \index{character!godless}godless, \index{character!accusative}accusers, \index{character!betraying}betrayers of reputations and the truth, \index{character!envious}envious, \index{character!petty}petty, occasionally \index{character!generous}generous (because of <this sign’s> flow of water), \index{character!uncontrollable}uncontrollable.

\index{signs!climate!\Aquarius}\textbf{Climate:} As a whole this sign is \index{climate!wet}wet. By part it is as follows: the first parts are wet, the upper parts \index{climate!fiery}fiery, the lower \index{climate!wortheless}worthless and useless. 

\textbf{Fixed Stars:} It has …stars. 

\textbf{Paranatellonta:} According to the Sphaerica the right parts of \index{constellations!Andromeda}Andromeda rise in the north with \Aquarius, as well as the rest of \index{constellations!Pegasus}Pegasus; in the south, the southern one of the <two> Fish, except for the head. \index{gods!Juno}Juno, \index{gods!Hercules}Hercules, \index{gods!Vulcan}Vulcan, \Saturn. \textbf{/12P/} In the north nothing sets. In the south
the rest of \index{constellations!Centaurus}Centaurus and of \index{constellations!Hydra}Hydra (up to \index{constellations!Corvus}Corvus) set <when \Aquarius\, rises>. 

This sign lies toward the west wind. In addition it faces toward the zone of Egypt and the surrounding cities, i.e. from Egypt’s southern parts up to Pselchos, Dodecaschoinos, and Sykaminos; from its western parts to the oasis of Ammon and the surrounding cities; from its eastern part to the Red Sea which touches Egypt; and from its northern parts to Sebennytos and the Heracleotic mouth of the Nile.

According to the Sphaerica, \index{constellations!Eridanus}Eridanus and the \index{constellations!Great Fish}Great Fish lie next to \Aquarius\, in the south, touching the tail of \Capricorn. In the north, around the north pole, is the so–called \index{constellations!Cygnus}Cygnus, above which is \index{constellations!Sagitta}Sagitta,where the \index{constellations!Bear}Bear (called \index{constellations!Cynosura}Cynosura) looks to the north. 

\textbf{Zones:} The following zones are subject to \Aquarius:
\begin{itemize}
\item to the front parts, \index{states!Syria}Syria; 
\item to the middle, the \index{states!Euphrates}Euphrates and \index{states!Tigris}Tigris, \index{states!Egypt}Egypt, \index{states!Libya}Libya, the interconnected Egyptian rivers, and the Indus. 
\item Under the middle of the \index{states!Water Jug}Water Jug are the \index{states!Tanais}Tanais and the rest of the rivers which flow from the Hyperboreans to the north and west. \textbf{/13K/}
\end{itemize}

% -----------------------------------------------------------
\secbr
\subsection{\textit{[Pisces]}}
\marginnote{\tiny{Pisces} \Pisces}[0.2cm]

\index{signs!Pisces} \Pisces\, is the celestial sign which is \index{signs!feminine} feminine, \index{climate!wet} moist, quite wet, \index{signs!bicorporeal} bicorporeal, \index{signs!fertile}with many offspring, \index{signs!mossy}mossy, \index{signs!scaley}scaley, \index{signs!sinewy}sinewy, \index{signs!humpbacked}humpbacked, \index{signs!leprous}leprous, \index{signs!bicorporeal} two-formed, \index{signs!mute} mute, \index{signs!motile}motile, \index{skin!rough}with rough skin, in \index{character!conflicted}conflict with itself because one Fish is northern, the other southern. It is moist, downward-trending, \index{signs!servile} servile, \index{signs!changeable}changeable, \index{signs!fertile}with many offspring, bicorporeal, \index{character!sociable}sociable/\index{character!lewd}lewd, with some limbs missing, the cause of \index{character!wanderer}wandering, \index{character!varied}varied.

\index{character!\Pisces}Men born under this sign are \index{character!unsteady}unsteady, \index{character!unreliable}unreliable, changing from bad fortune to good, \index{character!sexy}sexy, \index{character!theiving}thievish, \index{character!shameless}shameless, \index{character!prolific}prolific,\index{character!popular} popular.

\index{signs!climate!\Pisces}\textbf{Climate:} As a whole, \Pisces\, is \index{climate!cool}cool and \index{climate!breezy}breezy. By parts it is as follows: the first parts are \index{climate!temperate}temperate, the
middle \index{climate!moist}moist, the last \index{climate!destructive}destructive and worthless. 

\textbf{Fixed Stars:} It has…stars. 

\textbf{Paranatellonta:} In the north the rest of \index{constellations!Andromeda}Andromeda rises with \Pisces, as well as the rest of \index{constellations!Perseus}Perseus—the parts on the right—and \index{constellations!Triangulum}Triangulum in \Aries. In the south the head of the Southern Fish rises. \index{gods!Neptune}Neptune\footnote{The god, not the planet.}, \textbf{/13P/} \Mars, \Mercury, \Venus, \Jupiter. In the south \index{constellations!Ara}Ara and the rest of \index{constellations!Hydra}Hydra set <when \Pisces\, is rising>; in the north, nothing. \Pisces\, lies toward the north wind. It also lies toward the zone of the Red Sea, having not a few islands under its control, above which lie India and the so-called Indian Ocean. In its eastern parts \Pisces\, touches Parthia, the land of the Indies, and the Eastern Ocean; in its northern parts, Scythia. In its western parts it washes with its waves Myosormos, Orthosormos, and the surrounding cities.

According to the Sphaerica, Aquila, cut off by the north pole, and part of Sagitta lie to the north of Pisces, not far away from the north pole. The so-called Pegasus is within the \index{Artic!pole}Arctic pole. (The \index{Artic!circle}Arctic Circle, lying in the middle of the universe, stands apart from the other divisions <of the sky>. It has in it the \index{constellations!Great Bear}Great Bear (called \index{constellations!Cynosura}Cynosura) stretching from the north toward the east, and from the south the other \index{constellations!Lesser Bear}Bear, called the Lesser, \textbf{/14K/} which rises at midnight, and which the so–called \index{constellations!Bearguard | see{Bootes}} <Bootes> controls, having a rein on both Bears. He is invisible depending on the elevation of the two Bears. One looks north, the other south.) 

\textbf{Zones:} The following zones are subject to \Pisces: 
\begin{itemize}
\item to the front, the \index{rivers!Euphrates}Euphrates and the \index{rivers!Tigris}Tigris; 
\item to the middle, \index{states!Syria}Syria and the \index{seas!Red Sea}Red Sea, \index{states!India}India, \index{states!Persis}mid-Persis and the neighboring lands; 
\item to the tail, the \index{seas!Arabian Sea}Arabian Sea, the Red Sea, and the \index{rivers!Borysthenes}Borysthenes river; 
\item to the tie of the Northern Fish, \index{states!Thrace}Thrace; 
\item to that of the Southern Fish, \index{states!Asia}Asia, \index{states!Sardinia}Sardinia.
\end{itemize}

\newpage