\section{Transits and The Combination of the Stars (21K,19P)}

\subsection{\textit{[Transits]}}
\index{transit!places}
[\textbf{/21K/}
The \Sun: the second, the sixth, and the twelfth are good; the seventh and the fourth are rotten.

The \Moon: the third, the eighth, and the ninth are rotten; the fifth, the eleventh, and the twelfth are good.

\Saturn: the fourth and the tenth are rotten; the sixth, the eighth, and the twelfth are good.

\Jupiter: the third, the ninth, the tenth, and the eleventh are good; the fourth and the seventh are rotten.

\Mars: the third, the fourth, and the ninth are good; the \textbf{/37K/} seventh and the tenth are rotten.

\Venus: the third, the seventh, and the eighth are good; the fifth is rotten.

\Mercury: the second, the fifth, and the eleventh are rotten; the seventh, the eighth, and the ninth are good.

\mndl[0.2cm]\index{planets!transits}
\index{delineation!transits}
The other <numbers> of each star are variable in effect.
If the stars are in the previously mentioned places in their transits, particularly when they hold the chronocratorship in operative places, with benefics or malefics in aspect, then they are bestowers of good or evil depending on whichever aspect prevails. 

\mnm[0.3cm]
If the <benefics and malefics> are together, a mixture of good and bad will ensue according to the quality of each person’s nativity. Therefore it is always necessary to
observe the places with respect to <the stars’> transits in order to evaluate the chronocratorships.]

Let us append the associations and combinations of each star.\enlargethispage{2\baselineskip}\footnote{\Mars\, is listed in combination under each planet but not on his own. His combinations with the \Sun\, and \Moon\, are missing from the text.}

\secbr
\index{planets!Saturn!with the other planets}
\subsection{\textit{[Saturn]}}

\index{planets!\Saturn-\Jupiter}When \Saturn\, and \Jupiter\, are together, they are in agreement with each other, and they bring about benefits from \index{planets!productive of!legacies}legacies and \index{planets!productive of!adoptions}adoptions, and \index{land owner}they cause men to be masters of property consisting of land, to be \index{jobs!guardian}guardians, \index{jobs!property managers}managers of others’ property, \index{jobs!stewards}stewards, and \index{jobs!tax collector}tax gatherers.

\index{planets!\Saturn-\Mars}\Saturn\, and \Mars\, are hostile, \index{planets!productive of!reversals}productive of reversals and \index{planets!productive of!ruin}ruin. They bring \index{planets!productive of!quarrels}family quarrels, disharmony, and \index{planets!productive of!hatred}hatred, along with \index{planets!productive of!treachery}treachery, \index{planets!productive of!plots}plots, \index{planets!productive of!malevolence}malevolence, and \index{planets!productive of!trials}trials. However, if these stars are not in their own or in operative signs, and if they have benefics in aspect, they produce \index{character!distinguished}distinguished and \index{character!noble}noble nativities, although unsteady in their happiness and prone to \index{planets!productive of!unexpected dangers}unexpected dangers and treachery.

\index{planets!\Saturn-\Mercury}\textbf{/37P/}\Saturn\, and \Mercury\, are allies and productive of \index{planets!productive of!employmnent}activities/employment. They do, however, bring \index{planets!productive of!slander}slanders about religion, \index{planets!productive of!lawsuits}lawsuits, and \index{planets!productive of!debts}debts, as well as \index{planets!productive of!money problems}disturbances about written matters and money. On the other hand, these stars make men who are not without resources and not unintelligent, with much experience and awareness, and who are \index{character!curious}curious, far-seeing \index{jobs!scholars}scholars, \index{jobs!occultists}seekers after mystic lore, \index{character!reverent}revering the gods, but with much on their \index{thoughtful}consciences.

\index{planets!\Saturn-\Venus}\Saturn\, and \Venus\, act harmoniously with respect to activities/employment: \textbf{/38K/} they promote success with respect to entanglements and \index{planets!productive of!unstable marriage}marriage, agreeing and beneficial only for a time, not to the end. Indeed they cause \index{planets!productive of!marriage abuse}abuse, \index{planets!productive of!divorce}divorces, \index{planets!productive of!inconstancy}inconstancy, and \index{planets!productive of!death}death, often entangling men with the base-born and the lowly, and causing them to fall into \index{planets!productive of!harm}harm and \index{planets!productive of!lawsuits}lawsuits.

\index{planets!\Saturn-\Moon}\Saturn\, and the \Moon\, are beneficial, productive of \index{planets!productive of!money}money, \index{planets!productive of!estates}estates, \index{planets!productive of!ship ownership}ship ownership, and \index{planets!productive of!inheritance}profits from the deceased, especially if the \Moon\, happens to be in the part of its orbit just following first visibility and has benefics in aspect. Then it causes \index{planets!productive of!associations with the great}association with the great, \index{planets!productive of!gifts}gifts, and the discomfiture of enemies. This combination, however, is unsteady with respect to possession, and with respect to women it is insecure and painful because of \index{planets!productive of!separations}separations, \index{planets!productive of!hatred}hatred, and \index{planets!productive of!grief}grief. It also produces \index{planets!productive of!bodily suffering}bodily suffering, sudden \index{planets!productive of!fits}fits, pains of the governing faculties and nerves, as well as the \index{planets!productive of!important deaths}deaths of important figures.

\index{planets!\Saturn-\Sun}\Saturn\, and the \Sun\, are at odds, \index{planets!productive of!lost possessions}giving and taking away possessions and \index{planets!productive of!malicious friendships}friendships maliciously. Therefore those born under such a juncture suffer \index{planets!productive of!secret enemities}secret enmities and \index{planets!productive of!powerful enemies}threats from great persons and are plotted against by some and live hated to the end. Playing their part well, they outlive most <of their enemies>. They are, however, not without resources, but are disturbed and \index{long-suffering}long-suffering. They are \index{self controlled}self controlled in this onslaught of \index{reversals}reversals.

\secbr
\index{planets!Jupiter!with the other planets}
\subsection{\textit{[Jupiter]}}
\index{planets!\Jupiter-\Sun}When \Jupiter\, and the \Sun\, are together, they produce \index{character!noble} and \index{character!distinguished}distinguished men, \index{jobs!ruler}rulers, \index{jobs!governor}governors, \index{job!dictator}dictators, \index{character!vigorous}vigorous men, \index{character!honored}honored and \index{character!popular}blessed by the crowd. These men are \index{wealth}wealthy, rich, living with much spectacle. Sometimes however they are involved in uncertainties and \textbf{/38P/} \index{hostility}hostility. Especially if the star <\Jupiter> is found to be setting, they resort to \index{character!showy}greater showiness and make a \index{character!pretense of truth}pretense of the truth.

\index{planets!\Jupiter-\Moon}\Jupiter\, and the \Moon\, are good, \index{character!acquisitive}acquisitive: they cause men to be masters of \index{planets!productive of!adornments}adornments and \index{planets!productive of!slaves}slaves, and they bestow distinguished \index{planets!productive of!rank}offices and ranks. They cause men to benefit from women and \index{character!distinguished}distinguished individuals, to be treated well by family and children, and to be thought worthy of \index{planets!productive of!gifts}gifts and \index{planets!productive of!honors}honors. They make \index{jobs!treasurer}treasurers, men who \index{jobs!lender}lend much, who are \index{character!trusted}trusted, and who find \index{planets!productive of!treasure}treasures and become \index{planets!productive of!wealth}wealthy.

\index{planets!\Jupiter-\Mars}\textbf{/39K/}\Jupiter\, and \Mars\, make \index{character!glorious}glorious and \index{character!showy}showy characters, friends of the \index{planets!productive of!great acquaintances}great or of kings, \index{character!distinguished}distinguished \index{jobs!governor}governors and receivers of stipends, those making a career in \index{jobs!public}public affairs or in \index{planets!productive of!campaigns}campaigns, and those considered worthy of \index{planets!productive of!honor}honor and \index{planets!productive of!status}status, but \index{planets!productive of!changeable livelihood}uncertain in their livelihoods and habits, \index{planets!productive of!loss of possessions}tossing away their possessions.

\index{planets!\Jupiter-\Venus}\Jupiter\, and \Venus\, are good, in harmony, productive of \index{planets!productive of!rank}rank and \index{planets!productive of!profits}profits, bringing \index{planets!productive of!acquisitions}new acquisitions, \index{planets!productive of!gifts}gifts, \index{planets!productive of!adornments}adornments, \index{jobs!slave master}control over slaves, \index{jobs!ruler}rulerships, \index{planets!productive of!children}the begetting of children, \index{jobs!priest}high priesthoods, \index{planets!productive of!eminence}preeminence among the masses, \index{planets!productive of!honors}honors of garlands and gold crowns. These stars make men who are worthy of statues and images, but they also make them subject to \index{marriage!unsteady}ups and downs with respect to marriages and children.

\index{planets!\Jupiter-\Mercury}\Jupiter\, and \Mercury\, are good, in harmony, and supervisory. They make men who are \index{jobs!manager}managers, \index{jobs!overseer}overseers of affairs, \index{jobs!administrator}in posts of trust and administration. They make men who are successful as \index{jobs!secretary}secretaries and \index{jobs!accountant}accountants and who are respected in \index{jobs!educator}education. These are approachable people with many \index{planets!productive of!friends}, judged worthy of pay and stipends. If \Jupiter\, and \Mercury\, are found in operative signs, they make men \index{planets!productive of!treasure}discoverers of treasures, or \index{jobs!moneylenders}moneylenders who profit from cash deposits.

\secbr
\index{planets!Venus!with the other planets}
\subsection{\textit{[Venus]}}
\index{planets!\Venus-\Sun}\Venus\, and the \Sun\, are in harmony, glorious, bestowers of good. They cause the association of male and female, they bring \index{planets!productive of!gifts} and \index{planets!productive of!conveyances}conveyances, and make men \index{planets!productive of!successful enterprises}successful in their enterprises. Occasionally they make those men who take on \index{planets!productive of!popularity}popular leadership or \index{planets!productive of!trust}trusts, those who are in charge of foreign/secure places, those thought worthy of stipends. These men, however, are not without grief with \index{planets!productive of!marital grief}respect to wife and children, especially if \Venus\, is setting.

\index{planets!\Venus-\Moon}\textbf{/39P/}\Venus\, and the \Moon\, are good with respect to \index{planets!productive of!rank}rank, \index{planets!productive of!acquisitions}acquisitions, and the \index{planets!productive of!business}inception of business, but they are \index{planets!productive of!unstable marriage}\index{planets!productive of!associations}unsteady with respect to living together, friendships, and marriage, bringing \index{planets!productive of!rivalry}rivalry and \index{planets!productive of!hostility}hostility, as well as \index{planets!productive of!ill-treatment by family, friends}ill-treatment and upset from relatives and friends. Likewise with respect to children and slaves, these stars are not good: they cause possessions to be fleeting and bring \index{planets!productive of!mental anguish}mental anguish.

\index{planets!\Venus-\Mars}\Venus\, and \Mars\, are at odds. They make men \index{planets!productive of!unsteady, weak, mind}unsteady and weak of mind; they cause \index{planets!productive of!rivalry}rivalry and \index{planets!productive of!murder}murder; they cause men to have \index{planets!productive of!many friends}many friends, but to be \index{character!blameworthy}blameworthy, \index{character!shameless}shameless, \index{character!fickle}fickle, and \index{gender!bi-sexual}equally prone to intercourse with men or women; to be \index{character!malicious}malicious, and plotters of \index{murder!poison}murder by poison. These stars cause men to remain with neither the good nor the bad, to be \index{planets!productive of!slander}slandered and reviled because of their friendships, to be \index{character!spendthrift}spendthrift, \textbf{/40K/} flitting from one occupation to another, to be eager for many things, to be wronged by women and because of them to suffer \index{planets!productive of!crises}crises, \index{planets!productive of!upsets}upsets, and \index{planets!productive of!debts}debts.

\index{planets!\Venus-\Mercury}\Venus\, and \Mercury\, are in harmony. They make men \index{character!sociable}sociable and \index{character!gracious}gracious, \index{character!gregarious}gregarious and \index{character!hedonistic}hedonistic, paying attention to education and sensibility, receiving \index{planets!productive of!honors}honors and \index{planets!productive of!gifts}gifts. For those of mediocre fortune, these stars bring about the receiving of goods, \index{planets!productive of!selling and receiving goods}selling, and exchanges, and they bring \index{planets!productive of!basic livelihood}a base livelihood. These stars make men \index{character!unsteady}unsteady and \index{character!fickle} with respect to women, changeable in their agreements <with them>.

\secbr
\index{planets!Mercury!with the other planets}
\subsection{\textit{[Mercury]}}
\index{planets!\Mercury-\Sun}\Mercury\, and the \Sun\, make \index{character!adaptable}adaptable men with \index{planets!productive of!many friends}many friends, those \index{character!flexible}flexible and \index{character!self-controlled}self-controlled men who spend their \index{jobs!public}careers in public places. These stars make \index{character!pure}pure, \index{character!sensible}sensible men, \index{character!judgment!good}men of good judgment, lovers of beauty, \index{character!learned}learned men, initiates into divine matters, \index{character!beneficent}beneficent, fond of their associates, \index{character!independent}independent, \index{character!braggarts}braggarts. These men endure reversals nobly, but are \index{character!ineffective}ineffective, suffering ups and downs in their livelihoods, experiencing vicissitudes. They are not poverty-stricken, but find a \index{planets!productive of!success}success proportional to the basis of their nativities.

\index{planets!\Mercury-\Moon}\textbf{/40P/}\Mercury\, and the \Moon\, are good with respect to the \index{planets!productive of!marriage}union and \index{planets!productive of!status}status of men and women, with respect to the power of \index{planets!productive of!speech}speech and \index{planets!productive of!education}education, and concerning \index{planets!productive of!commerce}commerce and other enterprises. They make men who act in common, who are \index{character!resourceful}resourceful, \index{character!experienced}experienced, \index{character!inquisitive}inquisitive. They also cause men to advance by \index{expenses!great}great expenditures, to be very \index{character!changeable}changeable, \index{planets!productive of!unsteady activities}not persevering in their activities or intentions for the future. <These men are> noble in the face of adversity, but are subject to ups and downs in their \index{livelihood!changeable}livelihood.

\index{planets!\Mercury-\Mars}\Mercury\, and \Mars\, are not good. They cause \index{planets!productive of!hostility}hostility, \index{planets!productive of!lawsuits}lawsuits, \index{planets!productive of!reversals}reversals, \index{planets!productive of!malice}malice, \index{planets!productive of!betrayal}betrayals, \index{planets!productive of!wrongs}wrongs from superiors or inferiors. These stars make some men \index{character!athletic}athletic, \index{character!martial}martial, \index{character!commanding}commanding, \index{character!beneficent}beneficent, \index{jobs!occultists}inquisitive <of the occult>, getting a \index{livelihood!varied}livelihood in a varied manner. They resort to \index{jobs!forger}forgery in order to \index{jobs!embezzler}embezzle, \index{jobs!thief}steal, and loot, and having fallen into \index{debt}debt and expenses, they bring on themselves \index{infamy}infamy and hot pursuit. If the configuration is afflicted, men meet with \index{planets!productive of!accusations}accusations and \index{planets!productive of!imprisonment}imprisonment, and they suffer \index{planets!productive of!loss}loss or confiscation of goods.

\secbr
\index{planets!Sun!with the Moon}
\subsection{\textit{[Sun and Moon]}}
\index{planets!\Sun-\Moon}The \Sun\, and the \Moon\, are good. They are \index{planets!productive of!associations}productive of associations with the \index{planets!productive of!rank}great and of high rank, as well as possession of \index{planets!productive of!estates}estates, \index{planets!productive of!property}property, \index{planets!productive of!money}money, and \index{planets!productive of!adornment}adornment. These stars cause men to be \index{planets!productive of!business success}successful in business enterprises \textbf{/41K/} and to receive profit. If the basis <of the nativity> is found to be great, men become \index{jobs!mayors}leaders of cities, in charge of affairs, preeminent among the masses, gifted with a very high public image, \index{character!munificent}munificent, \index{jobs!governor}governing, \index{jobs!ruler}ruling, unsurpassed, and possessing a kingly property and spirit. Those starting with a moderate/average fortune become \index{lucky} and are called blessed. The good, however, does not last for this type of person, because of the waning configuration of the \Moon. 

\ldots


\newpage