\section{The Combination of Three Stars (22K,20P)}
\index{planets!Saturn!in combination with other planets}
\subsection{\textit{[Saturn in Combination]}}
\Saturn, \Jupiter, and the \Sun\xspace are unsteady and insecure. <They bring failure> with respect to possessions, friendships, and other business enterprises. They cause loss of possessions, and they cause some to fall into invidious accusations. \textbf{/41P/} These stars, having indicated help from unexpected sources or from legacies, and having increased someone’s reputation, bring ruin and accusation, along with sudden danger and plots. They do cause preeminence, guardianship of others’ business, tax gathering, and salaries, for the sake of which men endure disturbance and crises, but these stars make the basis <of the nativity> insecure and worrisome.

\Saturn, \Jupiter, and the \Moon\xspace are in harmony, bringing rank and profit, associations with the great, and gifts. Men travel abroad; they succeed in foreign lands or because of foreigners, not only in their own business, but also in others’. Men also derive benefits from women, and coming into possession \textbf{/42K/} of estates and land, they become lords. Some become shipowners and thus increase their livelihood, or they manage their livelihood by getting hold of whatever is involved with water.

\Saturn, \Jupiter, and \Mars\xspace bring about mixtures of good things. They make some men famous, high priestly,
governing, influential, in charge of the masses, of villages, or of military matters, commanding and obeyed. These men are not adorned with great show of wealth; they are involve in reversals, accusations, and violent affrays; and they lead worried lives. <These stars cause> others to be graced with the possession of an income, to be masters of estates and property, and to profit from the deceased, but their reputation is low. \mndl Therefore matters must be interpreted according to the configuration of the heavenly bodies and the effects of the signs.

\Saturn, \Jupiter, and \Venus\xspace are good, helpful in occupations, bringing possessions. They cause associations of male and female, as well as friendships, advancement, and benefits from legacies. However in their associations men are slandered and envied; they are unsteady in their marriages, suffering embarrassments, hostility, and judgements. On the other hand, they are fond of their associates and easy to
live with, enjoying many new friendships. They are not entirely tranquil, nor do they lack grief with respect to children and slaves.

\Saturn, \Jupiter, and \Mercury\xspace when configured together produce vigorous men, \textbf{/42P/} stewards,
trustworthy, preeminent among the masses, commanding and obeyed, handlers of money and directors of documents and accounts. Such men have an independent and adaptable nature: sometimes they appear malevolent and wicked, and they will become covetous of others’ property, thievish, and greedy, because of which they will endure upsets and crises, debts and public infamy. Sometimes these men advance because of their success in action and because of their trustworthiness. Then they gain support and are thought worthy of gifts from the great and of honors. Since they have a generous disposition, they will benefit their own family and even others’. They, however, will take part in the mysteries and in esoteric affairs, and in other respects they will inquire into the curious arts and be subtle,  pretending that their character is straightforward.

\textbf{/43K/}\Saturn, \Mars, and the \Sun\xspace are indicative of forcible, outré, and dangerous matters. These stars make bold men, men of great ambition, wicked atheists, traitors, insubordinate, men who hate their own families, who abandon their own relatives to go with strangers. They are involved in contumely and dangers. They suffer falls from high places or from animals. They are afraid of burns, and are toilsome in their activities. They do not guard what they already have, but desire others’ goods. They profit from
crime. If, however, the configuration happens to be military or athletic, they are toilsome, but not unsuccessful.

\Saturn, \Mars, and the \Moon\xspace cause men to be venturesome in their business enterprises and noble, but
ineffective, meeting with reversals and violence. They become in turn violent, reclusive, wicked: they have a plundering and thievish disposition,and become defendants in trials. They experience detention and criminal charges, unless of course the nativity happens to be fond of wrestling or of weapons, in which case the “detention” configuration is fulfilled by the holds <of wrestling>. Some become injured or diseased
and will suffer a violent end.

\Saturn, \Mars, and \Venus\xspace are favorable at the start of actions, friendships, associations. These stars bring profit, high rank, and political associations. Later, however, men are put into a disturbed state, liable to lawsuits arising from some envy/hatred and treachery. Because of this, such men make accusations and they endure hostility from men and women. \textbf{/43P/} They are involved in shameful faults and adultery, and are the object of scandal and denunciation. Some are inclined to unnatural, bisexual vices, and they become accomplices or participants in crime or murder by poison. Then they suffer no ordinary anxiety.

\Saturn, \Mars, and \Mercury\xspace cause crime, treachery, judgements, and alarms. Men go into debts and expenses for the sake of scriptures or mystic lore, and they suffer no ordinary tribulations and ruin. In other cases these stars make men keen and intelligent in business, leading a varied life, \textbf{/44K/} maligned by some because of violent and illegal activities. Occasionally they become involved in toilsome and dangerous business and fall into poverty. Then they blame their own Fortune, blaspheme the gods, and become oath breakers and atheists. If the stars are not in their proper domicile, they bring criminal charges and imprisonment. If the stars do happen to be in their proper, operative places, these men will undertake struggles of behalf of others and will generally prevail, or they will profit from documents, from accounts, or from public office, and will increase their livelihood.

\Saturn, \Venus, and the \Sun\xspace are indicative of lofty associations, honors, and deeds, and they are the cause of high rank, distinction, and preeminence among the masses. They are unstable with respect to property or other matters, and they involve men in ups and downs: they dissolve friendships, effect the reduction of livelihood, and bring public exposure or punishments arising from the betrayal of females or of
religious matters. <They cause men to be> unstable and bisexual in their intercourse and other relationships.

\Saturn, \Venus, and the \Moon\xspace bring vicissitudes and instability of life, especially with respect to wife, mother, and children. They impose bad manners, ingratitude, as well as jealousy and quarrels, divorces, censure, public exposure, unnatural vices. But in business these men are not without resource, sharp, full of accomplishment, profiting from legacies. They do not however retain this wealth, since they are plotted against by many, and are themselves accomplices in crime and murder by poison, as well as seducers of women.

\Saturn, \Venus, and \Mercury\xspace make intelligent, clever individuals, shrewd and designing in their business enterprises. These men, however, are unsteady and \textbf{/44P/} frozen in their first enterprises. They become covetous of others’ goods, accomplices in many crimes, seekers of curious lore, flexible, healing, enjoying newness, change, and travel. If, under these conditions, the configuration is afflicted, or if \Mars\xspace is in aspect from the right, these men fall into disturbances and trials because of poisonings, of females, or because of legacies, or they suffer a loss of livelihood or an afflicting accusation after being wronged by women. In general they will be insecure and pained with respect to women, children, and slaves.\footnote{Combinations of \Saturn-\Mercury-\Sun, \Saturn-\Mercury-\Moon, and \Saturn-\Sun-\Moon\xspace are missing from the text.}

\secbr
\index{planets!Jupiter!in combination with other planets}
\subsection{\textit{[Jupiter in Combination]}}
\Jupiter, the \Sun, and the \Moon\xspace cause distinguished, brilliant, prominent men, \textbf{/45K/} supervisors of
public, civic, and royal affairs, governors, generals, men without peer, dictators, as well as men who are envied, maligned, and betrayed by some, men who hate their own families, man who change their minds. These men are fickle and mentally unstable, arrogant, planning for their own advantage and falling into vicissitudes. They are adorned with all the pomp of wealth, but do not continue happy to the end; they
falter in some things and ultimately come to grief.

\Jupiter, \Mars, and the \Sun\xspace are indicative of men involved in disturbances and dangers, but enthusiastic
and effective in their business enterprises. These men have a share of glory: they are leaders, governors, supervisors of public matters, but are prone to fall because the hatred of the great follows them, along with threats, betrayals, plots from their families, and criminal charges. A few, lifted from average fortune by the favor of the great, have later been ruined.

\Jupiter, \Mars, and the \Moon\xspace produce shrewd men, bold, public men with many friends, men advancing to high place from humble fortune and thought worthy of trust. These men are governors, athletes, distinguished men, leaders, supervisors of the masses and of districts. They have a share of offices, stipends, or priesthoods. They fall into reversals and criminal charges, betrayed by their own relatives or by females, and they suffer loss of possessions. Later however they recover them because of religious or other unexpected affairs.

\Jupiter, \Mars, and \Mercury\xspace cause vigorous, enthusiastic, active men. They receive a salary for public
office or military assignment or for doing royal or civic business. But they are unsteady in their \textbf{/45P/}
livelihood and spendthrift of their goods. They are however intelligent and trustworthy stewards, easily straightening out mistakes and laying on others the criticism originally directed at them. They are maligned and fall into reversals. These stars make some men athletes, prizewinners, and trainers, skilled at many things, fond of travelling and profiting in foreign lands, but failing with their own estates. 

\Jupiter, \Mars, and \Venus\xspace cause men to have many friends, to be easy to associate with, to be thought worthy of association with and help from the great, to be successful and to progress with the help of women. These stars make some men high-priests, prizewinners, athletes, or supervisors of temples or of downs. These men are blameworthy and indiscriminate about sexual matters, experiencing public exposure and betrayal, grieved with respect to children and slaves, enjoying new associations, and enduring separations from women.

\Jupiter, \Mercury, and the \Sun\xspace cause men to be easily successful in business enterprises and to have many friends, to be thought worthy of trusts, honors, stewardships, association with the great, and success. Some men advance from humble origins and are honored. But they let their possessions slip from their grasp; they are easily deceived, and they become poor for some time. They do many things for religious
reasons. They are not without a livelihood, but are supported by unexpected sources of high rank.

\Jupiter, \Mercury, and the \Moon\xspace make noble, propertied men, shrewd in business, collectors of gifts
and sharers in trusts, religious men, intelligent, eloquent, guardians of property and deposits, making their careers amidst documents and accounts. They are lavish, tax-gatherers, stipend holders, with many friends, well-known, trustees, administrators of affairs, generous. These stars also make men athletes, prizewinners, worthy of honors, pictures, and statues, If these stars occur in operative places, they make men discoverers of treasures and overseers of shrines and temples. These men will rebuild, replant, and restore places, and will win eternal fame.

\textbf{/46P/}\Jupiter, \Mercury, and \Venus\xspace are good, bringing possession of livelihoods and success in business. Men become intelligent, straightforward, generous, sweet, loving their families, cheerful, participants in education and culture, pure, decent, worthy of honor and high rank, associated with the great, and sharing in trusts and stewardships. These men are honored with livelihoods. They foster the young and are fond of education. They are masters of slaves and they rear some and benefit them as if they
were their own children. Since they are pious, they know the future from the gods, but they will become unsteady and grief-stricken with respect to wife and children.

\textbf{/47K/}\Jupiter, \Venus, and the \Sun\xspace make men who are spectacular and glorious, but who are also petty,
mentally unstable, and arrogant. Sometimes they are liberal and beneficent, though changeable. At other times they are exalted with the help of another person’s fame and possessions, and although coming from humble origins, they become high-priests, prizewinners, leaders, governors, preeminent in public matters, and protectors of the masses. They are thought worthy of honors and gifts and are granted livelihoods. They will however become unnatural and blameworthy in sexual matters. If these stars happen to be rising or in operative places, then these men will be happy with their wives and children.

\Jupiter, \Venus, and the \Moon\xspace cause vigorous, famous men, high-priests, prizewinners, overseers of temples and shrines, benefactors, men eager for fame, catering to the pleasures of the masses, of cities, or of villages. These men receive trusts and are thought worthy of honor. They are well spoken of and envied by family and friends, but experience hostility and opposition. With respect to wives and intimate friends, they are unsteady and quarrelsome, living with jealousy and separation and pain, always in suspense. Sometimes they are intimate with relatives, but not even then do they have an undisturbed home life. They get into partnerships. They will, however, become very spectacular in their manner of life, but they are full of false show, not of the truth.

\secbr
\index{planets!Venus!in combination with other planets}
\subsection{\textit{[Venus in Combination]}}
\Venus, the \Sun, and the \Moon\xspace cause famous and vigorous men, those who live with ostentation, those who are malicious and blameworthy, slandered by most people and envied/hated by the great and by their friends. They succeed and gain possessions and are raised high by Fortune, but they are also unsteady
\textbf{/47P/} with respect to wife and children. Otherwise they are fond of their friends and travel much, finding
good fortune in foreign lands.

\Venus, \Mars, and the \Moon\xspace make men who are not without resources and not inactive, but who are also fickle and mentally unstable, quixotic, beginning in confusion and putting <no> end to their affairs. They have great plans, are contemptuous, wandering, bold, public, martial, indiscriminate in their use of male and female partners. They are maligned and fall into insulting treatment and trials, changing friendship into enmity because of their criminal attempts, and failing in their livelihood.

\secbr
\index{planets!Mercury!in combination with other planets}
\subsection{\textit{[Mercury in Combination]}}
\textbf{/48K/}\Mercury, the \Sun, and the \Moon\xspace make revered and pure men, those who play their part well, stewards, and those who share honors and positions. They are benefactors, participants in the mysteries, troubleshooters, and they put on a great show of possessions. They become bodyguards, chamberlains, and men placed in charge of money, records, and accounts. The speech of such men will be most effective for advice or instruction.

\Mercury, the \Sun, and \Venus\xspace make polymaths and men of wide experience. These men are noble, prominent in the arts and sciences, worthy of trusts and positions. They easily regret what has been done, sometimes wavering and moved in all directions, or enjoying changes in their occupations. They have many friends, are well known, succeed through their acquaintance with the great, and are honored with a livelihood and high rank, despite being blameworthy.

\Mercury, the \Moon, and \Venus\xspace make good men, easy to live with, straightforward, generous, with a sense of humor, civic-minded, sharers in education and rhythm, ingenious, of wide experience, neat, pure, simple, participating in religious ceremonies, helpful, envied and hated, unstable in their livelihoods, and indiscriminate in their intercourse with men or women, wealthy, and thrifty.

\Mercury, \Mars, and \Venus\xspace when configured together bring profit, high rank, occupations. <These stars make men who are> shrewd in giving, receiving, and undertaking other business, who are stewards, wicked and widely experienced men, men who start their careers with documents and training. They are blameworthy, wasting much wealth, generous, wallowing in loans and debts and defaulting, embezzlers of others’ money, seducers, deceiving with their charm, wealthy, malignant—but repenting of what they have done.

\secbr
\index{planets!Mars!in combination with other planets}
\subsection{\textit{[Mars in Combination]}}
\textbf{/48P/}\Mars, the \Sun, and the \Moon\xspace make bold, manly, reckless, vigorous men. They become athletes and soldiers, rulers and governors, and they make their careers through violent, hateful deeds, in laborious crafts, or in work in hard materials. They fall into reverses and into dangerous situations, and suffer hostility and attacks from the great, but if benefics are in aspect, they maintain the basis <of their nativity> unimpaired.

\Mars, the \Sun, and \Venus\xspace cause men to have many friends and to be well-known, \textbf{/49K/} to be thought
worthy of alliances and honors. These men have many resources, love their associates, but are criticized and gossiped about. Their friendships do not last and their accomplishments are fleeting. They desire much, they spend much, they are wrongers of women, and they are very ready to be insolent. They fall
into reverses and hostility through their reckless decisions.

\Mars, the \Sun, and \Mercury\xspace make men of much experience, inventive in business enterprises. Although careworn and unsuccessful in the goal of their calculations, they prevail unexpectedly. Therefore such men are mentally unstable, reckless, active, hot-tempered; after rushing against their enemies and bringing charges of wrongdoing or damages against them, these men then change their minds.
Occasionally they have a cowardly and despicable character. They control their emotions well, play a part, and yield to men whom they should not yield to. For the most part, they have a livelihood subject to ups and downs. On coming into another’s control, they curse their own Fortune.

\Mars, the \Moon, and \Mercury\xspace make men skillful and ingenious, easily aroused to action and very vigorous, wanting to act quickly, but being remiss, seekers of curious lore, initiates of the mysteries, and partakers of secret knowledge. They are oppressors, violent, insubordinate, covetous, falling into accusations and suits for damages, into trials and dangers, and they experience alarms because of documents
and money. However, these stars do make men wealthy and lavish, although failing in their livelihood. 

\textbf{/49P/} This then is what we have explained with respect to the distinctive characteristics of individual stars as well as several taken together. If other stars share the configuration (being in conjunction or in aspect), the reading of the horoscope will be changed according to the nature of the additional star. However I did not want to continue writing at length about such additional factors, because the old astrologers have expounded them already. 

\mndl[0.2cm]
\index{planets!predicting effects}
The particular effects of the natural influence of each star and sign will be obvious at once to anyone who pays attention. (These have been explained previously in our treatise.) Therefore it will be necessary to determine how each star is configured in relation to the others: 
\begin{itemize}
\item is it at an angle or rising? 
\item Is it the ruler of a lot, of the Ascendant, or of a triangle? 
\item Likewise with the sign in which the star appears: 
\begin{itemize}
\item is it of its own or of another sect, and 
\item which \textbf{/50K/} other signs does it have in aspect? 
\end{itemize}
\end{itemize}

If these things are determined, the predictions will be solidly based. 

If <stars> fall in inoperative places, the <level of> occupation and of Fortune will be less.


\newpage